\documentclass[14pt]{book}
\usepackage{kamatz_list_style}
\begin{document}
	
\title{\hebword{ספר מלא קָמצו}
	
	A Guide to Kamatz Katan}

\author{Nathan Kasimer}

\date{}

\maketitle

\tableofcontents

\chapter{Introduction}
This is a list of kamatz katans in the Torah.  The list was generated using a Python script from the "Miqra According to the Masora" project.  While it was reviewed and checked manually, the checking process was not very in-depth, and it likely contains errors.  Please report errors found by submitting an issue report in the github repo here: \url{https://github.com/nkasimer/kamatz-katan-list/issues}

The various forms of the word \hebword{כל} have not been included because of how common the word is.  Special mention should be made, however, of Isaiah 40:12, where the word \hebword{כל} has a kamatz gadol and is a verb.  Because kamatz katan (like all Masoretic vowels) is purely a phenomenon of the text as vocalized, not the written text, the list of kamatzes includes \textit{only} the kri, not the ketiv.

Words where reading traditions vary have been noted.  Generally these are words where a kamatz is followed by a gutteral consonant which is followed by a chataf-kamatz.  Sephardim, following the Radak, pronounce these as kamatz gadol. Others read it as a kamatz klatan. The same variation exists for words that, grammatically, usually would have a maqqaf joining them to the following word, but for some reason the maqqaf is missing. Sepharadim follow the Radak and pronounce it as a kamatz gadol, others read a kamatz katan.

This is designed as a quick reference guide.  The book "The Ohs and Ahs of Torah Reading" by Rivka Sherman-Gold has a similar guide which inspired this one.  While that text is extremely helpful, both in its reference guide and its explanation of the rules for kamatz-types, it is out-of-print and difficult to find. This is intended to fill the gap, in part, from the difficulty in finding it.

\chapter{An Overview of Determining Kamatz Length}


\chapter{Chumash}

\section{Genesis}

\begin{multicols}{2}
\begin{itemize} \item Gen 1:29\hebword{לְאׇכְלָֽה}

\item Gen 1:30\hebword{לְאׇכְלָ֑ה}

\item Gen 2:15\hebword{לְעׇבְדָ֖הּ}

\item Gen 2:15\hebword{וּלְשׇׁמְרָֽהּ}

\item Gen 2:24\hebword{יַֽעֲזׇב־אִ֔ישׁ}

\item Gen 3:16\hebword{יִמְשׇׁל־בָּֽךְ}

\item Gen 3:21\hebword{כׇּתְנ֥וֹת}

\item Gen 4:7\hebword{תִּמְשׇׁל־בּֽוֹ}

\item Gen 4:8\hebword{וַיָּ֥קׇם}

\subsection{Noa\d{h}}

\item Gen 6:15\hebword{רׇחְבָּ֔הּ}

\item Gen 6:21\hebword{לְאׇכְלָֽה}

\item Gen 7:17\hebword{וַתָּ֖רׇם}

\item Gen 8:9\hebword{וַתָּ֤שׇׁב}

\item Gen 9:3\hebword{לְאׇכְלָ֑ה}

\item Gen 9:21\hebword{אׇהֳלֹֽה} This kamatz katan is subject to debate between experts and reading traditions.

\item Gen 9:27\hebword{בְּאׇֽהֳלֵי־שֵׁ֑ם} This kamatz katan is subject to debate between experts and reading traditions.

\item Gen 10:25\hebword{יׇקְטָֽן}

\item Gen 10:26\hebword{וְיׇקְטָ֣ן}

\item Gen 10:29\hebword{יׇקְטָֽן}

\item Gen 11:2\hebword{בְּנׇסְעָ֣ם}

\item Gen 11:28\hebword{וַיָּ֣מׇת}

\item Gen 11:32\hebword{וַיָּ֥מׇת}

\subsection{Lekh-lekha}

\item Gen 12:8\hebword{אׇהֳלֹ֑ה} This kamatz katan is subject to debate between experts and reading traditions.

\item Gen 13:3\hebword{אׇֽהֳלֹה֙} This kamatz katan is subject to debate between experts and reading traditions.

\item Gen 13:17\hebword{לְאׇרְכָּ֖הּ}

\item Gen 13:17\hebword{וּלְרׇחְבָּ֑הּ}

\item Gen 14:1\hebword{כְּדׇרְלָעֹ֙מֶר֙}

\item Gen 14:4\hebword{אֶת־כְּדׇרְלָעֹ֑מֶר}

\item Gen 14:5\hebword{כְדׇרְלָעֹ֗מֶר}

\item Gen 14:9\hebword{כְּדׇרְלָעֹ֜מֶר}

\item Gen 14:11\hebword{וְאֶת־כׇּל־אׇכְלָ֖ם}

\item Gen 14:17\hebword{כְּדׇרְלָעֹ֔מֶר}

\item Gen 16:11\hebword{אֶל־עׇנְיֵֽךְ}

\item Gen 17:11\hebword{עׇרְלַתְכֶ֑ם}

\item Gen 17:14\hebword{עׇרְלָת֔וֹ}

\item Gen 17:23\hebword{וַיָּ֜מׇל}

\item Gen 17:24\hebword{עׇרְלָתֽוֹ}

\item Gen 17:25\hebword{עׇרְלָתֽוֹ}

\subsection{Vayera}

\item Gen 18:2\hebword{וַיָּ֤רׇץ}

\item Gen 19:1\hebword{וַיָּ֣קׇם}

\item Gen 19:21\hebword{הׇפְכִּ֥י}

\item Gen 19:24\hebword{גׇּפְרִ֣ית}

\item Gen 19:34\hebword{מִֽמׇּחֳרָ֔ת} This kamatz katan is subject to debate between experts and reading traditions.

\item Gen 19:35\hebword{וַתָּ֤קׇם}

\item Gen 20:1\hebword{וַיָּ֖גׇר}

\item Gen 20:5\hebword{בְּתׇם־לְבָבִ֛י}

\item Gen 20:6\hebword{בְתׇם־לְבָבְךָ֙}

\item Gen 20:8\hebword{בְּאׇזְנֵיהֶ֑ם}

\item Gen 20:12\hebword{וְגַם־אׇמְנָ֗ה}

\item Gen 21:4\hebword{וַיָּ֤מׇל}

\item Gen 21:32\hebword{וַיָּ֣קׇם}

\item Gen 21:34\hebword{וַיָּ֧גׇר}

\item Gen 22:3\hebword{וַיָּ֣קׇם}

\item Gen 22:19\hebword{וַיָּ֤שׇׁב}

\subsection{\d{H}ayei Sara}

\item Gen 23:2\hebword{וַתָּ֣מׇת}

\item Gen 23:3\hebword{וַיָּ֙קׇם֙}

\item Gen 23:7\hebword{וַיָּ֧קׇם}

\item Gen 23:10\hebword{בְּאׇזְנֵ֣י}

\item Gen 23:13\hebword{בְּאׇזְנֵ֤י}

\item Gen 23:16\hebword{בְּאׇזְנֵ֣י}

\item Gen 23:17\hebword{וַיָּ֣קׇם}

\item Gen 23:20\hebword{וַיָּ֨קׇם}

\item Gen 24:10\hebword{וַיָּ֗קׇם}

\item Gen 24:17\hebword{וַיָּ֥רׇץ}

\item Gen 24:20\hebword{וַתָּ֥רׇץ}

\item Gen 24:28\hebword{וַתָּ֙רׇץ֙}

\item Gen 24:29\hebword{וַיָּ֨רׇץ}

\item Gen 24:30\hebword{וּכְשׇׁמְע֗וֹ}

\item Gen 24:61\hebword{וַתָּ֨קׇם}

\item Gen 25:2\hebword{וְאֶת־יׇקְשָׁ֔ן}

\item Gen 25:3\hebword{וְיׇקְשָׁ֣ן}

\item Gen 25:8\hebword{וַיָּ֧מׇת}

\item Gen 25:17\hebword{וַיָּ֔מׇת}

\item Gen 25:34\hebword{וַיָּ֖קׇם}

\subsection{Toledot}

\item Gen 26:18\hebword{וַיָּ֨שׇׁב}

\item Gen 26:25\hebword{אׇהֳל֑וֹ} This kamatz katan is subject to debate between experts and reading traditions.

\item Gen 27:19\hebword{וְאׇכְלָה֙}

\item Gen 27:42\hebword{לְהׇרְגֶֽךָ}

\subsection{Vayetzei}

\item Gen 29:12\hebword{וַתָּ֖רׇץ}

\item Gen 29:13\hebword{וַיָּ֤רׇץ}

\item Gen 29:18\hebword{אֶֽעֱבׇדְךָ֙}

\item Gen 29:32\hebword{בְּעׇנְיִ֔י}

\item Gen 30:13\hebword{בְּאׇשְׁרִ֕י}

\item Gen 30:28\hebword{נׇקְבָ֧ה}

\item Gen 31:15\hebword{נׇכְרִיּ֛וֹת}

\item Gen 31:17\hebword{וַיָּ֖קׇם}

\item Gen 31:21\hebword{וַיָּ֖קׇם}

\item Gen 31:25\hebword{אֶֽת־אׇהֳלוֹ֙} This kamatz katan is subject to debate between experts and reading traditions.

\item Gen 31:42\hebword{אֶת־עׇנְיִ֞י}

\item Gen 32:1\hebword{וַיָּ֥שׇׁב}

\item Gen 32:18\hebword{יִֽפְגׇשְׁךָ֞} This kamatz katan is subject to debate between experts and reading traditions.

\item Gen 32:23\hebword{וַיָּ֣קׇם}

\item Gen 33:4\hebword{וַיָּ֨רׇץ}

\item Gen 33:14\hebword{יַעֲבׇר־נָ֥א}

\item Gen 33:16\hebword{וַיָּ֩שׇׁב֩}

\item Gen 33:19\hebword{אׇהֳל֔וֹ} This kamatz katan is subject to debate between experts and reading traditions.

\item Gen 34:7\hebword{כְּשׇׁמְעָ֔ם}

\item Gen 34:14\hebword{עׇרְלָ֑ה}

\item Gen 35:1\hebword{בְּבׇ֨רְחֲךָ֔}

\item Gen 35:4\hebword{בְּאׇזְנֵיהֶ֑ם}

\item Gen 35:7\hebword{בְּבׇרְח֖וֹ}

\item Gen 35:8\hebword{וַתָּ֤מׇת}

\item Gen 35:19\hebword{וַתָּ֖מׇת}

\item Gen 35:21\hebword{אׇֽהֳלֹ֔ה} This kamatz katan is subject to debate between experts and reading traditions.

\item Gen 35:29\hebword{וַיָּ֙מׇת֙}

\item Gen 36:2\hebword{וְאֶת־אׇהֳלִֽיבָמָה֙} This kamatz katan is subject to debate between experts and reading traditions.

\item Gen 36:5\hebword{וְאׇהֳלִֽיבָמָה֙} This kamatz katan is subject to debate between experts and reading traditions.

\item Gen 36:14\hebword{אׇהֳלִיבָמָ֧ה} This kamatz katan is subject to debate between experts and reading traditions.

\item Gen 36:18\hebword{אׇהֳלִֽיבָמָה֙} This kamatz katan is subject to debate between experts and reading traditions.

\item Gen 36:18\hebword{אׇהֳלִֽיבָמָ֛ה} This kamatz katan is subject to debate between experts and reading traditions.

\item Gen 36:25\hebword{וְאׇהֳלִיבָמָ֖ה} This kamatz katan is subject to debate between experts and reading traditions.

\item Gen 36:31\hebword{מְלׇךְ־מֶ֖לֶךְ}

\item Gen 36:33\hebword{וַיָּ֖מׇת}

\item Gen 36:33\hebword{מִבׇּצְרָֽה}

\item Gen 36:35\hebword{וַיָּ֖מׇת}

\item Gen 36:36\hebword{וַיָּ֖מׇת}

\item Gen 36:37\hebword{וַיָּ֖מׇת}

\item Gen 36:38\hebword{וַיָּ֖מׇת}

\item Gen 36:39\hebword{וַיָּ֘מׇת֮}

\item Gen 36:41\hebword{אׇהֳלִיבָמָ֛ה} This kamatz katan is subject to debate between experts and reading traditions.

\subsection{Vayeshev}

\item Gen 37:23\hebword{אֶת־כֻּתׇּנְתּ֔וֹ}

\item Gen 37:29\hebword{וַיָּ֤שׇׁב}

\item Gen 37:30\hebword{וַיָּ֥שׇׁב}

\item Gen 37:34\hebword{בְּמׇתְנָ֑יו}

\item Gen 38:9\hebword{נְתׇן־זֶ֖רַע}

\item Gen 38:12\hebword{וַתָּ֖מׇת}

\item Gen 38:19\hebword{וַתָּ֣קׇם}

\item Gen 38:22\hebword{וַיָּ֙שׇׁב֙}

\item Gen 39:12\hebword{וַיָּ֖נׇס}

\item Gen 39:13\hebword{וַיָּ֖נׇס}

\item Gen 39:15\hebword{כְשׇׁמְע֔וֹ}

\item Gen 39:15\hebword{וַיָּ֖נׇס}

\item Gen 39:18\hebword{וַיָּ֥נׇס}

\subsection{Mikketz}

\item Gen 41:12\hebword{וַיִּפְתׇּר־לָ֖נוּ}

\item Gen 41:46\hebword{בְּעׇמְד֕וֹ}

\item Gen 41:50\hebword{יֻלׇּד֙} Most texts do not have a kamatz here, if it is a kamatz it should be katan.

\item Gen 41:52\hebword{עׇנְיִֽי}

\item Gen 42:7\hebword{לִשְׁבׇּר־אֹֽכֶל}

\item Gen 42:10\hebword{לִשְׁבׇּר־אֹֽכֶל}

\item Gen 42:24\hebword{וַיָּ֤שׇׁב}

\item Gen 43:11\hebword{בׇּטְנִ֖ים}

\item Gen 43:16\hebword{בַּֽצׇּהֳרָֽיִם} This kamatz katan is subject to debate between experts and reading traditions.

\item Gen 43:20\hebword{לִשְׁבׇּר־אֹֽכֶל}

\item Gen 43:22\hebword{לִשְׁבׇּר־אֹ֑כֶל}

\item Gen 43:25\hebword{בַּֽצׇּהֳרָ֑יִם} This kamatz katan is subject to debate between experts and reading traditions.

\item Gen 43:29\hebword{יׇחְנְךָ֖}

\subsection{Vayigash}

\item Gen 44:18\hebword{בְּאׇזְנֵ֣י}

\item Gen 45:26\hebword{וַיָּ֣פׇג}

\item Gen 46:5\hebword{וַיָּ֥קׇם}

\item Gen 46:12\hebword{וַיָּ֨מׇת}

\item Gen 47:24\hebword{וּֽלְאׇכְלְכֶ֛ם}

\item Gen 49:26\hebword{וּלְקׇדְקֹ֖ד}

\item Gen 50:4\hebword{בְּאׇזְנֵ֥י}

\item Gen 50:14\hebword{וַיָּ֨שׇׁב}

\item Gen 50:14\hebword{קׇבְר֥וֹ}

\item Gen 50:26\hebword{וַיָּ֣מׇת}
\end{itemize}\end{multicols}
\section{Exodus}
\begin{multicols}{2}\begin{itemize}
\item Ex 1:6\hebword{וַיָּ֤מׇת}

\item Ex 1:8\hebword{וַיָּ֥קׇם}

\item Ex 1:16\hebword{עַל־הָאׇבְנָ֑יִם}

\item Ex 2:14\hebword{הַלְהׇרְגֵ֙נִי֙}

\item Ex 2:17\hebword{וַיָּ֤קׇם}

\item Ex 2:22\hebword{נׇכְרִיָּֽה}

\item Ex 2:23\hebword{וַיָּ֙מׇת֙}

\item Ex 4:3\hebword{וַיָּ֥נׇס}

\item Ex 4:18\hebword{וַיָּ֣שׇׁב}

\item Ex 4:20\hebword{וַיָּ֖שׇׁב}

\item Ex 4:25\hebword{אֶת־עׇרְלַ֣ת}

\item Ex 4:31\hebword{אֶת־עׇנְיָ֔ם}

\item Ex 5:14\hebword{חׇקְכֶ֤ם}

\item Ex 5:21\hebword{לְהׇרְגֵֽנוּ}

\item Ex 5:22\hebword{וַיָּ֧שׇׁב}

\subsection{Va'era}

\item Ex 6:24\hebword{הַקׇּרְחִֽי}

\item Ex 9:6\hebword{מִֽמׇּחֳרָ֔ת} This kamatz katan is subject to debate between experts and reading traditions.

\item Ex 9:6\hebword{וַיָּ֕מׇת}

\item Ex 9:8\hebword{חׇפְנֵיכֶ֔ם}

\subsection{Bo}

\item Ex 10:2\hebword{בְּאׇזְנֵ֨י}

\item Ex 11:2\hebword{בְּאׇזְנֵ֣י}

\item Ex 11:8\hebword{בׇּחֳרִי־אָֽף} This kamatz katan is subject to debate between experts and reading traditions.

\item Ex 12:2\hebword{לְחׇדְשֵׁ֖י}

\item Ex 12:4\hebword{אׇכְל֔וֹ}

\item Ex 12:11\hebword{מׇתְנֵיכֶ֣ם}

\item Ex 12:14\hebword{תְּחׇגֻּֽהוּ}

\item Ex 12:24\hebword{לְחׇק־לְךָ֥}

\item Ex 12:27\hebword{בְּנׇגְפּ֥וֹ}

\item Ex 12:30\hebword{וַיָּ֨קׇם}

\subsection{Beshalla\d{h}}

\item Ex 14:24\hebword{וַיָּ֕הׇם}

\item Ex 14:27\hebword{וַיָּ֨שׇׁב}

\item Ex 15:13\hebword{בְעׇזְּךָ֖}

\item Ex 15:13\hebword{קׇדְשֶֽׁךָ}

\item Ex 16:3\hebword{בְּאׇכְלֵ֥נוּ}

\item Ex 16:7\hebword{בְּשׇׁמְע֥וֹ}

\item Ex 16:15\hebword{לְאׇכְלָֽה}

\item Ex 16:16\hebword{אׇכְל֑וֹ}

\item Ex 16:16\hebword{בְּאׇהֳל֖וֹ} This kamatz katan is subject to debate between experts and reading traditions.

\item Ex 16:18\hebword{לְפִֽי־אׇכְל֖וֹ}

\item Ex 16:21\hebword{אׇכְל֑וֹ}

\item Ex 17:14\hebword{בְּאׇזְנֵ֣י}

\subsection{Yitro}

\item Ex 18:3\hebword{נׇכְרִיָּֽה}

\item Ex 18:13\hebword{מִֽמׇּחֳרָ֔ת} This kamatz katan is subject to debate between experts and reading traditions.

\item Ex 19:24\hebword{פֶּן־יִפְרׇץ־בָּֽם}

\item Ex 20:4\hebword{תׇעׇבְדֵ֑ם֒} This kamatz katan is subject to debate between experts and reading traditions.

\subsection{Mishpatim}

\item Ex 21:2\hebword{לַֽחׇפְשִׁ֖י}

\item Ex 21:5\hebword{חׇפְשִֽׁי}

\item Ex 21:6\hebword{אֶת־אׇזְנוֹ֙}

\item Ex 21:8\hebword{נׇכְרִ֛י}

\item Ex 21:8\hebword{לְמׇכְרָ֖הּ}

\item Ex 21:11\hebword{וְאִ֨ם־שְׁלׇשׁ־אֵ֔לֶּה}

\item Ex 21:14\hebword{לְהׇרְג֣וֹ}

\item Ex 21:14\hebword{בְעׇרְמָ֑ה}

\item Ex 21:27\hebword{לַֽחׇפְשִׁ֥י}

\item Ex 22:19\hebword{יׇֽחֳרָ֑ם} This kamatz katan is subject to debate between experts and reading traditions.

\item Ex 23:16\hebword{בְּאׇסְפְּךָ֥}

\item Ex 23:24\hebword{תָֽעׇבְדֵ֔ם}

\item Ex 24:7\hebword{בְּאׇזְנֵ֣י}

\item Ex 24:13\hebword{וַיָּ֣קׇם}

\subsection{Teruma}

\item Ex 25:5\hebword{מְאׇדָּמִ֛ים}

\item Ex 25:10\hebword{רׇחְבּ֔וֹ}

\item Ex 25:17\hebword{אׇרְכָּ֔הּ}

\item Ex 25:17\hebword{רׇחְבָּֽהּ}

\item Ex 25:23\hebword{אׇרְכּוֹ֙}

\item Ex 25:23\hebword{רׇחְבּ֔וֹ}

\item Ex 25:40\hebword{מׇרְאֶ֖ה}

\item Ex 26:1\hebword{מׇשְׁזָ֗ר}

\item Ex 26:14\hebword{מְאׇדָּמִ֑ים}

\item Ex 26:30\hebword{הׇרְאֵ֖יתָ}

\item Ex 26:31\hebword{מׇשְׁזָ֑ר}

\item Ex 26:36\hebword{מׇשְׁזָ֑ר}

\item Ex 27:9\hebword{מׇשְׁזָ֗ר}

\item Ex 27:16\hebword{מׇשְׁזָ֖ר}

\item Ex 27:18\hebword{מׇשְׁזָ֑ר}

\subsection{Tetzaveh}

\item Ex 28:3\hebword{חׇכְמָ֑ה}

\item Ex 28:6\hebword{מׇשְׁזָ֖ר}

\item Ex 28:8\hebword{מׇשְׁזָֽר}

\item Ex 28:15\hebword{מׇשְׁזָ֖ר}

\item Ex 28:16\hebword{אׇרְכּ֖וֹ}

\item Ex 28:16\hebword{רׇחְבּֽוֹ}

\item Ex 28:38\hebword{קׇדְשֵׁיהֶ֑ם}

\item Ex 28:42\hebword{מִמׇּתְנַ֥יִם}

\item Ex 29:28\hebword{לְחׇק־עוֹלָ֗ם}

\item Ex 29:29\hebword{לְמׇשְׁחָ֣ה}

\item Ex 29:37\hebword{קׇֽדָשִׁ֔ים} This kamatz katan is subject to debate between experts and reading traditions.

\item Ex 29:46\hebword{לְשׇׁכְנִ֣י}

\item Ex 30:2\hebword{אׇרְכּ֜וֹ}

\item Ex 30:2\hebword{רׇחְבּוֹ֙}

\item Ex 30:10\hebword{קֹֽדֶשׁ־קׇדָשִׁ֥ים} This kamatz katan is subject to debate between experts and reading traditions.

\subsection{Ki-tissa}

\item Ex 30:18\hebword{לְרׇחְצָ֑ה}

\item Ex 30:21\hebword{חׇק־עוֹלָ֛ם}

\item Ex 30:23\hebword{מׇר־דְּרוֹר֙}

\item Ex 30:23\hebword{וְקִנְּמׇן־בֶּ֥שֶׂם}

\item Ex 30:29\hebword{קׇֽדָשִׁ֑ים} This kamatz katan is subject to debate between experts and reading traditions.

\item Ex 30:36\hebword{קׇֽדָשִׁ֖ים} This kamatz katan is subject to debate between experts and reading traditions.

\item Ex 31:3\hebword{בְּחׇכְמָ֛ה}

\item Ex 31:6\hebword{אׇהֳלִיאָ֞ב} This kamatz katan is subject to debate between experts and reading traditions.

\item Ex 31:6\hebword{חׇכְמָ֑ה}

\item Ex 32:2\hebword{בְּאׇזְנֵ֣י}

\item Ex 32:3\hebword{בְּאׇזְנֵיהֶ֑ם}

\item Ex 32:6\hebword{מִֽמׇּחֳרָ֔ת} This kamatz katan is subject to debate between experts and reading traditions.

\item Ex 32:30\hebword{מִֽמׇּחֳרָ֔ת} This kamatz katan is subject to debate between experts and reading traditions.

\item Ex 32:31\hebword{וַיָּ֧שׇׁב}

\item Ex 32:34\hebword{פׇּקְדִ֔י}

\item Ex 33:8\hebword{אׇהֳל֑וֹ} This kamatz katan is subject to debate between experts and reading traditions.

\item Ex 33:10\hebword{אׇהֳלֽוֹ} This kamatz katan is subject to debate between experts and reading traditions.

\item Ex 33:22\hebword{עַד־עׇבְרִֽי}

\item Ex 34:1\hebword{פְּסׇל־לְךָ֛}

\item Ex 34:11\hebword{שְׁמׇ֨ר־לְךָ֔}

\item Ex 34:27\hebword{כְּתׇב־לְךָ֖}

\subsection{Vayakhel}

\item Ex 35:7\hebword{מְאׇדָּמִ֛ים}

\item Ex 35:11\hebword{אֶֽת־אׇהֳל֖וֹ} This kamatz katan is subject to debate between experts and reading traditions.

\item Ex 35:23\hebword{מְאׇדָּמִ֛ים}

\item Ex 35:26\hebword{בְּחׇכְמָ֑ה}

\item Ex 35:31\hebword{בְּחׇכְמָ֛ה}

\item Ex 35:34\hebword{וְאׇֽהֳלִיאָ֥ב} This kamatz katan is subject to debate between experts and reading traditions.

\item Ex 35:35\hebword{חׇכְמַת־לֵ֗ב}

\item Ex 36:1\hebword{וְאׇהֳלִיאָ֜ב} This kamatz katan is subject to debate between experts and reading traditions.

\item Ex 36:1\hebword{חׇכְמָ֤ה}

\item Ex 36:2\hebword{וְאֶל־אׇֽהֳלִיאָב֒} This kamatz katan is subject to debate between experts and reading traditions.

\item Ex 36:2\hebword{חׇכְמָ֖ה}

\item Ex 36:2\hebword{לְקׇרְבָ֥ה}

\item Ex 36:8\hebword{מׇשְׁזָ֗ר}

\item Ex 36:19\hebword{מְאׇדָּמִ֑ים}

\item Ex 36:35\hebword{מׇשְׁזָ֑ר}

\item Ex 36:37\hebword{מׇשְׁזָ֑ר}

\item Ex 37:1\hebword{אׇרְכּ֗וֹ}

\item Ex 37:1\hebword{רׇחְבּ֔וֹ}

\item Ex 37:6\hebword{אׇרְכָּ֔הּ}

\item Ex 37:6\hebword{רׇחְבָּֽהּ}

\item Ex 37:10\hebword{אׇרְכּוֹ֙}

\item Ex 37:10\hebword{רׇחְבּ֔וֹ}

\item Ex 37:25\hebword{אׇרְכּוֹ֩}

\item Ex 37:25\hebword{רׇחְבּ֜וֹ}

\item Ex 38:1\hebword{אׇרְכּ֜וֹ}

\item Ex 38:1\hebword{רׇחְבּוֹ֙}

\item Ex 38:9\hebword{מׇשְׁזָ֔ר}

\item Ex 38:16\hebword{מׇשְׁזָֽר}

\subsection{Pekudei}

\item Ex 38:23\hebword{אׇהֳלִיאָ֞ב} This kamatz katan is subject to debate between experts and reading traditions.

\item Ex 39:2\hebword{מׇשְׁזָֽר}

\item Ex 39:5\hebword{מׇשְׁזָ֑ר}

\item Ex 39:8\hebword{מׇשְׁזָֽר}

\item Ex 39:9\hebword{אׇרְכּ֛וֹ}

\item Ex 39:9\hebword{רׇחְבּ֖וֹ}

\item Ex 39:24\hebword{מׇשְׁזָֽר}

\item Ex 39:27\hebword{אֶת־הַכׇּתְנֹ֥ת}

\item Ex 39:28\hebword{מׇשְׁזָֽר}

\item Ex 39:29\hebword{מׇשְׁזָ֗ר}

\item Ex 39:34\hebword{הַמְאׇדָּמִ֔ים}

\item Ex 40:10\hebword{קׇֽדָשִֽׁים} This kamatz katan is subject to debate between experts and reading traditions.

\item Ex 40:15\hebword{מׇשְׁחָתָ֛ם}

\item Ex 40:30\hebword{לְרׇחְצָֽה}

\item Ex 40:32\hebword{וּבְקׇרְבָתָ֛ם}
\end{itemize}\end{multicols}
\section{Leviticus}
\begin{multicols}{2}\begin{itemize}
\item Lev 1:2\hebword{קׇרְבָּ֖ן}

\item Lev 1:2\hebword{אֶת־קׇרְבַּנְכֶֽם}

\item Lev 1:3\hebword{קׇרְבָּנוֹ֙}

\item Lev 1:10\hebword{קׇרְבָּנ֧וֹ}

\item Lev 1:14\hebword{קׇרְבָּנ֖וֹ}

\item Lev 1:14\hebword{אֶת־קׇרְבָּנֽוֹ}

\item Lev 2:1\hebword{קׇרְבַּ֤ן}

\item Lev 2:1\hebword{קׇרְבָּנ֑וֹ}

\item Lev 2:2\hebword{מִסׇּלְתָּהּ֙}

\item Lev 2:3\hebword{קׇֽדָשִׁ֖ים} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 2:4\hebword{קׇרְבַּ֥ן}

\item Lev 2:5\hebword{קׇרְבָּנֶ֑ךָ}

\item Lev 2:7\hebword{קׇרְבָּנֶ֑ךָ}

\item Lev 2:10\hebword{קׇֽדָשִׁ֖ים} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 2:12\hebword{קׇרְבַּ֥ן}

\item Lev 2:13\hebword{וְכׇל־קׇרְבַּ֣ן}

\item Lev 2:13\hebword{כׇּל־קׇרְבָּנְךָ֖}

\item Lev 3:1\hebword{קׇרְבָּנ֑וֹ}

\item Lev 3:2\hebword{קׇרְבָּנ֔וֹ}

\item Lev 3:6\hebword{קׇרְבָּנ֛וֹ}

\item Lev 3:7\hebword{אֶת־קׇרְבָּנ֑וֹ}

\item Lev 3:8\hebword{קׇרְבָּנ֔וֹ}

\item Lev 3:12\hebword{קׇרְבָּנ֑וֹ}

\item Lev 3:14\hebword{קׇרְבָּנ֔וֹ}

\item Lev 4:23\hebword{אֶת־קׇרְבָּנ֛וֹ}

\item Lev 4:28\hebword{קׇרְבָּנ֜וֹ}

\item Lev 4:32\hebword{קׇרְבָּנ֖וֹ}

\item Lev 5:8\hebword{עׇרְפּ֖וֹ}

\item Lev 5:11\hebword{אֶת־קׇרְבָּנ֜וֹ}

\item Lev 5:15\hebword{מִקׇּדְשֵׁ֖י}

\item Lev 5:23\hebword{הׇפְקַ֖ד}

\subsection{Tzav}

\item Lev 6:10\hebword{קׇֽדָשִׁים֙} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 6:11\hebword{חׇק־עוֹלָם֙}

\item Lev 6:13\hebword{קׇרְבַּן֩}

\item Lev 6:15\hebword{חׇק־עוֹלָ֕ם}

\item Lev 6:15\hebword{תׇּקְטָֽר}

\item Lev 6:18\hebword{קׇֽדָשִׁ֖ים} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 6:22\hebword{קׇֽדָשִׁ֖ים} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 7:1\hebword{קׇֽדָשִׁ֖ים} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 7:6\hebword{קׇֽדָשִׁ֖ים} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 7:13\hebword{קׇרְבָּנ֑וֹ}

\item Lev 7:14\hebword{מִכׇּל־קׇרְבָּ֔ן}

\item Lev 7:15\hebword{קׇרְבָּנ֖וֹ}

\item Lev 7:16\hebword{קׇרְבָּנ֔וֹ}

\item Lev 7:16\hebword{וּמִֽמׇּחֳרָ֔ת} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 7:29\hebword{אֶת־קׇרְבָּנ֛וֹ}

\item Lev 7:34\hebword{לְחׇק־עוֹלָ֔ם}

\item Lev 7:36\hebword{מׇשְׁח֣וֹ}

\item Lev 7:38\hebword{אֶת־קׇרְבְּנֵיהֶ֛ם}

\item Lev 8:24\hebword{אׇזְנָם֙}

\subsection{Shemini}

\item Lev 9:7\hebword{אֶת־קׇרְבַּ֤ן}

\item Lev 9:15\hebword{קׇרְבַּ֣ן}

\item Lev 10:12\hebword{קׇֽדָשִׁ֖ים} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 10:13\hebword{חׇקְךָ֤}

\item Lev 10:13\hebword{וְחׇק־בָּנֶ֙יךָ֙}

\item Lev 10:14\hebword{כִּֽי־חׇקְךָ֤}

\item Lev 10:14\hebword{וְחׇק־בָּנֶ֙יךָ֙}

\item Lev 10:15\hebword{לְחׇק־עוֹלָ֔ם}

\item Lev 10:17\hebword{קׇֽדָשִׁ֖ים} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 11:13\hebword{הָעׇזְנִיָּֽה}

\item Lev 11:22\hebword{וְאֶת־הַסׇּלְעָ֖ם}

\item Lev 11:39\hebword{לְאׇכְלָ֑ה}

\subsection{Tazriaȝ}

\item Lev 12:3\hebword{עׇרְלָתֽוֹ}

\item Lev 12:4\hebword{טׇהֳרָ֑ה} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 12:4\hebword{טׇהֳרָֽהּ} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 12:5\hebword{טׇהֳרָֽה} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 12:6\hebword{טׇהֳרָ֗הּ} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 13:7\hebword{לְטׇהֳרָת֑וֹ} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 13:35\hebword{טׇהֳרָתֽוֹ} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 13:49\hebword{וְהׇרְאָ֖ה}

\subsection{Metzoraȝ}

\item Lev 14:2\hebword{טׇהֳרָת֑וֹ} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 14:8\hebword{לְאׇהֳל֖וֹ} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 14:13\hebword{קׇֽדָשִׁ֖ים} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 14:23\hebword{לְטׇהֳרָת֖וֹ} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 14:32\hebword{בְּטׇהֳרָתֽוֹ} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 15:13\hebword{לְטׇהֳרָת֖וֹ} This kamatz katan is subject to debate between experts and reading traditions.


\item Lev 15:23\hebword{בְּנׇגְעוֹ־ב֑וֹ}

\item Lev 15:32\hebword{לְטׇמְאָה־בָֽהּ}

\subsection{A\d{h}arei-mot}

\item Lev 16:1\hebword{בְּקׇרְבָתָ֥ם}

\item Lev 16:10\hebword{יׇֽעֳמַד־חַ֛י} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 16:12\hebword{חׇפְנָ֔יו}

\item Lev 17:4\hebword{קׇרְבָּן֙}

\item Lev 18:20\hebword{שְׁכׇבְתְּךָ֖}

\item Lev 18:20\hebword{לְטׇמְאָה־בָֽהּ}

\item Lev 18:23\hebword{שְׁכׇבְתְּךָ֖}

\item Lev 18:23\hebword{לְטׇמְאָה־בָ֑הּ}

\subsection{Kedoshim}

\item Lev 19:6\hebword{וּמִֽמׇּחֳרָ֑ת} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 19:20\hebword{וְהׇפְדֵּה֙}

\item Lev 19:23\hebword{עׇרְלָת֖וֹ}

\item Lev 19:31\hebword{לְטׇמְאָ֣ה}

\item Lev 20:3\hebword{קׇדְשִֽׁי}

\item Lev 20:15\hebword{שְׁכׇבְתּ֛וֹ}

\subsection{'Emor}

\item Lev 21:5\hebword{קׇרְחָה֙}

\item Lev 21:22\hebword{מִקׇּדְשֵׁ֖י}

\item Lev 22:2\hebword{מִקׇּדְשֵׁ֣י}

\item Lev 22:2\hebword{קׇדְשִׁ֑י}

\item Lev 22:8\hebword{לְטׇמְאָה־בָ֑הּ}

\item Lev 22:15\hebword{אֶת־קׇדְשֵׁ֖י}

\item Lev 22:16\hebword{בְּאׇכְלָ֖ם}

\item Lev 22:16\hebword{אֶת־קׇדְשֵׁיהֶ֑ם}

\item Lev 22:18\hebword{קׇרְבָּנוֹ֙}

\item Lev 22:25\hebword{מׇשְׁחָתָ֤ם}

\item Lev 22:27\hebword{לְקׇרְבַּ֥ן}

\item Lev 22:32\hebword{קׇדְשִׁ֔י}

\item Lev 23:11\hebword{מִֽמׇּחֳרַת֙} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 23:14\hebword{אֶת־קׇרְבַּ֖ן}

\item Lev 23:15\hebword{מִמׇּחֳרַ֣ת} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 23:16\hebword{מִֽמׇּחֳרַ֤ת} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 23:39\hebword{בְּאׇסְפְּכֶם֙}

\item Lev 24:9\hebword{קׇֽדָשִׁ֨ים} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 24:9\hebword{חׇק־עוֹלָֽם}

\item Lev 24:16\hebword{בְּנׇקְבוֹ־שֵׁ֖ם}

\subsection{Behar}

\item Lev 25:6\hebword{לְאׇכְלָ֔ה}

\item Lev 25:15\hebword{יִמְכׇּר־לָֽךְ}

\item Lev 25:37\hebword{אׇכְלֶֽךָ}

\subsection{Be\d{h}ukotai}

\item Lev 26:31\hebword{חׇרְבָּ֔ה}

\item Lev 26:33\hebword{חׇרְבָּֽה}

\item Lev 26:34\hebword{הׇשַּׁמָּ֔ה}

\item Lev 26:43\hebword{בׇּהְשַׁמָּה֙}

\item Lev 27:9\hebword{קׇרְבָּ֖ן}

\item Lev 27:11\hebword{קׇרְבָּ֖ן}

\item Lev 27:28\hebword{קֹֽדֶשׁ־קׇדָשִׁ֥ים} This kamatz katan is subject to debate between experts and reading traditions.

\item Lev 27:28\hebword{קֹֽדֶשׁ־קׇֽדָשִׁ֥ים}

\item Lev 27:29\hebword{יׇחֳרַ֛ם} This kamatz katan is subject to debate between experts and reading traditions.
\end{itemize}\end{multicols}
\section{Numbers}
\begin{multicols}{2}\begin{itemize}
\item Num 1:13\hebword{בֶּן־עׇכְרָֽן}

\item Num 1:47\hebword{הׇתְפָּקְד֖וּ}

\item Num 2:27\hebword{בֶּן־עׇכְרָֽן}

\item Num 2:33\hebword{הׇתְפָּקְד֔וּ}

\item Num 3:4\hebword{וַיָּ֣מׇת}

\item Num 3:27\hebword{הָעׇזִּֽיאֵלִ֑י}

\subsection{Naso}

\item Num 5:9\hebword{לְכׇל־קׇדְשֵׁ֧י}

\item Num 5:15\hebword{אֶת־קׇרְבָּנָהּ֙}

\item Num 5:20\hebword{אֶת־שְׁכׇבְתּ֔וֹ}

\item Num 6:9\hebword{טׇהֳרָת֔וֹ} This kamatz katan is subject to debate between experts and reading traditions.

\item Num 6:14\hebword{אֶת־קׇרְבָּנ֣וֹ}

\item Num 6:21\hebword{קׇרְבָּנ֤וֹ}

\item Num 7:3\hebword{אֶת־קׇרְבָּנָ֜ם}

\item Num 7:10\hebword{אֶת־קׇרְבָּנָ֖ם}

\item Num 7:11\hebword{אֶת־קׇרְבָּנָ֔ם}

\item Num 7:12\hebword{אֶת־קׇרְבָּנ֑וֹ}

\item Num 7:13\hebword{וְקׇרְבָּנ֞וֹ}

\item Num 7:17\hebword{קׇרְבַּ֥ן}

\item Num 7:19\hebword{אֶת־קׇרְבָּנ֜וֹ}

\item Num 7:23\hebword{קׇרְבַּ֥ן}

\item Num 7:25\hebword{קׇרְבָּנ֞וֹ}

\item Num 7:29\hebword{קׇרְבַּ֥ן}

\item Num 7:31\hebword{קׇרְבָּנ֞וֹ}

\item Num 7:35\hebword{קׇרְבַּ֥ן}

\item Num 7:37\hebword{קׇרְבָּנ֞וֹ}

\item Num 7:41\hebword{קׇרְבַּ֥ן}

\item Num 7:43\hebword{קׇרְבָּנ֞וֹ}

\item Num 7:47\hebword{קׇרְבַּ֥ן}

\item Num 7:49\hebword{קׇרְבָּנ֞וֹ}

\item Num 7:53\hebword{קׇרְבַּ֥ן}

\item Num 7:55\hebword{קׇרְבָּנ֞וֹ}

\item Num 7:59\hebword{קׇרְבַּ֥ן}

\item Num 7:61\hebword{קׇרְבָּנ֞וֹ}

\item Num 7:65\hebword{קׇרְבַּ֥ן}

\item Num 7:67\hebword{קׇרְבָּנ֞וֹ}

\item Num 7:71\hebword{קׇרְבַּ֥ן}

\item Num 7:72\hebword{בֶּן־עׇכְרָֽן}

\item Num 7:73\hebword{קׇרְבָּנ֞וֹ}

\item Num 7:77\hebword{קׇרְבַּ֥ן}

\item Num 7:77\hebword{בֶּן־עׇכְרָֽן}

\item Num 7:79\hebword{קׇרְבָּנ֞וֹ}

\item Num 7:83\hebword{קׇרְבַּ֥ן}

\subsection{Behaȝalotekha}

\item Num 9:7\hebword{אֶת־קׇרְבַּ֤ן}

\item Num 9:13\hebword{קׇרְבַּ֣ן}

\item Num 9:17\hebword{יִשְׁכׇּן־שָׁם֙}

\item Num 10:10\hebword{חׇדְשֵׁיכֶם֒}

\item Num 10:10\hebword{חׇדְשֵׁכֶם֒}

\item Num 10:26\hebword{בֶּן־עׇכְרָֽן}

\item Num 10:34\hebword{בְּנׇסְעָ֖ם}

\item Num 11:1\hebword{בְּאׇזְנֵ֣י}

\item Num 11:10\hebword{אׇהֳל֑וֹ} This kamatz katan is subject to debate between experts and reading traditions.

\item Num 11:15\hebword{הׇרְגֵ֤נִי}

\item Num 11:18\hebword{בְּאׇזְנֵ֨י}

\item Num 11:27\hebword{וַיָּ֣רׇץ}

\item Num 11:31\hebword{וַיָּ֣גׇז}

\item Num 11:32\hebword{וַיָּ֣קׇם}

\item Num 11:32\hebword{הַֽמׇּחֳרָ֗ת} This kamatz katan is subject to debate between experts and reading traditions.

\item Num 12:4\hebword{שְׁלׇשְׁתְּכֶ֖ם}

\item Num 12:4\hebword{שְׁלׇשְׁתָּֽם}

\subsection{Shela\d{h}-lekha}

\item Num 13:14\hebword{בֶּן־וׇפְסִֽי}

\item Num 14:28\hebword{בְּאׇזְנָ֑י}

\item Num 14:45\hebword{עַד־הַֽחׇרְמָֽה}

\item Num 15:4\hebword{קׇרְבָּנ֖וֹ}

\item Num 15:25\hebword{אֶת־קׇרְבָּנָ֜ם}

\subsection{Kora\d{h}}

\item Num 16:25\hebword{וַיָּ֣קׇם}

\item Num 16:26\hebword{אׇהֳלֵ֨י} This kamatz katan is subject to debate between experts and reading traditions.

\item Num 16:27\hebword{אׇֽהֳלֵיהֶ֔ם} This kamatz katan is subject to debate between experts and reading traditions.

\item Num 17:6\hebword{מִֽמׇּחֳרָ֔ת} This kamatz katan is subject to debate between experts and reading traditions.

\item Num 17:12\hebword{וַיָּ֙רׇץ֙}

\item Num 17:15\hebword{וַיָּ֤שׇׁב}

\item Num 17:23\hebword{מִֽמׇּחֳרָ֗ת} This kamatz katan is subject to debate between experts and reading traditions.

\item Num 18:8\hebword{לְכׇל־קׇדְשֵׁ֣י}

\item Num 18:8\hebword{לְמׇשְׁחָ֛ה}

\item Num 18:8\hebword{לְחׇק־עוֹלָֽם}

\item Num 18:9\hebword{כׇּל־קׇ֠רְבָּנָ֠ם}

\item Num 18:9\hebword{קׇֽדָשִׁ֥ים} This kamatz katan is subject to debate between experts and reading traditions.

\item Num 18:11\hebword{לְחׇק־עוֹלָ֑ם}

\item Num 18:19\hebword{לְחׇק־עוֹלָ֑ם}

\item Num 18:32\hebword{וְאֶת־קׇדְשֵׁ֧י}

\subsection{\d{H}ukkat}

\item Num 20:1\hebword{וַתָּ֤מׇת}

\item Num 20:28\hebword{וַיָּ֧מׇת}

\item Num 21:3\hebword{חׇרְמָֽה}

\item Num 21:6\hebword{וַיָּ֥מׇת}

\subsection{Balak}

\item Num 22:3\hebword{וַיָּ֨גׇר}

\item Num 22:3\hebword{וַיָּ֣קׇץ}

\item Num 22:13\hebword{וַיָּ֤קׇם}

\item Num 22:21\hebword{וַיָּ֤קׇם}

\item Num 23:6\hebword{וַיָּ֣שׇׁב}

\item Num 23:13\hebword{וְקׇבְנוֹ־לִ֖י}

\item Num 24:25\hebword{וַיָּ֣קׇם}

\item Num 24:25\hebword{וַיָּ֣שׇׁב}

\item Num 25:7\hebword{וַיָּ֙קׇם֙}

\subsection{Pin\d{h}as}

\item Num 25:15\hebword{כׇּזְבִּ֣י}

\item Num 25:18\hebword{כׇּזְבִּ֨י}

\item Num 26:16\hebword{לְאׇזְנִ֕י}

\item Num 26:16\hebword{הָאׇזְנִ֑י}

\item Num 26:19\hebword{וַיָּ֥מׇת}

\item Num 26:33\hebword{וּצְלׇפְחָ֣ד}

\item Num 26:33\hebword{צְלׇפְחָ֔ד}

\item Num 26:33\hebword{חׇגְלָ֥ה}

\item Num 26:58\hebword{הַקׇּרְחִ֑י}

\item Num 26:61\hebword{וַיָּ֥מׇת}

\item Num 26:62\hebword{הׇתְפָּקְד֗וּ}

\item Num 27:1\hebword{צְלׇפְחָ֗ד}

\item Num 27:1\hebword{וְחׇגְלָ֥ה}

\item Num 27:7\hebword{צְלׇפְחָד֮}

\item Num 28:2\hebword{אֶת־קׇרְבָּנִ֨י}

\item Num 28:11\hebword{חׇדְשֵׁיכֶ֔ם}

\item Num 28:14\hebword{בְּחׇדְשׁ֔וֹ}

\item Num 28:14\hebword{לְחׇדְשֵׁ֖י}

\subsection{Mattot}

\item Num 30:6\hebword{שׇׁמְעוֹ֒}

\item Num 30:8\hebword{שׇׁמְע֖וֹ}

\item Num 30:13\hebword{שׇׁמְעוֹ֒}

\item Num 30:15\hebword{שׇׁמְעֽוֹ}

\item Num 30:16\hebword{שׇׁמְע֑וֹ}

\item Num 31:16\hebword{לִמְסׇר־מַ֥עַל}

\item Num 31:50\hebword{אֶת־קׇרְבַּ֣ן}

\item Num 32:8\hebword{בְּשׇׁלְחִ֥י}

\item Num 32:35\hebword{וְיׇגְבְּהָֽה}

\subsection{Masȝei}

\item Num 33:3\hebword{מִֽמׇּחֳרַ֣ת} This kamatz katan is subject to debate between experts and reading traditions.

\item Num 33:7\hebword{וַיָּ֙שׇׁב֙}

\item Num 33:12\hebword{בְּדׇפְקָֽה}

\item Num 33:13\hebword{מִדׇּפְקָ֑ה}

\item Num 33:33\hebword{בְּיׇטְבָֽתָה}

\item Num 33:34\hebword{מִיׇּטְבָ֑תָה}

\item Num 33:38\hebword{וַיָּ֣מׇת}

\item Num 34:22\hebword{בֶּן־יׇגְלִֽי}

\item Num 35:12\hebword{עַד־עׇמְד֛וֹ}

\item Num 36:2\hebword{צְלׇפְחָ֥ד}

\item Num 36:6\hebword{צְלׇפְחָד֙}

\item Num 36:10\hebword{צְלׇפְחָֽד}

\item Num 36:11\hebword{וְחׇגְלָ֧ה}

\item Num 36:11\hebword{צְלׇפְחָ֑ד}
\end{itemize}\end{multicols}
\section{Deuteronomy}
\begin{multicols}{2}\begin{itemize}
\item Deut 1:12\hebword{טׇרְחֲכֶ֥ם}

\item Deut 1:27\hebword{בְאׇהֳלֵיכֶם֙} This kamatz katan is subject to debate between experts and reading traditions.

\item Deut 1:44\hebword{עַד־חׇרְמָֽה}

\item Deut 2:1\hebword{וַנָּ֥סׇב}

\item Deut 3:11\hebword{אׇרְכָּ֗הּ}

\item Deut 3:11\hebword{רׇחְבָּ֖הּ}

\subsection{Va'et\d{h}anan}

\item Deut 3:24\hebword{אֶ֨ת־גׇּדְלְךָ֔}

\item Deut 4:6\hebword{חׇכְמַתְכֶם֙}

\item Deut 4:21\hebword{עׇבְרִי֙}

\item Deut 4:35\hebword{הׇרְאֵ֣תָ}

\item Deut 5:1\hebword{בְּאׇזְנֵיכֶ֖ם}

\item Deut 5:8\hebword{תָעׇבְדֵ֑ם֒}

\item Deut 5:19\hebword{כְּשׇׁמְעֲכֶ֤ם}

\item Deut 5:20\hebword{וְאֶת־גׇּדְל֔וֹ}

\item Deut 5:26\hebword{לְאׇהֳלֵיכֶֽם} This kamatz katan is subject to debate between experts and reading traditions.

\item Deut 6:7\hebword{וּֽבְשׇׁכְבְּךָ֖}

\item Deut 6:20\hebword{כִּֽי־יִשְׁאׇלְךָ֥} This kamatz katan is subject to debate between experts and reading traditions.

\item Deut 7:2\hebword{תְחׇנֵּֽם}

\item Deut 7:8\hebword{וּמִשׇּׁמְר֤וֹ}

\subsection{Ȝekev}

\item Deut 9:26\hebword{בְּגׇדְלֶ֑ךָ}

\item Deut 10:1\hebword{פְּסׇל־לְךָ֞}

\item Deut 10:7\hebword{יׇטְבָ֔תָה}

\item Deut 10:16\hebword{עׇרְלַ֣ת}

\item Deut 10:16\hebword{וְעׇ֨רְפְּכֶ֔ם}

\item Deut 11:2\hebword{אֶת־גׇּדְל֕וֹ}

\item Deut 11:4\hebword{בְּרׇדְפָ֖ם}

\item Deut 11:6\hebword{וְאֶת־אׇהֳלֵיהֶ֑ם} This kamatz katan is subject to debate between experts and reading traditions.

\item Deut 11:13\hebword{וּלְעׇבְד֔וֹ}

\item Deut 11:19\hebword{וּֽבְשׇׁכְבְּךָ֖}

\item Deut 11:22\hebword{וּלְדׇבְקָה־בֽוֹ}

\subsection{Re'eh}

\item Deut 12:26\hebword{קׇֽדָשֶׁ֛יךָ} This kamatz katan is subject to debate between experts and reading traditions.

\item Deut 13:3\hebword{וְנׇֽעׇבְדֵֽם} This kamatz katan is subject to debate between experts and reading traditions.

\item Deut 14:1\hebword{קׇרְחָ֛ה}

\item Deut 14:12\hebword{וְהָֽעׇזְנִיָּֽה}

\item Deut 14:21\hebword{לְנׇכְרִ֔י}

\item Deut 14:26\hebword{תִּֽשְׁאׇלְךָ֖} This kamatz katan is subject to debate between experts and reading traditions.

\item Deut 15:3\hebword{אֶת־הַנׇּכְרִ֖י}

\item Deut 15:12\hebword{חׇפְשִׁ֖י}

\item Deut 15:13\hebword{חׇפְשִׁ֖י}

\item Deut 15:14\hebword{וּמִֽגׇּרְנְךָ֖}

\item Deut 15:17\hebword{בְאׇזְנוֹ֙}

\item Deut 15:18\hebword{חׇפְשִׁי֙}

\item Deut 16:9\hebword{תִּסְפׇּר־לָ֑ךְ}

\item Deut 16:13\hebword{בְּאׇ֨סְפְּךָ֔}

\item Deut 16:13\hebword{מִֽגׇּרְנְךָ֖}

\subsection{Shofetim}

\item Deut 17:15\hebword{נׇכְרִ֔י}

\item Deut 20:2\hebword{כְּקָֽרׇבְכֶ֖ם}

\item Deut 20:19\hebword{לְתׇפְשָׂ֗הּ}

\subsection{Ki-tetzei}

\item Deut 21:12\hebword{אֶת־צִפׇּרְנֶֽיהָ}

\item Deut 23:2\hebword{שׇׁפְכָ֖ה}

\item Deut 23:21\hebword{לַנׇּכְרִ֣י}

\item Deut 23:25\hebword{שׇׂבְעֶ֑ךָ}

\subsection{Ki-tavo}

\item Deut 26:5\hebword{וַיָּ֥גׇר}

\item Deut 26:7\hebword{אֶת־עׇנְיֵ֛נוּ}

\item Deut 26:15\hebword{קׇדְשְׁךָ֜}

\item Deut 27:3\hebword{בְּעׇבְרֶ֑ךָ}

\item Deut 27:4\hebword{בְּעׇבְרְכֶ֣ם}

\item Deut 27:12\hebword{בְּעׇבְרְכֶ֖ם}

\item Deut 28:14\hebword{לְעׇבְדָֽם}

\item Deut 28:20\hebword{וְעַד־אֲבׇדְךָ֙}

\item Deut 28:22\hebword{אׇבְדֶֽךָ}

\item Deut 28:29\hebword{בַּֽצׇּהֳרַ֗יִם} This kamatz katan is subject to debate between experts and reading traditions.

\item Deut 28:35\hebword{קׇדְקֳדֶֽךָ}

\item Deut 28:59\hebword{וׇחֳלָיִ} This kamatz katan is subject to debate between experts and reading traditions.

\item Deut 28:68\hebword{בׇּאֳנִיּוֹת֒} This kamatz katan is subject to debate between experts and reading traditions.

\item Deut 29:3\hebword{וְאׇזְנַ֣יִם}

\subsection{Nitzavim}

\item Deut 29:11\hebword{לְעׇבְרְךָ֗}

\item Deut 29:18\hebword{בְּשׇׁמְעוֹ֩}

\item Deut 29:21\hebword{וְהַ֨נׇּכְרִ֔י}

\item Deut 29:22\hebword{גׇּפְרִ֣ית}

\item Deut 30:13\hebword{יַעֲבׇר־לָ֜נוּ}

\item Deut 30:20\hebword{וּלְדׇבְקָה־ב֑וֹ}

\subsection{Vayelekh}

\item Deut 31:11\hebword{בְּאׇזְנֵיהֶֽם}

\item Deut 31:27\hebword{וְאֶֽת־עׇרְפְּךָ֖}

\item Deut 31:28\hebword{בְאׇזְנֵיהֶ֗ם}

\item Deut 31:30\hebword{בְּאׇזְנֵי֙}

\subsection{Ha'azinu}

\item Deut 32:4\hebword{פׇּֽעֳל֔וֹ} This kamatz katan is subject to debate between experts and reading traditions.

\item Deut 32:44\hebword{בְּאׇזְנֵ֣י}

\subsection{Vezot Haberakha}

\item Deut 33:11\hebword{מׇתְנַ֧יִם}

\item Deut 33:16\hebword{וּלְקׇדְקֹ֖ד}

\item Deut 33:20\hebword{אַף־קׇדְקֹֽד}

\item Deut 33:25\hebword{דׇּבְאֶֽךָ}

\item Deut 34:5\hebword{וַיָּ֨מׇת}

\item Deut 34:9\hebword{חׇכְמָ֔ה}

\end{itemize}
\end{multicols}

\chapter{The Prophets}

\section{Former Prophets}

\subsection{Joshua}

\begin{multicols}{2}
\begin{itemize} \item Josh 3:14\hebword{מֵאׇ֣הֳלֵיהֶ֔ם} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Josh 4:7\hebword{בְּעׇבְרוֹ֙}
	
	\item Josh 4:10\hebword{כׇּֽל־הַ֠דָּבָ֠ר}
	
	\item Josh 4:23\hebword{עַֽד־עׇבְרְכֶ֑ם}
	
	\item Josh 4:23\hebword{עַד־עׇבְרֵֽנוּ}
	
	\item Josh 5:3\hebword{וַיָּ֙מׇל֙}
	
	\item Josh 5:11\hebword{מִמׇּחֳרַ֥ת} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Josh 5:12\hebword{מִֽמׇּחֳרָ֗ת} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Josh 5:12\hebword{בְּאׇכְלָם֙}
	
	\item Josh 6:5\hebword{כְּשׇׁמְעֲכֶם֙}
	
	\item Josh 6:10\hebword{אׇמְרִ֧י}
	
	\item Josh 6:27\hebword{שׇׁמְע֖וֹ}
	
	\item Josh 7:20\hebword{אׇמְנָ֗ה}
	
	\item Josh 7:21\hebword{הָאׇהֳלִ֖י} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Josh 7:22\hebword{בְּאׇהֳל֖וֹ} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Josh 7:24\hebword{וְאֶֽת־אׇהֳלוֹ֙} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Josh 7:25\hebword{יַעְכׇּרְךָ֥}
	
	\item Josh 7:26\hebword{וַיָּ֥שׇׁב}
	
	\item Josh 8:3\hebword{וַיָּ֧קׇם}
	
	\item Josh 8:8\hebword{כְּתׇפְשְׂכֶ֣ם|}
			
			\item Josh 8:8\hebword{בְּתׇפְשְׂכֶ֣ם}
			
			\item Josh 8:32\hebword{וַיִּכְתׇּב־שָׁ֖ם}
			
			\item Josh 9:1\hebword{כׇּֽל־הַמְּלָכִ֡ים}
			
			\item Josh 9:4\hebword{בְּעׇרְמָ֔ה}
			
			\item Josh 9:9\hebword{שׇׁמְע֔וֹ}
			
			\item Josh 10:6\hebword{וְעׇזְרֵ֔נוּ}
			
			\item Josh 10:15\hebword{וַיָּ֤שׇׁב}
			
			\item Josh 10:18\hebword{לְשׇׁמְרָֽם}
			
			\item Josh 10:29\hebword{וְכׇֽל־יִשְׂרָאֵ֥ל}
			
			\item Josh 10:31\hebword{וְכׇֽל־יִשְׂרָאֵ֥ל}
			
			\item Josh 10:34\hebword{וְכׇֽל־יִשְׂרָאֵ֥ל}
			
			\item Josh 10:36\hebword{וְכׇֽל־יִשְׂרָאֵ֥ל}
			
			\item Josh 10:38\hebword{וַיָּ֧שׇׁב}
			
			\item Josh 10:43\hebword{וַיָּ֤שׇׁב}
			
			\item Josh 11:10\hebword{וַיָּ֨שׇׁב}
			
			\item Josh 12:14\hebword{חׇרְמָה֙}
			
			\item Josh 12:22\hebword{מֶלֶךְ־יׇקְנְעָ֥ם}
			
			\item Josh 13:21\hebword{וְכׇֽל־מַמְלְכ֗וּת}
			
			\item Josh 13:30\hebword{כׇּֽל־הַבָּשָׁ֜ן}
			
			\item Josh 13:30\hebword{כׇּֽל־מַמְלְכ֣וּת}
			
			\item Josh 15:6\hebword{חׇגְלָ֔ה}
			
			\item Josh 15:17\hebword{עׇתְנִיאֵ֥ל}
			
			\item Josh 15:30\hebword{וְחׇרְמָֽה}
			
			\item Josh 15:33\hebword{וְצׇרְעָ֖ה}
			
			\item Josh 15:38\hebword{וְיׇקְתְאֵֽל}
			
			\item Josh 15:39\hebword{וּבׇצְקַ֖ת}
			
			\item Josh 15:56\hebword{וְיׇקְדְעָ֖ם}
			
			\item Josh 17:3\hebword{וְלִצְלׇפְחָד֩}
			
			\item Josh 17:3\hebword{חׇגְלָ֥ה}
			
			\item Josh 18:19\hebword{בֵּית־חׇגְלָה֮}
			
			\item Josh 18:21\hebword{וּבֵית־חׇגְלָ֖ה}
			
			\item Josh 18:23\hebword{וְעׇפְרָֽה}
			
			\item Josh 18:24\hebword{וְהָעׇפְנִ֖י}
			
			\item Josh 19:4\hebword{וְחׇרְמָֽה}
			
			\item Josh 19:11\hebword{יׇקְנְעָֽם}
			
			\item Josh 19:41\hebword{צׇרְעָ֥ה}
			
			\item Josh 20:4\hebword{בְּאׇזְנֵ֛י}
			
			\item Josh 20:6\hebword{עַד־עׇמְד֞וֹ}
			
			\item Josh 20:9\hebword{עַד־עׇמְד֖וֹ}
			
			\item Josh 21:34\hebword{אֶֽת־יׇקְנְעָ֖ם}
			
			\item Josh 22:4\hebword{לְאׇהֳלֵיכֶ֗ם} This kamatz katan is subject to debate between experts and reading traditions.
			
			\item Josh 22:5\hebword{וּלְדׇבְקָה־ב֑וֹ}
			
			\item Josh 22:5\hebword{וּלְעׇבְד֕וֹ}
			
			\item Josh 22:6\hebword{אֶל־אׇהֳלֵיהֶֽם} This kamatz katan is subject to debate between experts and reading traditions.
			
			\item Josh 22:7\hebword{אֶל־אׇהֳלֵיהֶ֖ם} This kamatz katan is subject to debate between experts and reading traditions.
			
			\item Josh 22:8\hebword{אֶל־אׇֽהֳלֵיכֶם֙} This kamatz katan is subject to debate between experts and reading traditions.
			
			\item Josh 22:16\hebword{לִמְרׇדְכֶ֥ם}
			
			\item Josh 22:32\hebword{וַיָּ֣שׇׁב}
			
			\item Josh 23:10\hebword{יִרְדׇּף־אָ֑לֶף}
			
			\item Josh 23:13\hebword{עַד־אֲבׇדְכֶ֗ם}
			
			\item Josh 23:16\hebword{בְּ֠עׇבְרְכֶ֠ם}
			
			\item Josh 24:9\hebword{וַיָּ֨קׇם}
			
			\item Josh 24:29\hebword{וַיָּ֛מׇת}
			
			\end{itemize}\end{multicols}
		
		\subsection{Judges}
		
		\begin{multicols}{2}\begin{itemize}
			
			\item Judges 1:6\hebword{וַיָּ֙נׇס֙}
			
			\item Judges 1:7\hebword{וַיָּ֥מׇת}
			
			\item Judges 1:13\hebword{עׇתְנִיאֵ֣ל}
			
			\item Judges 1:17\hebword{חׇרְמָֽה}
			
			\item Judges 2:8\hebword{וַיָּ֛מׇת}
			
			\item Judges 2:10\hebword{וַיָּ֩קׇם֩}
			
			\item Judges 2:19\hebword{לְעׇבְדָ֖ם}
			
			\item Judges 3:9\hebword{עׇתְנִיאֵ֣ל}
			
			\item Judges 3:10\hebword{וַתָּ֣עׇז}
			
			\item Judges 3:11\hebword{וַיָּ֖מׇת}
			
			\item Judges 3:11\hebword{עׇתְנִיאֵ֥ל}
			
			\item Judges 3:16\hebword{אׇרְכָּ֑הּ}
			
			\item Judges 3:20\hebword{וַיָּ֖קׇם}
			
			\item Judges 4:3\hebword{בְּחׇזְקָ֖ה}
			
			\item Judges 4:9\hebword{וַתָּ֧קׇם}
			
			\item Judges 4:11\hebword{אׇֽהֳל֔וֹ} This kamatz katan is subject to debate between experts and reading traditions.
			
			\item Judges 4:15\hebword{וַיָּ֣הׇם}
			
			\item Judges 4:15\hebword{וַיָּ֥נׇס}
			
			\item Judges 5:14\hebword{שׇׁרְשָׁם֙}
			
			\item Judges 6:2\hebword{וַתָּ֥עׇז}
			
			\item Judges 6:5\hebword{וְאׇהֳלֵיהֶ֗ם} This kamatz katan is subject to debate between experts and reading traditions.
			
			\item Judges 6:11\hebword{בְּעׇפְרָ֔ה}
			
			\item Judges 6:13\hebword{כׇֽל־נִפְלְאֹתָ֡יו}
			
			\item Judges 6:24\hebword{בְּעׇפְרָ֖ת}
			
			\item Judges 6:38\hebword{מִֽמׇּחֳרָ֔ת} This kamatz katan is subject to debate between experts and reading traditions.
			
			\item Judges 7:3\hebword{בְּאׇזְנֵ֤י}
			
			\item Judges 7:3\hebword{וַיָּ֣שׇׁב}
			
			\item Judges 7:15\hebword{וַיָּ֙שׇׁב֙}
			
			\item Judges 7:21\hebword{וַיָּ֧רׇץ}
			
			\item Judges 7:22\hebword{וַיָּ֨נׇס}
			
			\item Judges 8:1\hebword{בְּחׇזְקָֽה}
			
			\item Judges 8:11\hebword{בׇאֳהָלִ֔ים} This kamatz katan is subject to debate between experts and reading traditions.
			
			\item Judges 8:11\hebword{וְיׇגְבְּהָ֑ה}
			
			\item Judges 8:13\hebword{וַיָּ֛שׇׁב}
			
			\item Judges 8:14\hebword{וַיִּלְכׇּד־נַ֛עַר}
			
			\item Judges 8:21\hebword{וַיָּ֣קׇם}
			
			\item Judges 8:27\hebword{בְּעׇפְרָ֔ה}
			
			\item Judges 8:32\hebword{וַיָּ֛מׇת}
			
			\item Judges 8:32\hebword{בְּעׇפְרָ֖ה}
			
			\item Judges 9:2\hebword{בְּאׇזְנֵ֨י}
			
			\item Judges 9:3\hebword{בְּאׇזְנֵי֙}
			
			\item Judges 9:5\hebword{עׇפְרָ֔תָה}
			
			\item Judges 9:8\hebword{מׇלְכָ֥ה}
			
			\item Judges 9:10\hebword{מׇלְכִ֥י}
			
			\item Judges 9:11\hebword{אֶת־מׇתְקִ֔י}
			
			\item Judges 9:14\hebword{מְלׇךְ־עָלֵֽינוּ}
			
			\item Judges 9:21\hebword{וַיָּ֣נׇס}
			
			\item Judges 9:31\hebword{בְּתׇרְמָ֣ה}
			
			\item Judges 9:34\hebword{וַיָּ֧קׇם}
			
			\item Judges 9:35\hebword{וַיָּ֧קׇם}
			
			\item Judges 9:40\hebword{וַיָּ֖נׇס}
			
			\item Judges 9:42\hebword{מִֽמׇּחֳרָ֔ת} This kamatz katan is subject to debate between experts and reading traditions.
			
			\item Judges 9:43\hebword{וַיָּ֥קׇם}
			
			\item Judges 9:52\hebword{לְשׇׂרְפ֥וֹ}
			
			\item Judges 9:53\hebword{אֶת־גֻּלְגׇּלְתּֽוֹ}
			
			\item Judges 10:1\hebword{וַיָּ֩קׇם֩}
			
			\item Judges 10:2\hebword{וַיָּ֖מׇת}
			
			\item Judges 10:3\hebword{וַיָּ֣קׇם}
			
			\item Judges 10:5\hebword{וַיָּ֣מׇת}
			
			\item Judges 11:18\hebword{וַיָּ֜סׇב}
			
			\item Judges 11:39\hebword{וַתָּ֙שׇׁב֙}
			
			\item Judges 12:7\hebword{וַיָּ֗מׇת}
			
			\item Judges 12:10\hebword{וַיָּ֣מׇת}
			
			\item Judges 12:12\hebword{וַיָּ֖מׇת}
			
			\item Judges 12:15\hebword{וַיָּ֛מׇת}
			
			\item Judges 13:2\hebword{מִצׇּרְעָ֛ה}
			
			\item Judges 13:10\hebword{וַתָּ֖רׇץ}
			
			\item Judges 13:11\hebword{וַיָּ֛קׇם}
			
			\item Judges 13:25\hebword{צׇרְעָ֖ה}
			
			\item Judges 14:8\hebword{וַיָּ֤שׇׁב}
			
			\item Judges 14:15\hebword{הַלְיׇרְשֵׁ֕נוּ}
			
			\item Judges 15:12\hebword{לֶאֱסׇרְךָ֣}
			
			\item Judges 15:13\hebword{נֶאֱסׇרְךָ֙}
			
			\item Judges 15:19\hebword{וַתָּ֥שׇׁב}
			
			\item Judges 16:3\hebword{וַיָּ֣קׇם}
			
			\item Judges 16:28\hebword{זׇכְרֵ֣נִי}
			
			\item Judges 16:31\hebword{צׇרְעָה֙}
			
			\item Judges 17:2\hebword{בְּאׇזְנַ֔י}
			
			\item Judges 18:2\hebword{מִצׇּרְעָ֣ה}
			
			\item Judges 18:2\hebword{וּלְחׇקְרָ֔הּ}
			
			\item Judges 18:8\hebword{צׇרְעָ֖ה}
			
			\item Judges 18:11\hebword{מִצׇּרְעָ֖ה}
			
			\item Judges 18:26\hebword{וַיָּ֥שׇׁב}
			
			\item Judges 19:3\hebword{וַיָּ֨קׇם}
			
			\item Judges 19:5\hebword{וַיָּ֣קׇם}
			
			\item Judges 19:7\hebword{וַיָּ֥קׇם}
			
			\item Judges 19:7\hebword{וַיָּ֖שׇׁב}
			
			\item Judges 19:8\hebword{סְעׇד־נָא֙}
			
			\item Judges 19:9\hebword{וַיָּ֤קׇם}
			
			\item Judges 19:10\hebword{וַיָּ֣קׇם}
			
			\item Judges 19:12\hebword{נׇכְרִ֔י}
			
			\item Judges 19:21\hebword{וַיָּ֖בׇל}
					
			\item Judges 19:27\hebword{וַיָּ֨קׇם}
					
			\item Judges 19:28\hebword{וַיָּ֣קׇם}
					
			\item Judges 20:8\hebword{וַיָּ֙קׇם֙}
					
			\item Judges 20:8\hebword{לְאׇהֳל֔וֹ} This kamatz katan is subject to debate between experts and reading traditions.
					
			\item Judges 20:31\hebword{הׇנְתְּק֖וּ}
					
			\item Judges 21:4\hebword{מִֽמׇּחֳרָ֔ת} This kamatz katan is subject to debate between experts and reading traditions.
					
			\item Judges 21:14\hebword{וַיָּ֤שׇׁב}
					
	\end{itemize}\end{multicols}
				
	\subsection{Samuel}
		
	\begin{multicols}{2}\begin{itemize}
					
					\item 1Sam 1:3\hebword{חׇפְנִי֙}
					
					\item 1Sam 1:9\hebword{וַתָּ֣קׇם}
					
					\item 1Sam 1:9\hebword{אׇכְלָ֥ה}
					
					\item 1Sam 1:11\hebword{בׇּעֳנִ֣י} This kamatz katan is subject to debate between experts and reading traditions.
					
					\item 1Sam 1:23\hebword{עַד־גׇּמְלֵ֣ךְ}
					
					\item 1Sam 1:23\hebword{עַד־גָּמְלָ֖הּ}
							
							\item 1Sam 2:16\hebword{בְחׇזְקָֽה}
							
							\item 1Sam 2:34\hebword{אֶל־חׇפְנִ֖י}
							
							\item 1Sam 3:5\hebword{וַיָּ֣רׇץ}
							
							\item 1Sam 3:6\hebword{וַיָּ֤קׇם}
							
							\item 1Sam 3:8\hebword{וַיָּ֙קׇם֙}
							
							\item 1Sam 3:11\hebword{אׇזְנָֽיו}
							
							\item 1Sam 4:4\hebword{חׇפְנִ֖י}
							
							\item 1Sam 4:11\hebword{חׇפְנִ֖י}
							
							\item 1Sam 4:12\hebword{וַיָּ֤רׇץ}
							
							\item 1Sam 4:17\hebword{חׇפְנִי֙}
							
							\item 1Sam 5:3\hebword{מִֽמׇּחֳרָ֔ת} This kamatz katan is subject to debate between experts and reading traditions.
							
							\item 1Sam 5:4\hebword{מִֽמׇּחֳרָת֒} This kamatz katan is subject to debate between experts and reading traditions.

							
							\item 1Sam 8:5\hebword{לְשׇׁפְטֵ֖נוּ}
							
							\item 1Sam 8:6\hebword{לְשׇׁפְטֵ֑נוּ}

							\item 1Sam 8:21\hebword{בְּאׇזְנֵ֥י}
	
							\item 1Sam 9:26\hebword{וַיָּ֣קׇם}
							
							\item 1Sam 10:9\hebword{וַיַּהֲפׇךְ־ל֥וֹ}
							
							\item 1Sam 11:1\hebword{כְּרׇת־לָ֥נוּ}
							
							\item 1Sam 11:4\hebword{בְּאׇזְנֵ֣י}
							
							\item 1Sam 11:6\hebword{כְּשׇׁמְע֖וֹ}
							
							\item 1Sam 11:11\hebword{מִֽמׇּחֳרָ֗ת} This kamatz katan is subject to debate between experts and reading traditions.
							
							\item 1Sam 13:1\hebword{בְּמׇלְכ֑וֹ}
							
							\item 1Sam 13:15\hebword{וַיָּ֣קׇם}
							
							\item 1Sam 13:17\hebword{עׇפְרָ֖ה}
							
							\item 1Sam 15:14\hebword{בְּאׇזְנָ֑י}
							
							\item 1Sam 15:31\hebword{וַיָּ֥שׇׁב}
							
							\item 1Sam 16:13\hebword{וַיָּ֣קׇם}
							
							\item 1Sam 17:4\hebword{גׇּלְיָ֥ת}
							
							\item 1Sam 17:4\hebword{גׇּבְה֕וֹ}
							
							\item 1Sam 17:22\hebword{וַיָּ֖רׇץ}
							
							\item 1Sam 17:23\hebword{גׇּלְיָת֩}
							
							\item 1Sam 17:25\hebword{חׇפְשִׁ֖י}
							
							\item 1Sam 17:35\hebword{וַיָּ֣קׇם}
							
							\item 1Sam 17:48\hebword{וַיָּ֥רׇץ}
							
							\item 1Sam 17:51\hebword{וַיָּ֣רׇץ}
							
							\item 1Sam 17:51\hebword{וַיִּכְרׇת־בָּ֖הּ}
							
							\item 1Sam 17:54\hebword{בְּאׇהֳלֽוֹ} This kamatz katan is subject to debate between experts and reading traditions.
							
							\item 1Sam 18:10\hebword{מִֽמׇּחֳרָ֗ת} This kamatz katan is subject to debate between experts and reading traditions.
							
							\item 1Sam 18:15\hebword{וַיָּ֖גׇר}
							
							\item 1Sam 18:23\hebword{בְּאׇזְנֵ֣י}
							
							\item 1Sam 18:25\hebword{עׇרְל֣וֹת}
							
							\item 1Sam 18:27\hebword{וַיָּ֨קׇם}
							
							\item 1Sam 18:27\hebword{אֶת־עׇרְלֹ֣תֵיהֶ֔ם}
							
							\item 1Sam 19:11\hebword{לְשׇׁמְר֔וֹ}
							
							\item 1Sam 20:2\hebword{אֶת־אׇזְנִ֑י}
							
							\item 1Sam 20:12\hebword{אֶת־אׇזְנֶֽךָ}
							
							\item 1Sam 20:13\hebword{אֶת־אׇזְנֶ֔ךָ}
							
							\item 1Sam 20:25\hebword{וַיָּ֙קׇם֙}
							
							\item 1Sam 20:27\hebword{מִֽמׇּחֳרַ֤ת} This kamatz katan is subject to debate between experts and reading traditions.
							
							\item 1Sam 20:30\hebword{לְבׇ֨שְׁתְּךָ֔}
							
							\item 1Sam 20:34\hebword{וַיָּ֧קׇם}
							
							\item 1Sam 20:34\hebword{בׇּחֳרִי־אָ֑ף} This kamatz katan is subject to debate between experts and reading traditions.
							
							\item 1Sam 21:1\hebword{וַיָּ֖קׇם}
							
							\item 1Sam 21:10\hebword{גׇּלְיָ֨ת}
							
							\item 1Sam 21:11\hebword{וַיָּ֣קׇם}
							
							\item 1Sam 22:8\hebword{אֶת־אׇזְנִי֙}
							
							\item 1Sam 22:8\hebword{בִּכְרׇת־בְּנִ֣י}
							
							\item 1Sam 22:8\hebword{אֶת־אׇזְנִ֑י}
							
							\item 1Sam 22:10\hebword{גׇּלְיָ֥ת}
							
							\item 1Sam 23:13\hebword{וַיָּ֩קׇם֩}
							
							\item 1Sam 23:16\hebword{וַיָּ֙קׇם֙}
							
							\item 1Sam 23:26\hebword{לְתׇפְשָֽׂם}
							
							\item 1Sam 23:28\hebword{וַיָּ֣שׇׁב}
							
							\item 1Sam 24:4\hebword{וַיָּ֣קׇם}
							
							\item 1Sam 24:8\hebword{וַיָּ֨קׇם}
							
							\item 1Sam 24:10\hebword{וַתָּ֣חׇס}
							
							\item 1Sam 24:11\hebword{בְּכׇרְתִי֩}
							
							\item 1Sam 25:1\hebword{וַיָּ֣מׇת}
							
							\item 1Sam 25:1\hebword{וַיָּ֣קׇם}
							
							\item 1Sam 25:15\hebword{הׇכְלַ֙מְנוּ֙}
							
							\item 1Sam 25:24\hebword{בְּאׇזְנֶ֔יךָ}
							
							\item 1Sam 25:29\hebword{וַיָּ֤קׇם}
							
							\item 1Sam 25:29\hebword{לִרְדׇפְךָ֔}
							
							\item 1Sam 25:31\hebword{וְלִשְׁפׇּךְ־דָּם֙}
							
							\item 1Sam 25:37\hebword{וַיָּ֤מׇת}
							
							\item 1Sam 25:41\hebword{וַתָּ֕קׇם}
							
							\item 1Sam 25:42\hebword{וַתָּ֣קׇם}
							
							\item 1Sam 26:2\hebword{וַיָּ֣קׇם}
							
							\item 1Sam 26:5\hebword{וַיָּ֣קׇם}
							
							\item 1Sam 27:2\hebword{וַיָּ֣קׇם}
							
							\item 1Sam 27:9\hebword{וַיָּ֖שׇׁב}
							
							\item 1Sam 28:14\hebword{מַֽה־תׇּאֳר֔וֹ} This kamatz katan is subject to debate between experts and reading traditions.
							
							\item 1Sam 28:23\hebword{וַיָּ֙קׇם֙}
							
							\item 1Sam 30:6\hebword{לְסׇקְל֔וֹ}
							
							\item 1Sam 30:12\hebword{וַתָּ֥שׇׁב}
							
							\item 1Sam 30:17\hebword{לְמׇחֳרָתָ֑ם} This kamatz katan is subject to debate between experts and reading traditions.
							
							\item 1Sam 30:30\hebword{בְּחׇרְמָ֛ה}
							
							\item 1Sam 31:4\hebword{וְדׇקְרֵ֣נִי}
							
							\item 1Sam 31:5\hebword{וַיָּ֥מׇת}
							
							\item 1Sam 31:6\hebword{וַיָּ֣מׇת}
							
							\item 1Sam 31:8\hebword{מִֽמׇּחֳרָ֔ת} This kamatz katan is subject to debate between experts and reading traditions.
							
							\item 2Sam 1:9\hebword{עֲמׇד־נָ֤א}
							
							\item 2Sam 2:10\hebword{בְּמׇלְכוֹ֙}
							
							\item 2Sam 2:23\hebword{וַיִּפׇּל־שָׁ֖ם}
							
							\item 2Sam 2:23\hebword{וַיָּ֣מׇת}
							
							\item 2Sam 3:14\hebword{עׇרְל֥וֹת}
							
							\item 2Sam 3:19\hebword{בְּאׇזְנֵ֣י}
							
							\item 2Sam 3:19\hebword{בְּאׇזְנֵ֤י}
							
							\item 2Sam 3:27\hebword{וַיָּ֤שׇׁב}
							
							\item 2Sam 3:27\hebword{וַיָּ֕מׇת}
							
							\item 2Sam 4:4\hebword{בְּחׇפְזָ֥הּ}
							
							\item 2Sam 4:5\hebword{הַֽצׇּהֳרָֽיִם} This kamatz katan is subject to debate between experts and reading traditions.
							
							\item 2Sam 5:4\hebword{בְּמׇלְכ֑וֹ}
							
							\item 2Sam 5:24\hebword{כְּֽשׇׁמְעֲךָ֞}
							
							\item 2Sam 6:2\hebword{וַיָּ֣קׇם}
							
							\item 2Sam 6:7\hebword{וַיָּ֣מׇת}
							
							\item 2Sam 6:20\hebword{וַיָּ֥שׇׁב}
							
							\item 2Sam 7:22\hebword{בְּאׇזְנֵֽינוּ}
							
							\item 2Sam 8:10\hebword{לִשְׁאׇל־ל֨וֹ}
							
							\item 2Sam 10:1\hebword{וַיָּ֕מׇת}
							
							\item 2Sam 10:3\hebword{וּלְהׇפְכָ֔הּ}
							
							\item 2Sam 10:14\hebword{וַיָּ֣שׇׁב}
							
							\item 2Sam 10:18\hebword{וַיָּ֣נׇס}
							
							\item 2Sam 10:18\hebword{וַיָּ֥מׇת}
							
							\item 2Sam 10:19\hebword{כׇֽל־הַמְּלָכִ֜ים}
							
							\item 2Sam 11:2\hebword{וַיָּ֨קׇם}
							
							\item 2Sam 11:4\hebword{וַתָּ֖שׇׁב}
							
							\item 2Sam 11:12\hebword{וּמִֽמׇּחֳרָֽת} This kamatz katan is subject to debate between experts and reading traditions.
							
							\item 2Sam 11:17\hebword{וַיָּ֕מׇת}
							
							\item 2Sam 11:21\hebword{וַיָּ֣מׇת}
							
							\item 2Sam 11:25\hebword{וְהׇרְסָ֖הּ}
							
							\item 2Sam 12:16\hebword{וַיָּ֤צׇם}
							
							\item 2Sam 12:18\hebword{וַיָּ֣מׇת}
							
							\item 2Sam 12:20\hebword{וַיָּ֩קׇם֩}
							
							\item 2Sam 12:28\hebword{וְלׇכְדָ֑הּ}
							
							\item 2Sam 12:31\hebword{וַיָּ֧שׇׁב}
							
							\item 2Sam 13:8\hebword{וַתָּ֙לׇשׁ֙}
							
							\item 2Sam 13:25\hebword{וַיִּפְרׇץ־בּ֛וֹ}
							
							\item 2Sam 13:27\hebword{וַיִּפְרׇץ־בּ֖וֹ}
							
							\item 2Sam 13:31\hebword{וַיָּ֧קׇם}
							
							\item 2Sam 14:5\hebword{וַיָּ֥מׇת}
							
							\item 2Sam 14:7\hebword{כׇֽל־הַמִּשְׁפָּחָ֜ה}
							
							\item 2Sam 14:11\hebword{יִזְכׇּר־נָ֨א}
							
							\item 2Sam 14:20\hebword{כְּחׇכְמַת֙}
							
							\item 2Sam 14:23\hebword{וַיָּ֥קׇם}
							
							\item 2Sam 14:25\hebword{קׇדְקֳד֔וֹ}
							
							\item 2Sam 14:31\hebword{וַיָּ֣קׇם}
							
							\item 2Sam 15:5\hebword{בִּקְרׇב־אִ֔ישׁ}
							
							\item 2Sam 15:9\hebword{וַיָּ֖קׇם}
							
							\item 2Sam 15:10\hebword{כְּשׇׁמְעֲכֶם֙}
							
							\item 2Sam 15:12\hebword{בְּזׇבְח֖וֹ}
							
							\item 2Sam 15:18\hebword{וְכׇֽל־הַגִּתִּ֞ים}
							
							\item 2Sam 15:19\hebword{כִּי־נׇכְרִ֣י}
							
							\item 2Sam 15:24\hebword{וְכׇֽל־הַלְוִיִּ֣ם}
							
							\item 2Sam 15:32\hebword{כֻּתׇּנְתּ֔וֹ}
							
							\item 2Sam 17:13\hebword{כׇֽל־יִשְׂרָאֵ֛ל}
							
							\item 2Sam 17:22\hebword{וַיָּ֣קׇם}
							
							\item 2Sam 17:23\hebword{וַיָּ֜קׇם}
							
							\item 2Sam 17:23\hebword{וַיָּ֕מׇת}
							
							\item 2Sam 18:12\hebword{בְאׇזְנֵ֜ינוּ}
							
							\item 2Sam 18:16\hebword{וַיָּ֣שׇׁב}
							
							\item 2Sam 18:17\hebword{וְכׇ֨ל־יִשְׂרָאֵ֔ל}
							
							\item 2Sam 18:23\hebword{וַיָּ֤רׇץ}
							
							\item 2Sam 19:9\hebword{וַיָּ֥קׇם}
							
							\item 2Sam 19:16\hebword{וַיָּ֣שׇׁב}
							
							\item 2Sam 19:19\hebword{בְּעׇבְר֖וֹ}
							
							\item 2Sam 19:38\hebword{יָשׇׁב־נָ֤א}
							
							\item 2Sam 19:40\hebword{וַיָּ֖שׇׁב}
							
							\item 2Sam 20:8\hebword{עַל־מׇתְנָיו֙}
							
							\item 2Sam 20:9\hebword{לִנְשׇׁק־לֽוֹ}
							
							\item 2Sam 20:22\hebword{בְּחׇכְמָתָ֗הּ}
							
							\item 2Sam 21:17\hebword{וַיַּֽעֲזׇר־לוֹ֙}
							
							\item 2Sam 21:19\hebword{גׇּלְיָ֣ת}
							
							\item 2Sam 22:7\hebword{בְּאׇזְנָֽיו}
							
							\item 2Sam 22:29\hebword{חׇשְׁכִּֽי}
							
							\item 2Sam 24:6\hebword{חׇדְשִׁ֑י}
							
							\item 2Sam 24:11\hebword{וַיָּ֥קׇם}
							
							\item 2Sam 24:15\hebword{וַיָּ֣מׇת}
							
										\end{itemize}\end{multicols}
						
					\subsection{Kings}
				
			\begin{multicols}{2}\begin{itemize}
							
							\item 1Kings 1:50\hebword{וַיָּ֣קׇם}
							
							\item 1Kings 2:5\hebword{בְּמׇתְנָ֔יו}
							
							\item 1Kings 2:6\hebword{כְּחׇכְמָתֶ֑ךָ}
							
							\item 1Kings 2:7\hebword{בְּבׇרְחִ֕י}
							
							\item 1Kings 2:19\hebword{וַיָּ֩קׇם֩}
							
							\item 1Kings 2:28\hebword{וַיָּ֤נׇס}
									
									\item 1Kings 2:40\hebword{וַיָּ֣קׇם}
									
									\item 1Kings 3:6\hebword{וַתִּשְׁמׇר־ל֗וֹ}
									
									\item 1Kings 3:19\hebword{וַיָּ֛מׇת}
									
									\item 1Kings 3:20\hebword{וַתָּ֩קׇם֩}
									
									\item 1Kings 3:28\hebword{כִּֽי־חׇכְמַ֧ת}
									
									\item 1Kings 5:7\hebword{חׇדְשׁ֑וֹ}
									
									\item 1Kings 5:9\hebword{חׇכְמָ֧ה}
									
									\item 1Kings 5:10\hebword{חׇכְמַ֣ת}
									
									\item 1Kings 5:10\hebword{מֵחׇכְמַ֖ת}
									
									\item 1Kings 5:10\hebword{חׇכְמַ֥ת}
									
									\item 1Kings 5:11\hebword{בְכׇֽל־הַגּוֹיִ֖ם}
									
									\item 1Kings 5:14\hebword{חׇכְמַ֣ת}
									
									\item 1Kings 5:14\hebword{אֶת־חׇכְמָתֽוֹ}
									
									\item 1Kings 5:20\hebword{לִכְרׇת־עֵצִ֖ים}
									
									\item 1Kings 5:26\hebword{חׇכְמָה֙}
									
									\item 1Kings 6:2\hebword{אׇרְכּ֖וֹ}
									
									\item 1Kings 6:2\hebword{רׇחְבּ֑וֹ}
									
									\item 1Kings 6:3\hebword{אׇרְכּ֔וֹ}
									
									\item 1Kings 6:3\hebword{רׇחְבּ֖וֹ}
									
									\item 1Kings 6:6\hebword{רׇחְבָּ֗הּ}
									
									\item 1Kings 6:6\hebword{רׇחְבָּ֔הּ}
									
									\item 1Kings 6:6\hebword{רׇחְבָּ֑הּ}
									
									\item 1Kings 7:2\hebword{אׇרְכּוֹ֙}
									
									\item 1Kings 7:2\hebword{רׇחְבּ֔וֹ}
									
									\item 1Kings 7:6\hebword{אׇרְכּ֔וֹ}
									
									\item 1Kings 7:6\hebword{רׇחְבּ֑וֹ}
									
									\item 1Kings 7:7\hebword{יִשְׁפׇּט־שָׁ֔ם}
									
									\item 1Kings 7:14\hebword{אֶת־הַחׇכְמָ֤ה}
									
									\item 1Kings 7:26\hebword{וְעׇבְי֣וֹ}
									
									\item 1Kings 7:27\hebword{רׇחְבָּ֔הּ}
									
									\item 1Kings 7:51\hebword{אֶת־קׇדְשֵׁ֣י}
									
									\item 1Kings 8:37\hebword{כׇּֽל־מַחֲלָֽה}
									
									\item 1Kings 8:40\hebword{כׇּ֨ל־הַיָּמִ֔ים}
									
									\item 1Kings 8:41\hebword{אֶל־הַנׇּכְרִ֔י}
									
									\item 1Kings 8:43\hebword{הַנׇּכְרִ֑י}
									
									\item 1Kings 8:52\hebword{קׇרְאָ֥ם}
									
									\item 1Kings 8:66\hebword{לְאׇהֳלֵיהֶ֗ם} This kamatz katan is subject to debate between experts and reading traditions.
									
									\item 1Kings 9:4\hebword{בְּתׇם־לֵבָ֣ב}
									
									\item 1Kings 9:26\hebword{וׇאֳנִ֡י} This kamatz katan is subject to debate between experts and reading traditions.
									
									\item 1Kings 9:27\hebword{בׇּֽאֳנִי֙} This kamatz katan is subject to debate between experts and reading traditions.
									
									\item 1Kings 10:4\hebword{כׇּל־חׇכְמַ֣ת}
									
									\item 1Kings 10:6\hebword{וְעַל־חׇכְמָתֶֽךָ}
									
									\item 1Kings 10:7\hebword{חׇכְמָה֙}
									
									\item 1Kings 10:8\hebword{אֶת־חׇכְמָתֶֽךָ}
									
									\item 1Kings 10:23\hebword{וּלְחׇכְמָֽה}
											
											\item 1Kings 10:24\hebword{אֶת־חׇכְמָת֔וֹ}
											
											\item 1Kings 11:8\hebword{הַנׇּכְרִיּ֑וֹת}
											
											\item 1Kings 11:26\hebword{וְיָרׇבְעָם֩}
											
											\item 1Kings 11:28\hebword{יָרׇבְעָ֖ם}
											
											\item 1Kings 11:29\hebword{וְיָרׇבְעָ֖ם}
											
											\item 1Kings 11:31\hebword{לְיָֽרׇבְעָ֔ם}
											
											\item 1Kings 11:36\hebword{כׇּֽל־הַיָּמִ֤ים}
											
											\item 1Kings 11:40\hebword{אֶת־יָרׇבְעָ֑ם}
											
											\item 1Kings 11:40\hebword{וַיָּ֣קׇם}
											
											\item 1Kings 11:40\hebword{יָרׇבְעָ֗ם}
											
											\item 1Kings 11:41\hebword{וְחׇכְמָת֑וֹ}
											
											\item 1Kings 12:2\hebword{יָרׇבְעָ֣ם}
											
											\item 1Kings 12:2\hebword{יָרׇבְעָ֖ם}
											
											\item 1Kings 12:3\hebword{יָרׇבְעָ֖ם}
											
											\item 1Kings 12:10\hebword{קׇטׇנִּ֥י} This kamatz katan is subject to debate between experts and reading traditions.
											
											\item 1Kings 12:10\hebword{מִמׇּתְנֵ֥י}
											
											\item 1Kings 12:12\hebword{יָרׇבְעָ֧ם}
											
											\item 1Kings 12:15\hebword{אֶל־יָרׇבְעָ֖ם}
											
											\item 1Kings 12:20\hebword{יָרׇבְעָ֔ם}
											
											\item 1Kings 12:25\hebword{יָרׇבְעָ֧ם}
											
											\item 1Kings 12:26\hebword{יָרׇבְעָ֖ם}
											
											\item 1Kings 12:32\hebword{יָרׇבְעָ֣ם}
											
											\item 1Kings 13:1\hebword{וְיָרׇבְעָ֛ם}
											
											\item 1Kings 13:4\hebword{יָרׇבְעָ֧ם}
											
											\item 1Kings 13:6\hebword{וַתָּ֤שׇׁב}
											
											\item 1Kings 13:19\hebword{וַיָּ֣שׇׁב}
											
											\item 1Kings 13:22\hebword{וַתָּ֗שׇׁב}
											
											\item 1Kings 13:23\hebword{אׇכְל֥וֹ}
											
											\item 1Kings 13:23\hebword{וַיַּחֲבׇשׁ־ל֣וֹ}
											
											\item 1Kings 13:29\hebword{וּלְקׇבְרֽוֹ}
											
											\item 1Kings 13:31\hebword{קׇבְר֣וֹ}
											
											\item 1Kings 13:33\hebword{יָרׇבְעָ֖ם}
											
											\item 1Kings 13:33\hebword{וַ֠יָּ֠שׇׁב}
											
											\item 1Kings 13:34\hebword{יָרׇבְעָ֑ם}
											
											\item 1Kings 14:1\hebword{בֶן־יָרׇבְעָֽם}
											
											\item 1Kings 14:2\hebword{יָרׇבְעָ֜ם}
											
											\item 1Kings 14:2\hebword{יָרׇבְעָ֑ם}
											
											\item 1Kings 14:4\hebword{יָרׇבְעָ֔ם}
											
											\item 1Kings 14:4\hebword{וַתָּ֙קׇם֙}
											
											\item 1Kings 14:5\hebword{יָרׇבְעָ֡ם}
											
											\item 1Kings 14:6\hebword{יָרׇבְעָ֑ם}
											
											\item 1Kings 14:7\hebword{לְיָרׇבְעָ֗ם}
											
											\item 1Kings 14:10\hebword{יָרׇבְעָ֔ם}
											
											\item 1Kings 14:10\hebword{לְיָֽרׇבְעָם֙}
											
											\item 1Kings 14:10\hebword{בֵית־יָרׇבְעָ֔ם}
											
											\item 1Kings 14:11\hebword{לְיָרׇבְעָ֤ם}
											
											\item 1Kings 14:13\hebword{לְיָרׇבְעָ֖ם}
											
											\item 1Kings 14:13\hebword{יָרׇבְעָֽם}
											
											\item 1Kings 14:14\hebword{יָרׇבְעָ֖ם}
											
											\item 1Kings 14:16\hebword{יָֽרׇבְעָם֙}
											
											\item 1Kings 14:17\hebword{וַתָּ֙קׇם֙}
											
											\item 1Kings 14:17\hebword{יָרׇבְעָ֔ם}
											
											\item 1Kings 14:19\hebword{יָרׇבְעָ֔ם}
											
											\item 1Kings 14:20\hebword{יָרׇבְעָ֔ם}
											
											\item 1Kings 14:21\hebword{בְּמׇלְכ֜וֹ}
											
											\item 1Kings 14:30\hebword{יָרׇבְעָ֖ם}
											
											\item 1Kings 15:1\hebword{יָרׇבְעָ֣ם}
											
											\item 1Kings 15:6\hebword{יָרׇבְעָ֖ם}
											
											\item 1Kings 15:7\hebword{יָרׇבְעָֽם}
											
											\item 1Kings 15:9\hebword{לְיָרׇבְעָ֖ם}
											
											\item 1Kings 15:15\hebword{אֶת־קׇדְשֵׁ֣י}
											
											\item 1Kings 15:15\hebword{וְקׇדְשֵׁ֖י}
											
											\item 1Kings 15:25\hebword{בֶּן־יָרׇבְעָ֗ם}
											
											\item 1Kings 15:29\hebword{כְמׇלְכ֗וֹ}
											
											\item 1Kings 15:29\hebword{יָרׇבְעָ֔ם}
											
											\item 1Kings 15:29\hebword{לְיָרׇבְעָ֖ם}
											
											\item 1Kings 15:30\hebword{יָֽרׇבְעָם֙}
											
											\item 1Kings 15:34\hebword{יָרׇבְעָ֔ם}
											
											\item 1Kings 16:2\hebword{יָרׇבְעָ֗ם}
											
											\item 1Kings 16:3\hebword{יָרׇבְעָ֥ם}
											
											\item 1Kings 16:7\hebword{יָרׇבְעָ֑ם}
											
											\item 1Kings 16:11\hebword{בְמׇלְכ֜וֹ}
											
											\item 1Kings 16:16\hebword{כׇֽל־יִ֠שְׂרָאֵ֠ל}
											
											\item 1Kings 16:16\hebword{אֶת־עׇמְרִ֨י}
											
											\item 1Kings 16:17\hebword{עׇמְרִ֛י}
											
											\item 1Kings 16:19\hebword{יָרׇבְעָ֔ם}
											
											\item 1Kings 16:21\hebword{עׇמְרִֽי}
											
											\item 1Kings 16:22\hebword{עׇמְרִ֔י}
											
											\item 1Kings 16:22\hebword{וַיָּ֣מׇת}
											
											\item 1Kings 16:22\hebword{עׇמְרִֽי}
											
											\item 1Kings 16:23\hebword{עׇמְרִי֙}
											
											\item 1Kings 16:25\hebword{עׇמְרִ֛י}
											
											\item 1Kings 16:26\hebword{יָרׇבְעָ֣ם}
											
											\item 1Kings 16:27\hebword{עׇמְרִי֙}
											
											\item 1Kings 16:28\hebword{עׇמְרִי֙}
											
											\item 1Kings 16:29\hebword{בֶּן־עׇמְרִ֗י}
											
											\item 1Kings 16:29\hebword{בֶּן־עׇמְרִ֤י}
											
											\item 1Kings 16:30\hebword{בֶּן־עׇמְרִ֛י}
											
											\item 1Kings 16:31\hebword{יָרׇבְעָ֣ם}
											
											\item 1Kings 17:10\hebword{וַיָּ֣קׇם}
											
											\item 1Kings 17:17\hebword{חׇלְיוֹ֙}
											
											\item 1Kings 17:21\hebword{תָּ֥שׇׁב}
											
											\item 1Kings 17:22\hebword{וַתָּ֧שׇׁב}
											
											\item 1Kings 18:6\hebword{לַֽעֲבׇר־בָּ֑הּ}
											
											\item 1Kings 18:18\hebword{בַּעֲזׇבְכֶם֙}
											
											\item 1Kings 18:26\hebword{וְעַד־הַצׇּהֳרַ֤יִם} This kamatz katan is subject to debate between experts and reading traditions.
											
											\item 1Kings 18:27\hebword{בַֽצׇּהֳרַ֜יִם} This kamatz katan is subject to debate between experts and reading traditions.
											
											\item 1Kings 18:28\hebword{עַד־שְׁפׇךְ־דָּ֖ם}
											
											\item 1Kings 18:29\hebword{הַֽצׇּהֳרַ֔יִם} This kamatz katan is subject to debate between experts and reading traditions.
											
											\item 1Kings 18:44\hebword{יַעֲצׇרְכָ֖ה}
											
											\item 1Kings 18:46\hebword{מׇתְנָ֑יו}
											
											\item 1Kings 18:46\hebword{וַיָּ֙רׇץ֙}
											
											\item 1Kings 19:3\hebword{וַיָּ֙קׇם֙}
											
											\item 1Kings 19:6\hebword{וַיָּ֖שׇׁב}
											
											\item 1Kings 19:7\hebword{וַיָּ֩שׇׁב֩}
											
											\item 1Kings 19:8\hebword{וַיָּ֖קׇם}
											
											\item 1Kings 19:18\hebword{וְכׇ֨ל־הַפֶּ֔ה}
											
											\item 1Kings 19:20\hebword{וַיָּ֙רׇץ֙}
											
											\item 1Kings 19:21\hebword{וַיָּ֨שׇׁב}
											
											\item 1Kings 19:21\hebword{וַיָּ֗קׇם}
											
											\item 1Kings 20:16\hebword{בַּֽצׇּהֳרָ֑יִם} This kamatz katan is subject to debate between experts and reading traditions.
											
											\item 1Kings 20:27\hebword{הׇתְפָּקְדוּ֙}
											
											\item 1Kings 20:31\hebword{בְּמׇתְנֵ֜ינוּ}
											
											\item 1Kings 20:32\hebword{בְּמׇתְנֵיהֶ֜ם}
											
											\item 1Kings 20:34\hebword{וַיִּכְרׇת־ל֥וֹ}
											
											\item 1Kings 21:16\hebword{וַיָּ֣קׇם}
											
											\item 1Kings 21:22\hebword{יָרׇבְעָ֣ם}
											
											\item 1Kings 22:5\hebword{דְּרׇשׁ־נָ֥א}
											
											\item 1Kings 22:10\hebword{וְכׇ֨ל־הַנְּבִיאִ֔ים}
											
											\item 1Kings 22:12\hebword{וְכׇ֨ל־הַנְּבִאִ֔ים}
											
											\item 1Kings 22:34\hebword{הׇחֳלֵֽיתִי} This kamatz katan is subject to debate between experts and reading traditions.
											
											\item 1Kings 22:35\hebword{מׇעֳמָ֛ד} This kamatz katan is subject to debate between experts and reading traditions.
											
											\item 1Kings 22:35\hebword{וַיָּ֣מׇת}
											
											\item 1Kings 22:37\hebword{וַיָּ֣מׇת}
											
											\item 1Kings 22:42\hebword{בְּמׇלְכ֔וֹ}
											
											\item 1Kings 22:50\hebword{בׇּאֳנִיּ֑וֹת} This kamatz katan is subject to debate between experts and reading traditions.
											
											\item 1Kings 22:53\hebword{יָרׇבְעָ֣ם}
											
											\item 2Kings 1:8\hebword{בְּמׇתְנָ֑יו}
											
											\item 2Kings 1:11\hebword{וַיָּ֜שׇׁב}
											
											\item 2Kings 1:13\hebword{וַיָּ֗שׇׁב}
											
											\item 2Kings 1:15\hebword{וַיָּ֛קׇם}
											
											\item 2Kings 1:17\hebword{וַיָּ֜מׇת}
											
											\item 2Kings 2:9\hebword{כְעׇבְרָ֗ם}
											
											\item 2Kings 2:13\hebword{וַיָּ֥שׇׁב}
											
											\item 2Kings 3:3\hebword{יָרׇבְעָ֧ם}
											
											\item 2Kings 3:23\hebword{הׇחֳרֵ֤ב} This kamatz katan is subject to debate between experts and reading traditions.
													
													\item 2Kings 4:8\hebword{עׇבְר֔וֹ}
													
													\item 2Kings 4:13\hebword{אֱמׇר־נָ֣א}
													
													\item 2Kings 4:20\hebword{עַד־הַֽצׇּהֳרַ֖יִם} This kamatz katan is subject to debate between experts and reading traditions.
													
													\item 2Kings 4:24\hebword{אַל־תַּעֲצׇר־לִ֣י}
													
													\item 2Kings 4:26\hebword{וֶאֱמׇר־לָ֗הּ}
													
													\item 2Kings 4:27\hebword{לְהׇדְפָ֗הּ}
													
													\item 2Kings 4:29\hebword{מׇתְנֶ֗יךָ}
													
													\item 2Kings 4:30\hebword{וַיָּ֖קׇם}
													
													\item 2Kings 4:31\hebword{וַיָּ֤שׇׁב}
													
													\item 2Kings 4:34\hebword{וַיָּ֖חׇם}
													
													\item 2Kings 4:35\hebword{וַיָּ֜שׇׁב}
													
													\item 2Kings 4:40\hebword{כְּאׇכְלָ֨ם}
													
													\item 2Kings 5:14\hebword{וַיָּ֣שׇׁב}
													
													\item 2Kings 5:15\hebword{וַיָּ֩שׇׁב֩}
													
													\item 2Kings 5:15\hebword{וְכׇֽל־מַחֲנֵ֗הוּ}
													
													\item 2Kings 5:23\hebword{וַיִּפְרׇץ־בּ֗וֹ}
													
													\item 2Kings 6:6\hebword{וַיִּקְצׇב־עֵץ֙}
													
													\item 2Kings 7:7\hebword{אֶת־אׇהֳלֵיהֶ֗ם} This kamatz katan is subject to debate between experts and reading traditions.
													
													\item 2Kings 7:12\hebword{וַיָּ֨קׇם}
													
													\item 2Kings 7:15\hebword{בְּחׇפְזָ֑ם}
													
													\item 2Kings 8:2\hebword{וַתָּ֙קׇם֙}
													
													\item 2Kings 8:2\hebword{וַתָּ֥גׇר}
													
													\item 2Kings 8:3\hebword{וַתָּ֥שׇׁב}
													
													\item 2Kings 8:15\hebword{מִֽמׇּחֳרָ֗ת} This kamatz katan is subject to debate between experts and reading traditions.
													
													\item 2Kings 8:17\hebword{בְמׇלְכ֑וֹ}
													
													\item 2Kings 8:21\hebword{וַיָּ֥נׇס}
													
													\item 2Kings 8:26\hebword{בְמׇלְכ֔וֹ}
													
													\item 2Kings 8:26\hebword{בַּת־עׇמְרִ֖י}
													
													\item 2Kings 8:29\hebword{וַיָּ֩שׇׁב֩}
													
													\item 2Kings 9:1\hebword{מׇתְנֶ֗יךָ}
													
													\item 2Kings 9:6\hebword{וַיָּ֙קׇם֙}
													
													\item 2Kings 9:9\hebword{יָרׇבְעָ֣ם}
													
													\item 2Kings 9:15\hebword{וַיָּ֩שׇׁב֩}
													
													\item 2Kings 9:27\hebword{וַיָּ֕נׇס}
													
													\item 2Kings 9:27\hebword{וַיָּ֥נׇס}
													
													\item 2Kings 9:27\hebword{וַיָּ֥מׇת}
													
													\item 2Kings 9:35\hebword{לְקׇבְרָ֑הּ}
													
													\item 2Kings 10:12\hebword{וַיָּ֙קׇם֙}
													
													\item 2Kings 10:19\hebword{בְעׇקְבָּ֔ה}
													
													\item 2Kings 10:29\hebword{יָרׇבְעָ֤ם}
													
													\item 2Kings 10:31\hebword{יָרׇבְעָ֔ם}
													
													\item 2Kings 11:1\hebword{וַתָּ֙קׇם֙}
													
													\item 2Kings 12:1\hebword{בְּמׇלְכֽוֹ}
													
													\item 2Kings 12:12\hebword{לְחׇרָשֵׁ֤י} This kamatz katan is subject to debate between experts and reading traditions.
													
													\item 2Kings 12:13\hebword{לְחׇזְקָֽה}
													
													\item 2Kings 13:2\hebword{יָרׇבְעָ֧ם}
													
													\item 2Kings 13:5\hebword{בְּאׇהֳלֵיהֶ֖ם} This kamatz katan is subject to debate between experts and reading traditions.
													
													\item 2Kings 13:6\hebword{בֵּית־יָרׇבְעָ֛ם}
													
													\item 2Kings 13:11\hebword{יָרׇבְעָ֧ם}
													
													\item 2Kings 13:13\hebword{וְיָרׇבְעָ֖ם}
													
													\item 2Kings 13:14\hebword{אֶת־חׇלְי֔וֹ}
													
													\item 2Kings 13:20\hebword{וַיָּ֥מׇת}
													
													\item 2Kings 13:21\hebword{וַיָּ֥קׇם}
													
													\item 2Kings 13:23\hebword{וַיָּ֩חׇן֩}
													
													\item 2Kings 13:24\hebword{וַיָּ֖מׇת}
													
													\item 2Kings 13:25\hebword{וַיָּ֜שׇׁב}
													
													\item 2Kings 14:2\hebword{בְמׇלְכ֔וֹ}
													
													\item 2Kings 14:7\hebword{יׇקְתְאֵ֔ל}
													
													\item 2Kings 14:14\hebword{וַיָּ֖שׇׁב}
													
													\item 2Kings 14:16\hebword{יָרׇבְעָ֥ם}
													
													\item 2Kings 14:19\hebword{וַיָּ֣נׇס}
													
													\item 2Kings 14:23\hebword{יָרׇבְעָ֨ם}
													
													\item 2Kings 14:24\hebword{יָרׇבְעָ֣ם}
													
													\item 2Kings 14:27\hebword{יָרׇבְעָ֥ם}
													
													\item 2Kings 14:28\hebword{יָרׇבְעָ֜ם}
													
													\item 2Kings 14:29\hebword{יָֽרׇבְעָם֙}
													
													\item 2Kings 15:1\hebword{לְיָרׇבְעָ֖ם}
													
													\item 2Kings 15:2\hebword{בְמׇלְכ֔וֹ}
													
													\item 2Kings 15:5\hebword{הַחׇפְשִׁ֑ית}
													
													\item 2Kings 15:8\hebword{בֶן־יָרׇבְעָ֧ם}
													
													\item 2Kings 15:9\hebword{יָרׇבְעָ֣ם}
													
													\item 2Kings 15:10\hebword{קׇֽבׇל־עָ֖ם} This kamatz katan is subject to debate between experts and reading traditions.
													
													\item 2Kings 15:18\hebword{יָרׇבְעָ֧ם}
													
													\item 2Kings 15:20\hebword{וַיָּ֙שׇׁב֙}
													
													\item 2Kings 15:24\hebword{יָרׇבְעָ֣ם}
													
													\item 2Kings 15:28\hebword{יָרׇבְעָ֣ם}
													
													\item 2Kings 15:30\hebword{וַיִּקְשׇׁר־קֶ֜שֶׁר}
													
													\item 2Kings 15:33\hebword{בְמׇלְכ֔וֹ}
													
													\item 2Kings 16:2\hebword{בְּמׇלְכ֔וֹ}
													
													\item 2Kings 16:10\hebword{לְכׇֽל־מַעֲשֵֽׂהוּ}
													
													\item 2Kings 17:13\hebword{כְּכׇ֨ל־הַתּוֹרָ֔ה}
													
													\item 2Kings 17:14\hebword{אֶת־עׇרְפָּם֙}
													
													\item 2Kings 17:21\hebword{אֶת־יָרׇבְעָ֣ם}
													
													\item 2Kings 17:21\hebword{יָרׇבְעָ֤ם}
													
													\item 2Kings 17:22\hebword{יָרׇבְעָ֖ם}
													
													\item 2Kings 18:2\hebword{בְמׇלְכ֔וֹ}
													
													\item 2Kings 18:21\hebword{לְכׇֽל־הַבֹּטְחִ֖ים}
													
													\item 2Kings 18:26\hebword{בְּאׇזְנֵ֣י}
													
													\item 2Kings 19:8\hebword{וַיָּ֙שׇׁב֙}
													
													\item 2Kings 19:9\hebword{וַיָּ֙שׇׁב֙}
													
													\item 2Kings 19:16\hebword{אׇזְנְךָ֙}
													
													\item 2Kings 19:17\hebword{אׇמְנָ֖ם}
													
													\item 2Kings 19:28\hebword{בְאׇזְנָ֑י}
													
													\item 2Kings 19:36\hebword{וַיָּ֖שׇׁב}
													
													\item 2Kings 20:3\hebword{זְכׇר־נָ֞א}
													
													\item 2Kings 21:1\hebword{בְמׇלְכ֔וֹ}
													
													\item 2Kings 21:3\hebword{וַיָּ֗שׇׁב}
													
													\item 2Kings 21:8\hebword{וּלְכׇ֨ל־הַתּוֹרָ֔ה}
													
													\item 2Kings 21:12\hebword{אׇזְנָֽיו}
													
													\item 2Kings 21:19\hebword{בְּמׇלְכ֔וֹ}
													
													\item 2Kings 21:19\hebword{מִן־יׇטְבָֽה}
													
													\item 2Kings 22:1\hebword{בְמׇלְכ֔וֹ}
													
													\item 2Kings 22:19\hebword{בְּֽשׇׁמְעֲךָ֡}
													
													\item 2Kings 23:2\hebword{בְאׇזְנֵיהֶ֗ם}
													
													\item 2Kings 23:12\hebword{וַיָּ֣רׇץ}
													
													\item 2Kings 23:15\hebword{יָרׇבְעָ֤ם}
													
													\item 2Kings 23:20\hebword{וַיָּ֖שׇׁב}
													
													\item 2Kings 23:31\hebword{בְּמׇלְכ֔וֹ}
													
													\item 2Kings 23:34\hebword{וַיָּ֥מׇת}
													
													\item 2Kings 23:36\hebword{בְּמׇלְכ֔וֹ}
													
													\item 2Kings 24:1\hebword{וַיָּ֖שׇׁב}
													
													\item 2Kings 24:1\hebword{וַיִּמְרׇד־בּֽוֹ}
													
													\item 2Kings 24:8\hebword{בְּמׇלְכ֔וֹ}
													
													\item 2Kings 24:12\hebword{לְמׇלְכֽוֹ}
													
													\item 2Kings 24:18\hebword{בְמׇלְכ֔וֹ}
													
													\item 2Kings 25:1\hebword{לְמׇלְכ֗וֹ}
													
													\item 2Kings 25:5\hebword{וְכׇ֨ל־חֵיל֔וֹ}
													
													\item 2Kings 25:27\hebword{מׇלְכ֗וֹ}
\end{itemize}\end{multicols}
\section{Latter Prophets}
\subsection{Isaiah}
\begin{multicols}{2}\begin{itemize}

\item Is 1:14\hebword{חׇדְשֵׁיכֶ֤ם}

\item Is 1:22\hebword{סׇבְאֵ֖ךְ}

\item Is 2:6\hebword{נׇכְרִ֖ים}

\item Is 3:17\hebword{קׇדְקֹ֖ד}

\item Is 3:17\hebword{פׇּתְהֵ֥ן}

\item Is 3:24\hebword{קׇרְחָ֔ה}

\item Is 5:17\hebword{כְּדׇבְרָ֑ם}

\item Is 5:17\hebword{וְחׇרְב֥וֹת}

\item Is 5:24\hebword{שׇׁרְשָׁם֙}

\item Is 6:6\hebword{וַיָּ֣עׇף}

\item Is 6:10\hebword{וְאׇזְנָ֥יו}

\item Is 6:10\hebword{וּבְאׇזְנָ֣יו}

\item Is 7:4\hebword{בׇּחֳרִי־אַ֛ף} This kamatz katan is subject to debate between experts and reading traditions.

\item Is 10:13\hebword{וּבְחׇכְמָתִ֖י}

\item Is 11:1\hebword{מִשׇּׁרָשָׁ֥יו} This kamatz katan is subject to debate between experts and reading traditions.

\item Is 11:2\hebword{חׇכְמָ֣ה}

\item Is 11:3\hebword{אׇזְנָ֖יו}

\item Is 11:5\hebword{מׇתְנָ֑יו}

\item Is 11:9\hebword{קׇדְשִׁ֑י}

\item Is 12:2\hebword{כִּֽי־עׇזִּ֤י}

\item Is 14:3\hebword{מֵֽעׇצְבְּךָ֖}

\item Is 14:3\hebword{וּמִֽרׇגְזֶ֑ךָ}

\item Is 14:19\hebword{הׇשְׁלַ֤כְתָּ}

\item Is 14:30\hebword{שׇׁרְשֵׁ֔ךְ}

\item Is 15:2\hebword{קׇרְחָ֔ה}

\item Is 16:3\hebword{צׇהֳרָ֑יִם} This kamatz katan is subject to debate between experts and reading traditions.

\item Is 18:5\hebword{כְּתׇם־פֶּ֔רַח}

\item Is 19:4\hebword{יִמְשׇׁל־בָּ֔ם}

\item Is 20:2\hebword{מׇתְנֶ֔יךָ}

\item Is 21:3\hebword{מׇתְנַי֙}

\item Is 21:10\hebword{וּבֶן־גׇּרְנִ֑י}

\item Is 22:12\hebword{וּלְקׇרְחָ֖ה}

\item Is 22:14\hebword{בְאׇזְנָ֖י}

\item Is 22:18\hebword{יִצְנׇפְךָ֙}

\item Is 22:21\hebword{כֻּתׇּנְתֶּ֗ךָ}

\item Is 23:18\hebword{לְשׇׂבְעָ֖ה}

\item Is 25:11\hebword{אׇרְבּ֥וֹת}

\item Is 26:1\hebword{עׇז־לָ֔נוּ}

\item Is 26:12\hebword{כׇּֽל־מַעֲשֵׂ֖ינוּ}

\item Is 26:20\hebword{עַד־יַעֲבׇור־זָֽעַם}
		
		\item Is 28:19\hebword{עׇבְרוֹ֙}
		
		\item Is 28:21\hebword{נׇכְרִיָּ֖ה}
		
		\item Is 29:14\hebword{חׇכְמַ֣ת}
		
		\item Is 30:8\hebword{כׇתְבָ֥הּ}
		
		\item Is 30:19\hebword{יׇחְנְךָ֙}
		
		\item Is 30:19\hebword{כְּשׇׁמְעָת֖וֹ}
		
		\item Is 30:21\hebword{וְאׇזְנֶ֙יךָ֙}
		
		\item Is 30:33\hebword{תׇּפְתֶּ֔ה}
		
		\item Is 30:33\hebword{גׇּפְרִ֔ית}
		
		\item Is 32:1\hebword{יִמְלׇךְ־מֶ֑לֶךְ}
		
		\item Is 32:3\hebword{וְאׇזְנֵ֥י}
		
		\item Is 33:2\hebword{חׇנֵּ֖נוּ}
		
		\item Is 33:6\hebword{חׇכְמַ֣ת}
		
		\item Is 33:15\hebword{אׇזְנוֹ֙}
		
		\item Is 33:17\hebword{בְּיׇפְי֖וֹ}
		
		\item Is 33:23\hebword{כֵן־תׇּרְנָם֙}
		
		\item Is 34:3\hebword{בׇאְשָׁ֑ם}
		
		\item Is 34:6\hebword{בְּבׇצְרָ֔ה}
		
		\item Is 34:9\hebword{לְגׇפְרִ֑ית}
		
		\item Is 35:5\hebword{וְאׇזְנֵ֥י}
		
		\item Is 36:6\hebword{לְכׇֽל־הַבֹּטְחִ֖ים}
		
		\item Is 36:11\hebword{בְּאׇזְנֵ֣י}
		
		\item Is 37:8\hebword{וַיָּ֙שׇׁב֙}
		
		\item Is 37:17\hebword{אׇזְנְךָ֙}
		
		\item Is 37:18\hebword{אׇמְנָ֖ם}
		
		\item Is 37:29\hebword{בְאׇזְנָ֑י}
		
		\item Is 37:37\hebword{וַיָּ֖שׇׁב}
		
		\item Is 38:3\hebword{זְכׇר־נָ֞א}
		
		\item Is 38:8\hebword{וַתָּ֤שׇׁב}
		
		\item Is 38:9\hebword{מֵחׇלְיֽוֹ}
		
		\item Is 38:14\hebword{עׇרְבֵֽנִי}
		
		\item Is 40:12\hebword{בְּשׇׁעֳל֜וֹ} This kamatz katan is subject to debate between experts and reading traditions.
		
		\item Is 40:29\hebword{עׇצְמָ֥ה}
		
		\item Is 41:24\hebword{וּפׇֽעׇלְכֶ֖ם}
		
		\item Is 42:1\hebword{אֶתְמׇךְ־בּ֔וֹ}
		
		\item Is 42:6\hebword{וְאֶצׇּרְךָ֗}
		
		\item Is 42:20\hebword{אׇזְנַ֖יִם}
		
		\item Is 42:22\hebword{הׇחְבָּ֑אוּ}
		
		\item Is 43:3\hebword{כׇפְרְךָ֙}
		
		\item Is 43:8\hebword{וְאׇזְנַ֥יִם}
		
		\item Is 43:9\hebword{כׇּֽל־הַגּוֹיִ֞ם}
		
		\item Is 44:3\hebword{אֶצׇּק־מַ֙יִם֙}
		
		\item Is 44:13\hebword{יְתׇאֳרֵ֑הוּ} This kamatz katan is subject to debate between experts and reading traditions.
		
		\item Is 44:14\hebword{לִכְרׇת־ל֣וֹ}
		
		\item Is 44:15\hebword{וַיָּ֔חׇם}
		
		\item Is 44:15\hebword{וַיִּסְגׇּד־לָֽמוֹ}
		
		\item Is 44:17\hebword{יִסְגׇּד־ל֤וֹ}
				
				\item Is 44:21\hebword{זְכׇר־אֵ֣לֶּה}
				
				\item Is 44:26\hebword{וְחׇרְבוֹתֶ֖יהָ}
				
				\item Is 45:1\hebword{וּמׇתְנֵ֥י}
				
				\item Is 45:9\hebword{וּפׇעׇלְךָ֖}
				
				\item Is 47:9\hebword{בְּעׇצְמַ֥ת}
				
				\item Is 47:10\hebword{חׇכְמָתֵ֥ךְ}
				
				\item Is 48:4\hebword{עׇרְפֶּ֔ךָ}
				
				\item Is 48:5\hebword{עׇצְבִּ֣י}
				
				\item Is 48:8\hebword{אׇזְנֶ֑ךָ}
				
				\item Is 48:9\hebword{אֶחֱטׇם־לָ֑ךְ}
				
				\item Is 48:21\hebword{בׇּֽחֳרָבוֹת֙} This kamatz katan is subject to debate between experts and reading traditions.
				
				\item Is 49:8\hebword{וְאֶצׇּרְךָ֗}
				
				\item Is 49:19\hebword{חׇרְבֹתַ֙יִךְ֙}
				
				\item Is 49:20\hebword{בְאׇזְנַ֔יִךְ}
				
				\item Is 50:7\hebword{יַֽעֲזׇר־לִ֔י}
				
				\item Is 50:9\hebword{יַעֲזׇר־לִ֔י}
				
				\item Is 51:3\hebword{כׇּל־חׇרְבֹתֶ֔יהָ}
				
				\item Is 52:9\hebword{חׇרְב֖וֹת}
				
				\item Is 52:10\hebword{קׇדְשׁ֔וֹ}
				
				\item Is 54:2\hebword{אׇהֳלֵ֗ךְ} This kamatz katan is subject to debate between experts and reading traditions.
				
				\item Is 54:9\hebword{וּמִגְּעׇר־בָּֽךְ}
				
				\item Is 55:2\hebword{לְשׇׂבְעָ֑ה}
				
				\item Is 55:3\hebword{אׇזְנְכֶם֙}
				
				\item Is 56:7\hebword{קׇדְשִׁ֗י}
				
				\item Is 56:11\hebword{שׇׂבְעָ֔ה}
				
				\item Is 57:8\hebword{וַתִּכְרׇת־לָ֣ךְ}
				
				\item Is 57:13\hebword{הַר־קׇדְשִֽׁי}
				
				\item Is 58:6\hebword{חׇפְשִׁ֔ים}
				
				\item Is 58:10\hebword{כַּֽצׇּהֳרָֽיִם} This kamatz katan is subject to debate between experts and reading traditions.
				
				\item Is 58:12\hebword{חׇרְב֣וֹת}
				
				\item Is 58:13\hebword{קׇדְשִׁ֑י}
				
				\item Is 59:1\hebword{אׇזְנ֖וֹ}
				
				\item Is 59:10\hebword{בַֽצׇּהֳרַ֙יִם֙} This kamatz katan is subject to debate between experts and reading traditions.
				
				\item Is 60:9\hebword{וׇֽאֳנִיּ֤וֹת} This kamatz katan is subject to debate between experts and reading traditions.
				
				\item Is 61:4\hebword{חׇרְב֣וֹת}
				
				\item Is 61:7\hebword{בׇּשְׁתְּכֶם֙}
				
				\item Is 62:9\hebword{קׇדְשִֽׁי}
				
				\item Is 63:1\hebword{מִבׇּצְרָ֔ה}
				
				\item Is 63:10\hebword{קׇדְשׁ֑וֹ}
				
				\item Is 63:11\hebword{קׇדְשֽׁוֹ}
				
				\item Is 63:15\hebword{קׇדְשְׁךָ֖}
				
				\item Is 63:18\hebword{עַם־קׇדְשֶׁ֑ךָ}
				
				\item Is 64:9\hebword{קׇדְשְׁךָ֖}
				
				\item Is 64:10\hebword{קׇדְשֵׁ֣נוּ}
				
				\item Is 64:10\hebword{לְחׇרְבָּֽה}
				
				\item Is 65:11\hebword{קׇדְשִׁ֑י}
				
				\item Is 65:25\hebword{קׇדְשִׁ֖י}
				
				\item Is 66:12\hebword{תְּשׇׁעֳשָֽׁעוּ} This kamatz katan is subject to debate between experts and reading traditions.
				
				\item Is 66:20\hebword{קׇדְשִׁ֛י}
				
				\item Is 66:23\hebword{בְּחׇדְשׁ֔וֹ}
				
			\end{itemize}\end{multicols}
		\subsection{Jeremiah}
	\begin{multicols}{2}\begin{itemize}
				
				\item Jer 1:2\hebword{לְמׇלְכֽוֹ}
				
				\item Jer 1:17\hebword{מׇתְנֶ֔יךָ}
				
				\item Jer 2:2\hebword{בְאׇזְנֵ֨י}
			
				\item Jer 2:12\hebword{חׇרְב֥וּ}
						
						\item Jer 2:16\hebword{קׇדְקֹֽד}
						
						\item Jer 2:17\hebword{עׇזְבֵךְ֙}
						
						\item Jer 2:19\hebword{עׇזְבֵ֖ךְ}
						
						\item Jer 2:21\hebword{נׇכְרִיָּֽה}
						
						\item Jer 2:24\hebword{בְּחׇדְשָׁ֖הּ}
						
						\item Jer 2:35\hebword{עַל־אׇמְרֵ֖ךְ}
						
						\item Jer 3:17\hebword{כׇֽל־הַגּוֹיִ֛ם}
						
						\item Jer 3:25\hebword{בְּבׇשְׁתֵּ֗נוּ}
						
						\item Jer 4:4\hebword{עׇרְל֣וֹת}
						
						\item Jer 5:6\hebword{יְשׇׁדְדֵ֔ם}
						
						\item Jer 5:21\hebword{אׇזְנַ֥יִם}
						
						\item Jer 5:22\hebword{חׇק־עוֹלָ֖ם}
						
						\item Jer 5:24\hebword{יִשְׁמׇר־לָֽנוּ}
						
						\item Jer 6:4\hebword{בַֽצׇּהֳרָ֑יִם} This kamatz katan is subject to debate between experts and reading traditions.
						
						\item Jer 6:6\hebword{הׇפְקַ֔ד}
						
						\item Jer 6:10\hebword{אׇזְנָ֔ם}
						
						\item Jer 6:24\hebword{אֶת־שׇׁמְע֖וֹ}
						
						\item Jer 7:24\hebword{אֶת־אׇזְנָ֔ם}
						
						\item Jer 7:26\hebword{אֶת־אׇזְנָ֑ם}
						
						\item Jer 7:26\hebword{אֶת־עׇרְפָּ֔ם}
						
						\item Jer 7:29\hebword{גׇּזִּ֤י}
						
						\item Jer 7:34\hebword{לְחׇרְבָּ֖ה}
						
						\item Jer 8:9\hebword{וְחׇכְמַ֥ת}
						
						\item Jer 8:21\hebword{הׇשְׁבָּ֑רְתִּי}
						
						\item Jer 9:7\hebword{אׇרְבּֽוֹ}
						
						\item Jer 9:8\hebword{לֹא־אֶפְקׇד־בָּ֖ם}
						
						\item Jer 9:12\hebword{עַל־עׇזְבָם֙}
						
						\item Jer 9:19\hebword{אׇזְנְכֶ֖ם}
						
						\item Jer 9:22\hebword{בְּחׇכְמָת֔וֹ}
						
						\item Jer 9:22\hebword{בְּעׇשְׁרֽוֹ}
						
						\item Jer 9:24\hebword{בְּעׇרְלָֽה}
						
						\item Jer 10:12\hebword{בְּחׇכְמָת֑וֹ}
						
						\item Jer 10:20\hebword{אׇהֳלִ֣י} This kamatz katan is subject to debate between experts and reading traditions.
						
						\item Jer 10:20\hebword{אׇהֳלִ֔י} This kamatz katan is subject to debate between experts and reading traditions.
						
						\item Jer 11:8\hebword{אֶת־אׇזְנָ֔ם}
						
						\item Jer 11:10\hebword{לְעׇבְדָ֑ם}
						
						\item Jer 11:14\hebword{קׇרְאָ֥ם}
						
						\item Jer 12:9\hebword{לְאׇכְלָֽה}
						
						\item Jer 12:15\hebword{נׇתְשִׁ֣י}
						
						\item Jer 13:1\hebword{עַל־מׇתְנֶ֑יךָ}
						
						\item Jer 13:2\hebword{עַל־מׇתְנָֽי}
						
						\item Jer 13:4\hebword{עַל־מׇתְנֶ֑יךָ}
						
						\item Jer 13:4\hebword{וְטׇמְנֵ֥הוּ}
						
						\item Jer 13:6\hebword{לְטׇמְנוֹ־שָֽׁם}
						
						\item Jer 13:10\hebword{לְעׇבְדָ֖ם}
						
						\item Jer 13:11\hebword{אֶל־מׇתְנֵי־אִ֗ישׁ}
						
						\item Jer 13:19\hebword{הׇגְלָ֧ת}
						
						\item Jer 13:19\hebword{הׇגְלָ֥ת}
						
						\item Jer 14:3\hebword{וְהׇכְלְמ֖וּ}
						
						\item Jer 15:8\hebword{בַּֽצׇּהֳרָ֑יִם} This kamatz katan is subject to debate between experts and reading traditions.
						
						\item Jer 15:15\hebword{זׇכְרֵ֤נִי}
						
						\item Jer 15:15\hebword{וּפׇקְדֵ֙נִי֙}
						
						\item Jer 17:8\hebword{שׇׁרָשָׁ֔יו} This kamatz katan is subject to debate between experts and reading traditions.
						
						\item Jer 17:18\hebword{שׇׁבְרֵֽם}
						
						\item Jer 17:23\hebword{אֶת־אׇזְנָ֑ם}
						
						\item Jer 17:23\hebword{אֶת־עׇרְפָּ֔ם}
						
						\item Jer 18:3\hebword{עַל־הָאׇבְנָֽיִם}
						
						\item Jer 18:11\hebword{אֱמׇר־נָ֣א}
						
						\item Jer 18:20\hebword{עׇמְדִ֣י}
						
						\item Jer 18:22\hebword{לְלׇכְדֵ֔נִי}
						
						\item Jer 19:3\hebword{אׇזְנָֽיו}
						
						\item Jer 19:15\hebword{אֶת־עׇרְפָּ֔ם}
						
						\item Jer 20:3\hebword{מִֽמׇּחֳרָ֔ת} This kamatz katan is subject to debate between experts and reading traditions.
						
						\item Jer 20:16\hebword{צׇהֳרָֽיִם} This kamatz katan is subject to debate between experts and reading traditions.
						
						\item Jer 21:2\hebword{דְּרׇשׁ־נָ֤א}
						
						\item Jer 22:5\hebword{כִּֽי־לְחׇרְבָּ֥ה}
						
						\item Jer 22:24\hebword{כׇּנְיָ֤הוּ}
						
						\item Jer 22:28\hebword{כׇּנְיָ֔הוּ}
						
						\item Jer 23:9\hebword{קׇדְשֽׁוֹ}
						
						\item Jer 23:33\hebword{וְכִֽי־יִשְׁאׇלְךָ֩} This kamatz katan is subject to debate between experts and reading traditions.
						
						\item Jer 23:38\hebword{אֲמׇרְכֶ֛ם}
						
						\item Jer 24:1\hebword{אֶת־יְכׇנְיָ֣הוּ}
						
						\item Jer 25:4\hebword{אֶֽת־אׇזְנְכֶ֖ם}
						
						\item Jer 25:6\hebword{לְעׇבְדָ֖ם}
						
						\item Jer 25:9\hebword{וּלְחׇרְב֖וֹת}
						
						\item Jer 25:11\hebword{לְחׇרְבָּ֖ה}
						
						\item Jer 25:14\hebword{כְּפׇעֳלָ֖ם} This kamatz katan is subject to debate between experts and reading traditions.
						
						\item Jer 25:18\hebword{לְחׇרְבָּ֧ה}
						
						\item Jer 25:30\hebword{קׇדְשׁוֹ֙}
						
						\item Jer 26:11\hebword{בְּאׇזְנֵיכֶֽם}
						
						\item Jer 26:15\hebword{בְּאׇזְנֵיכֶ֔ם}
						
						\item Jer 27:6\hebword{לְעׇבְדֽוֹ}
						
						\item Jer 27:17\hebword{חׇרְבָּֽה}
						
						\item Jer 27:20\hebword{אֶת־יְכׇנְיָ֨ה}
						
						\item Jer 27:22\hebword{פׇּקְדִ֤י}
						
						\item Jer 28:4\hebword{וְאֶת־יְכׇנְיָ֣ה}
						
						\item Jer 28:4\hebword{מֶלֶךְ־יְ֠הוּדָׇ֠ה}
						
						\item Jer 28:7\hebword{בְּאׇזְנֶ֑יךָ}
						
						\item Jer 28:7\hebword{וּבְאׇזְנֵ֖י}
						
						\item Jer 28:17\hebword{וַיָּ֛מׇת}
						
						\item Jer 29:2\hebword{יְכׇנְיָֽה־הַ֠מֶּ֠לֶךְ}
						
								
								\item Jer 29:29\hebword{בְּאׇזְנֵ֖י}
								
								\item Jer 30:2\hebword{כְּתׇב־לְךָ֗}
								
								
								\item Jer 30:18\hebword{אׇהֳלֵ֣י} This kamatz katan is subject to debate between experts and reading traditions.
								
								
								\item Jer 32:5\hebword{עַד־פׇּקְדִ֥י}
								
								\item Jer 32:24\hebword{לְלׇכְדָהּ֒}
								
								\item Jer 34:9\hebword{חׇפְשִׁ֑ים}
								
								\item Jer 34:9\hebword{עֲבׇד־בָּ֛ם}
								
								\item Jer 34:10\hebword{חׇפְשִׁ֔ים}
								
								\item Jer 34:10\hebword{עֲבׇד־בָּ֖ם}
								
								\item Jer 34:11\hebword{חׇפְשִׁ֑ים}
								
								\item Jer 34:14\hebword{חׇפְשִׁ֖י}
								
								\item Jer 34:14\hebword{אֶת־אׇזְנָֽם}
								
								\item Jer 34:16\hebword{חׇפְשִׁ֖ים}
								
								\item Jer 35:7\hebword{בׇּאֳהָלִ֤ים} This kamatz katan is subject to debate between experts and reading traditions.
								
								\item Jer 35:10\hebword{בׇּאֳהָלִ֑ים} This kamatz katan is subject to debate between experts and reading traditions.
								
								\item Jer 35:15\hebword{לְעׇבְדָ֔ם}
								
								\item Jer 35:15\hebword{אֶֽת־אׇזְנְכֶ֔ם}
								
								\item Jer 36:6\hebword{בְּאׇזְנֵ֥י}
								
								\item Jer 36:6\hebword{בְּאׇזְנֵ֧י}
								
								\item Jer 36:10\hebword{בְּאׇזְנֵ֖י}
								
								\item Jer 36:13\hebword{בְּאׇזְנֵ֥י}
								
								\item Jer 36:14\hebword{בְּאׇזְנֵ֣י}
								
								\item Jer 36:15\hebword{בְּאׇזְנֵ֑ינוּ}
								
								\item Jer 36:15\hebword{בְּאׇזְנֵיהֶֽם}
								
								\item Jer 36:16\hebword{כְּשׇׁמְעָם֙}
								
								\item Jer 36:20\hebword{בְּאׇזְנֵ֣י}
								
								\item Jer 36:21\hebword{בְּאׇזְנֵ֣י}
								
								\item Jer 36:21\hebword{וּבְאׇזְנֵי֙}
								
								\item Jer 37:1\hebword{וַיִּ֨מְלׇךְ־מֶ֔לֶךְ}
								
								\item Jer 37:7\hebword{לְדׇרְשֵׁ֑נִי}
								
								\item Jer 37:10\hebword{בְּאׇֽהֳלוֹ֙} This kamatz katan is subject to debate between experts and reading traditions.
								
								\item Jer 37:20\hebword{תִּפׇּל־נָ֤א}
								
								\item Jer 38:9\hebword{וַיָּ֤מׇת}
								
								\item Jer 38:22\hebword{הׇטְבְּע֥וּ}
								
								\item Jer 39:2\hebword{הׇבְקְעָ֖ה}
								
								\item Jer 39:3\hebword{וְכׇ֨ל־שְׁאֵרִ֔ית}
								
								\item Jer 40:7\hebword{לֹא־הׇגְל֖וּ}
								
								\item Jer 40:11\hebword{כׇּֽל־הַיְּהוּדִ֡ים}
								
								\item Jer 41:2\hebword{וַיָּ֩קׇם֩}
								
								\item Jer 42:2\hebword{תִּפׇּל־נָ֤א}
								
								\item Jer 42:4\hebword{כׇּֽל־הַדָּבָר֩}
								
								\item Jer 44:2\hebword{חׇרְבָּה֙}
								
								\item Jer 44:5\hebword{אֶת־אׇזְנָ֔ם}
								
								\item Jer 44:6\hebword{לְחׇרְבָּ֥ה}
								
								\item Jer 44:22\hebword{לְחׇרְבָּ֨ה}
								
								\item Jer 44:30\hebword{חׇפְרַ֤ע}
								
								\item Jer 45:1\hebword{בְּכׇתְבוֹ֩}
								
								\item Jer 46:28\hebword{בְּכׇֽל־הַגּוֹיִ֣ם}
								
								\item Jer 47:5\hebword{קׇרְחָה֙}
								
								\item Jer 48:24\hebword{וְעַל־בׇּצְרָ֑ה}
								
								\item Jer 48:29\hebword{גׇּבְה֧וֹ}
								
								\item Jer 48:37\hebword{קׇרְחָ֔ה}
								
								\item Jer 48:37\hebword{וְעַל־מׇתְנַ֖יִם}
								
								\item Jer 48:45\hebword{וְקׇדְקֹ֖ד}
								
								\item Jer 49:7\hebword{חׇכְמָ֖ה}
								
								\item Jer 49:7\hebword{חׇכְמָתָֽם}
								
								\item Jer 49:8\hebword{הׇפְנוּ֙}
								
								\item Jer 49:13\hebword{בׇצְרָ֑ה}
								
								\item Jer 49:13\hebword{לְחׇרְב֥וֹת}
								
								\item Jer 49:22\hebword{עַל־בׇּצְרָ֑ה}
								
								\item Jer 49:29\hebword{אׇהֳלֵיהֶ֤ם} This kamatz katan is subject to debate between experts and reading traditions.
								
								\item Jer 50:15\hebword{אׇשְׁיוֹתֶ֔יהָ}
								
								\item Jer 50:29\hebword{כְּפׇעֳלָ֔הּ} This kamatz katan is subject to debate between experts and reading traditions.
								
								\item Jer 51:15\hebword{בְּחׇכְמָת֑וֹ}
								
								\item Jer 51:59\hebword{לְמׇלְכ֑וֹ}
								
								\item Jer 52:1\hebword{בְמׇלְכ֔וֹ}
								
								\item Jer 52:4\hebword{לְמׇלְכ֗וֹ}
								
								\item Jer 52:8\hebword{וְכׇ֨ל־חֵיל֔וֹ}
								
								\item Jer 52:21\hebword{וְעׇבְי֛וֹ}
								
							\end{itemize}\end{multicols}
						\subsection{Ezekiel}
					\begin{multicols}{2}\begin{itemize}
								
								\item Ezek 1:21\hebword{וּבְעׇמְדָ֖ם}
								
								\item Ezek 1:24\hebword{בְּעׇמְדָ֖ם}
								
								\item Ezek 1:25\hebword{בְּעׇמְדָ֖ם}
								
								\item Ezek 1:27\hebword{מׇתְנָ֖יו}
								
								\item Ezek 1:27\hebword{מׇתְנָיו֙}
								
								\item Ezek 3:10\hebword{וּבְאׇזְנֶ֥יךָ}
								
								\item Ezek 3:18\hebword{בְּאׇמְרִ֤י}
								
								\item Ezek 5:14\hebword{לְחׇרְבָּ֣ה}
								
								\item Ezek 5:17\hebword{יַעֲבׇר־בָּ֑ךְ}
								
								\item Ezek 6:11\hebword{וֶאֱמׇר־אָ֔ח}
								
								\item Ezek 7:18\hebword{קׇרְחָֽה}
								
								\item Ezek 8:2\hebword{מׇתְנָ֛יו}
								
								\item Ezek 8:2\hebword{וּמִמׇּתְנָ֣יו}
								
								\item Ezek 8:6\hebword{לְרׇֽחֳקָה֙} This kamatz katan is subject to debate between experts and reading traditions.
								
								\item Ezek 8:8\hebword{חֲתׇר־נָ֣א}
								
								\item Ezek 8:18\hebword{בְאׇזְנַי֙}
								
								\item Ezek 9:1\hebword{בְאׇזְנַ֗י}
								
								\item Ezek 9:2\hebword{מׇפְנֶ֣ה}
								
								\item Ezek 9:2\hebword{בְּמׇתְנָ֑יו}
								
								\item Ezek 9:3\hebword{בְּמׇתְנָֽיו}
								
								\item Ezek 9:5\hebword{בְּאׇזְנַ֔י}
								
								\item Ezek 9:8\hebword{בְּשׇׁפְכְּךָ֥}
								
								\item Ezek 9:11\hebword{בְּמׇתְנָ֔יו}
								
								\item Ezek 10:2\hebword{חׇפְנֶ֤יךָ}
								
								\item Ezek 10:4\hebword{וַיָּ֤רׇם}
								
								\item Ezek 10:7\hebword{אֶל־חׇפְנֵ֖י}
								
								\item Ezek 10:13\hebword{בְּאׇזְנָֽי}
								
								\item Ezek 10:17\hebword{בְּעׇמְדָ֣ם}
								
								\item Ezek 12:2\hebword{אׇזְנַ֨יִם}
								
								\item Ezek 12:5\hebword{חֲתׇר־לְךָ֣}
								
								\item Ezek 12:18\hebword{בְּרׇגְזָ֥ה}
								
								\item Ezek 13:4\hebword{בׇּחֳרָב֑וֹת} This kamatz katan is subject to debate between experts and reading traditions.
								
								\item Ezek 14:7\hebword{לִדְרׇשׁ־ל֣וֹ}
								
								\item Ezek 14:13\hebword{לִמְעׇל־מַ֔עַל}
								
								\item Ezek 15:4\hebword{לְאׇכְלָ֑ה}
										
										\item Ezek 15:6\hebword{לְאׇכְלָ֑ה}
										
										\item Ezek 16:4\hebword{וְהׇמְלֵ֙חַ֙}
										
										\item Ezek 16:4\hebword{וְהׇחְתֵּ֖ל}
										
										\item Ezek 16:12\hebword{עַל־אׇזְנָ֑יִךְ}
										
										\item Ezek 16:14\hebword{בְּיׇפְיֵ֑ךְ}
										
										\item Ezek 16:15\hebword{בְיׇפְיֵ֔ךְ}
										
										\item Ezek 16:25\hebword{אֶת־יׇפְיֵ֔ךְ}
										
										\item Ezek 16:28\hebword{שׇׂבְעָתֵ֑ךְ}
										
										\item Ezek 17:6\hebword{וְשׇׁרָשָׁ֖יו} This kamatz katan is subject to debate between experts and reading traditions.
										
										\item Ezek 17:7\hebword{שׇׁרָשֶׁ֣יהָ} This kamatz katan is subject to debate between experts and reading traditions.
										
										\item Ezek 17:9\hebword{אֶת־שׇׁרָשֶׁ֨יהָ} This kamatz katan is subject to debate between experts and reading traditions.
										
										\item Ezek 17:9\hebword{מִשׇּׁרָשֶֽׁיהָ} This kamatz katan is subject to debate between experts and reading traditions.
										
										\item Ezek 17:12\hebword{אֱמׇר־נָא֙}
										
										\item Ezek 17:14\hebword{לְעׇמְדָֽהּ}
										
										\item Ezek 17:15\hebword{וַיִּמְרׇד־בּ֗וֹ}
										
										\item Ezek 18:28\hebword{וַיָּ֔שׇׁב}
										
										\item Ezek 19:3\hebword{לִטְרׇף־טֶ֖רֶף}
										
										\item Ezek 19:6\hebword{לִטְרׇף־טֶ֖רֶף}
										
										\item Ezek 19:11\hebword{בְגׇבְה֔וֹ}
										
										\item Ezek 20:5\hebword{בׇּחֳרִ֣י} This kamatz katan is subject to debate between experts and reading traditions.
										
										\item Ezek 20:17\hebword{וַתָּ֧חׇס}
										
										\item Ezek 20:28\hebword{קׇרְבָּנָ֔ם}
										
										\item Ezek 20:39\hebword{קׇדְשִׁי֙}
										
										\item Ezek 20:40\hebword{בְהַר־קׇדְשִׁ֞י}
										
										\item Ezek 20:40\hebword{בְּכׇל־קׇדְשֵׁיכֶֽם}
										
										\item Ezek 21:11\hebword{מׇתְנַ֙יִם֙}
										
										\item Ezek 21:16\hebword{לְמׇרְטָ֖ה}
										
										\item Ezek 21:26\hebword{לִקְסׇם־קָ֑סֶם}
										
										\item Ezek 21:28\hebword{כִּקְסׇם־שָׁוְא֙}
												
												\item Ezek 21:34\hebword{בִּקְסׇם־לָ֖ךְ}
												
												\item Ezek 21:37\hebword{לְאׇכְלָ֔ה}
												
												\item Ezek 22:3\hebword{לְטׇמְאָֽה}
												
												\item Ezek 22:6\hebword{שְׁפׇךְ־דָּֽם}
												
												\item Ezek 22:8\hebword{קׇדָשַׁ֖י} This kamatz katan is subject to debate between experts and reading traditions.
												
												\item Ezek 22:9\hebword{שְׁפׇךְ־דָּ֑ם}
												
												\item Ezek 22:12\hebword{שְׁפׇךְ־דָּ֑ם}
												
												\item Ezek 22:24\hebword{אֱמׇר־לָ֕הּ}
												
												\item Ezek 22:26\hebword{קׇדָשַׁי֒} This kamatz katan is subject to debate between experts and reading traditions.
												
												\item Ezek 22:27\hebword{לִשְׁפׇּךְ־דָּם֙}
												
												\item Ezek 23:4\hebword{אׇהֳלָ֤ה} This kamatz katan is subject to debate between experts and reading traditions.
												
												\item Ezek 23:4\hebword{וְאׇהֳלִיבָ֣ה} This kamatz katan is subject to debate between experts and reading traditions.
												
												\item Ezek 23:4\hebword{אׇהֳלָ֔ה} This kamatz katan is subject to debate between experts and reading traditions.
												
												\item Ezek 23:4\hebword{אׇהֳלִיבָֽה} This kamatz katan is subject to debate between experts and reading traditions.
												
												\item Ezek 23:5\hebword{אׇהֳלָ֖ה} This kamatz katan is subject to debate between experts and reading traditions.
												
												\item Ezek 23:11\hebword{אׇהֳלִיבָ֔ה} This kamatz katan is subject to debate between experts and reading traditions.
												
												\item Ezek 23:15\hebword{בְּמׇתְנֵיהֶ֗ם}
												
												\item Ezek 23:22\hebword{אׇהֳלִיבָ֗ה} This kamatz katan is subject to debate between experts and reading traditions.
												
												\item Ezek 23:25\hebword{וְאׇזְנַ֙יִךְ֙}
												
												\item Ezek 23:36\hebword{אֶֽת־אׇהֳלָ֖ה} This kamatz katan is subject to debate between experts and reading traditions.
												
												\item Ezek 23:36\hebword{וְאֶת־אׇהֳלִיבָ֑ה} This kamatz katan is subject to debate between experts and reading traditions.
												
												\item Ezek 23:37\hebword{לְאׇכְלָֽה}
												
												\item Ezek 23:42\hebword{סׇבָאִ֖ים} This kamatz katan is subject to debate between experts and reading traditions.
												
												\item Ezek 23:44\hebword{אֶֽל־אׇהֳלָה֙} This kamatz katan is subject to debate between experts and reading traditions.
												
												\item Ezek 23:44\hebword{וְאֶל־אׇ֣הֳלִיבָ֔ה} This kamatz katan is subject to debate between experts and reading traditions.
												
												\item Ezek 24:2\hebword{כְּתׇב־לְךָ֙}
												
												\item Ezek 24:18\hebword{וַתָּ֥מׇת}
												
												\item Ezek 24:26\hebword{אׇזְנָֽיִם}
												
												\item Ezek 25:3\hebword{אׇמְרֵ֨ךְ}
												
												\item Ezek 25:13\hebword{חׇרְבָּה֙}
												
												\item Ezek 26:9\hebword{קׇֽבׇלּ֔וֹ} This kamatz katan is subject to debate between experts and reading traditions.
												
												\item Ezek 26:20\hebword{כׇּחֳרָב֤וֹת} This kamatz katan is subject to debate between experts and reading traditions.
												
												\item Ezek 27:4\hebword{יׇפְיֵֽךְ}
												
												\item Ezek 27:15\hebword{וְהׇבְנִ֔ים}
												
												\item Ezek 27:31\hebword{קׇרְחָ֔ה}
												
												\item Ezek 28:4\hebword{בְּחׇכְמָֽתְךָ֙}
												
												\item Ezek 28:5\hebword{חׇכְמָתְךָ֛}
												
												\item Ezek 28:7\hebword{חׇכְמָתֶ֔ךָ}
												
												\item Ezek 28:12\hebword{תׇּכְנִ֔ית}
												
												\item Ezek 28:12\hebword{חׇכְמָ֖ה}
												
												\item Ezek 28:17\hebword{בְּיׇפְיֶ֔ךָ}
												
												\item Ezek 28:17\hebword{חׇכְמָתְךָ֖}
												
												\item Ezek 29:5\hebword{לְאׇכְלָֽה}
												
												\item Ezek 29:7\hebword{בְּתׇפְשָׂ֨ם}
														
														\item Ezek 29:7\hebword{כׇּל־מׇתְנָֽיִם}
														
														\item Ezek 29:9\hebword{וְחׇרְבָּ֔ה}
														
														\item Ezek 29:10\hebword{לְחׇרְבוֹת֙}
														
														\item Ezek 29:11\hebword{תַֽעֲבׇר־בָּהּ֙}
														
														\item Ezek 29:12\hebword{מׇֽחֳרָבוֹת֙} This kamatz katan is subject to debate between experts and reading traditions.
														
														\item Ezek 30:12\hebword{חׇֽרָבָ֔ה} This kamatz katan is subject to debate between experts and reading traditions.
														
														\item Ezek 30:21\hebword{לְחׇבְשָׁ֥הּ}
														
														\item Ezek 30:21\hebword{לְחׇזְקָ֖הּ}
														
														\item Ezek 31:2\hebword{בְגׇדְלֶֽךָ}
														
														\item Ezek 31:7\hebword{בְּגׇדְל֔וֹ}
														
														\item Ezek 31:7\hebword{שׇׁרְשׁ֖וֹ}
														
														\item Ezek 31:8\hebword{בְּיׇפְיֽוֹ}
														
														\item Ezek 31:10\hebword{בְּגׇבְהֽוֹ}
														
														\item Ezek 31:14\hebword{בְּגׇבְהָ֖ם}
														
														\item Ezek 32:19\hebword{וְהׇשְׁכְּבָ֖ה}
														
														\item Ezek 33:8\hebword{בְּאׇמְרִ֣י}
														
														\item Ezek 33:13\hebword{בְּאׇמְרִ֤י}
														
														\item Ezek 33:14\hebword{וּבְאׇמְרִ֥י}
														
														\item Ezek 33:27\hebword{לְאׇכְל֑וֹ}
														
														\item Ezek 34:4\hebword{וּבְחׇזְקָ֛ה}
														
														\item Ezek 34:5\hebword{לְאׇכְלָ֛ה}
														
														\item Ezek 34:8\hebword{לְאׇכְלָ֜ה}
														
														\item Ezek 34:10\hebword{לְאׇכְלָֽה}
														
														\item Ezek 35:4\hebword{חׇרְבָּ֣ה}
														
														\item Ezek 35:10\hebword{אֲ֠מׇרְךָ֠}
														
														\item Ezek 35:12\hebword{לְאׇכְלָֽה}
														
														\item Ezek 36:20\hebword{קׇדְשִׁ֑י}
														
														\item Ezek 36:21\hebword{קׇדְשִׁ֑י}
														
														\item Ezek 36:22\hebword{אִם־לְשֵׁם־קׇדְשִׁי֙}
														
														\item Ezek 36:38\hebword{קׇדָשִׁ֗ים} This kamatz katan is subject to debate between experts and reading traditions.
														
														\item Ezek 38:8\hebword{לְחׇרְבָּ֖ה}
														
														\item Ezek 38:22\hebword{וְגׇפְרִ֗ית}
														
														\item Ezek 39:4\hebword{לְאׇכְלָֽה}
														
														\item Ezek 39:7\hebword{קׇדְשִׁ֜י}
														
														\item Ezek 39:7\hebword{אֶת־שֵׁם־קׇדְשִׁ֖י}
														
														\item Ezek 39:19\hebword{לְשׇׂבְעָ֔ה}
														
														\item Ezek 39:25\hebword{קׇדְשִֽׁי}
														
														\item Ezek 40:4\hebword{וּבְאׇזְנֶ֨יךָ}
														
														\item Ezek 40:5\hebword{וַיָּ֜מׇד}
														
														\item Ezek 40:6\hebword{וַיָּ֣מׇד}
														
														\item Ezek 40:8\hebword{וַיָּ֜מׇד}
														
														\item Ezek 40:9\hebword{וַיָּ֜מׇד}
														
														\item Ezek 40:10\hebword{לִשְׁלׇשְׁתָּ֑ם}
														
														\item Ezek 40:11\hebword{וַיָּ֛מׇד}
														
														\item Ezek 40:13\hebword{וַיָּ֣מׇד}
														
														\item Ezek 40:19\hebword{וַיָּ֣מׇד}
														
														\item Ezek 40:20\hebword{אׇרְכּ֖וֹ}
														
														\item Ezek 40:20\hebword{וְרׇחְבּֽוֹ}
														
														\item Ezek 40:21\hebword{אׇרְכּ֔וֹ}
														
														\item Ezek 40:23\hebword{וַיָּ֧מׇד}
														
														\item Ezek 40:27\hebword{וַיָּ֨מׇד}
														
														\item Ezek 40:28\hebword{וַיָּ֙מׇד֙}
														
														\item Ezek 40:32\hebword{וַיָּ֣מׇד}
														
														\item Ezek 40:43\hebword{הַקׇּרְבָֽן}
														
														\item Ezek 40:47\hebword{וַיָּ֨מׇד}
														
														\item Ezek 41:1\hebword{וַיָּ֣מׇד}
														
														\item Ezek 41:2\hebword{וַיָּ֤מׇד}
														
														\item Ezek 41:2\hebword{אׇרְכּוֹ֙}
														
														\item Ezek 41:3\hebword{וַיָּ֥מׇד}
														
														\item Ezek 41:4\hebword{וַיָּ֨מׇד}
														
														\item Ezek 41:4\hebword{אֶת־אׇרְכּ֜וֹ}
														
														\item Ezek 41:5\hebword{וַיָּ֥מׇד}
														
														\item Ezek 41:12\hebword{וְאׇרְכּ֖וֹ}
														
														\item Ezek 41:16\hebword{לִשְׁלׇשְׁתָּ֔ם}
														
														\item Ezek 41:22\hebword{וְאׇרְכּ֣וֹ}
														
														\item Ezek 41:22\hebword{וְאׇרְכּ֥וֹ}
														
														\item Ezek 42:7\hebword{אׇרְכּ֖וֹ}
														
														\item Ezek 42:11\hebword{כְּאׇרְכָּ֖ן}
														
														\item Ezek 42:11\hebword{רׇחְבָּ֑ן}
														
														\item Ezek 42:13\hebword{קׇדְשֵׁ֣י}
														
														\item Ezek 42:13\hebword{קׇדְשֵׁ֣י}
														
														\item Ezek 43:7\hebword{אֶשְׁכׇּן־שָׁ֛ם}
														
														\item Ezek 43:7\hebword{קׇדְשִׁ֞י}
														
														\item Ezek 43:8\hebword{קׇדְשִׁ֗י}
														
														\item Ezek 43:10\hebword{אֶת־תׇּכְנִֽית}
														
														\item Ezek 43:12\hebword{קׇדָשִׁ֔ים} This kamatz katan is subject to debate between experts and reading traditions.
														
														\item Ezek 44:3\hebword{לֶאֱכׇל־לֶ֖חֶם}
														
														\item Ezek 44:5\hebword{וּבְאׇזְנֶ֣יךָ}
														
														\item Ezek 44:8\hebword{קׇדָשָׁ֑י} This kamatz katan is subject to debate between experts and reading traditions.
														
														\item Ezek 44:9\hebword{לְכׇ֨ל־בֶּן־נֵכָ֔ר}
														
														\item Ezek 44:13\hebword{עַל־כׇּל־קׇ֣דָשַׁ֔י} This kamatz katan is subject to debate between experts and reading traditions.
														
														\item Ezek 44:13\hebword{אֶל־קׇדְשֵׁ֖י}
														
														\item Ezek 44:18\hebword{עַל־מׇתְנֵיהֶ֑ם}
														
														\item Ezek 44:25\hebword{לְטׇמְאָ֑ה}
														
														\item Ezek 44:26\hebword{טׇהֳרָת֑וֹ} This kamatz katan is subject to debate between experts and reading traditions.
														
														\item Ezek 45:3\hebword{קׇדָשִֽׁים} This kamatz katan is subject to debate between experts and reading traditions.
														
														\item Ezek 47:3\hebword{וַיָּ֤מׇד}
														
														\item Ezek 47:3\hebword{אׇפְסָֽיִם}
														
														\item Ezek 47:4\hebword{וַיָּ֣מׇד}
														
														\item Ezek 47:4\hebword{וַיָּ֣מׇד}
														
														\item Ezek 47:4\hebword{מׇתְנָֽיִם}
														
														\item Ezek 47:5\hebword{וַיָּ֣מׇד}
														
														\item Ezek 47:12\hebword{לׇחֳדָשָׁיו֙} This kamatz katan is subject to debate between experts and reading traditions.
														
														\item Ezek 48:12\hebword{קׇדָשִׁ֑ים} This kamatz katan is subject to debate between experts and reading traditions.
														
													\end{itemize}\end{multicols}
												\section{Twelve Minor Prophets}
												
												\subsection{Hosea}
												
											\begin{multicols}{2}\begin{itemize}
														
														\item Hosea 1:1\hebword{יָרׇבְעָ֥ם}
														
														\item Hosea 2:13\hebword{חׇדְשָׁ֣הּ}
														
														\item Hosea 4:18\hebword{סׇבְאָ֑ם}
														
														\item Hosea 5:13\hebword{אֶת־חׇלְי֗וֹ}
														
														\item Hosea 7:1\hebword{כְּרׇפְאִ֣י}
														
														\item Hosea 7:6\hebword{בְּאׇרְבָּ֑ם}
														
														\item Hosea 8:12\hebword{אֶ֨כְתׇּב־ל֔וֹ}
																
																\item Hosea 9:1\hebword{כׇּל־גׇּרְנ֥וֹת}
																
																\item Hosea 9:6\hebword{בְּאׇהֳלֵיהֶֽם} This kamatz katan is subject to debate between experts and reading traditions.
																
																\item Hosea 9:10\hebword{כְּאׇהֳבָֽם} This kamatz katan is subject to debate between experts and reading traditions.
																
																\item Hosea 9:16\hebword{שׇׁרְשָׁ֥ם}
																
																\item Hosea 10:6\hebword{בׇּשְׁנָה֙}
																
																\item Hosea 10:10\hebword{בְּאׇסְרָ֖ם}
																
																\item Hosea 12:10\hebword{בׇאֳהָלִ֖ים} This kamatz katan is subject to debate between experts and reading traditions.
																
																\item Hosea 13:6\hebword{וַיָּ֣רׇם}
																
																\item Hosea 13:14\hebword{קָֽטׇבְךָ֙}
																
																\item Hosea 14:6\hebword{שׇׁרָשָׁ֖יו} This kamatz katan is subject to debate between experts and reading traditions.
																
															\end{itemize}\end{multicols}
														\subsection{Joel}
													\begin{multicols}{2}\begin{itemize}
																
																\item Joel 1:9\hebword{הׇכְרַ֥ת}
																
																\item Joel 2:1\hebword{קׇדְשִׁ֔י}
																
																\item Joel 2:10\hebword{נׇגְהָֽם}
																
																\item Joel 2:17\hebword{לִמְשׇׁל־בָּ֣ם}
																
																\item Joel 4:11\hebword{כׇֽל־הַגּוֹיִ֛ם}
																
																\item Joel 4:15\hebword{נׇגְהָֽם}
																
																\item Joel 4:17\hebword{הַר־קׇדְשִׁ֑י}
																
																								\end{itemize}\end{multicols}
															\subsection{Amos}
														\begin{multicols}{2}\begin{itemize}
																
																\item Amos 1:1\hebword{יָרׇבְעָ֤ם}
																
																\item Amos 1:11\hebword{עַל־רׇדְפ֨וֹ}
																
																\item Amos 1:12\hebword{בׇּצְרָֽה}
																
																\item Amos 2:1\hebword{עַל־שׇׂרְפ֛וֹ}
																
																\item Amos 2:4\hebword{עַֽל־מׇאֳסָ֞ם} This kamatz katan is subject to debate between experts and reading traditions.
																
																\item Amos 2:7\hebword{קׇדְשִֽׁי}
																
																\item Amos 2:9\hebword{גׇּבְה֔וֹ}
																
																\item Amos 2:9\hebword{וְשׇׁרָשָׁ֖יו} This kamatz katan is subject to debate between experts and reading traditions.
																
																\item Amos 3:14\hebword{פׇּקְדִ֥י}
																
																\item Amos 4:2\hebword{בְּקׇדְשׁ֔וֹ}
																
																\item Amos 4:13\hebword{עַל־בׇּ֣מֳתֵי} This kamatz katan is subject to debate between experts and reading traditions.
																
																\item Amos 6:13\hebword{בְחׇזְקֵ֔נוּ}
																
																\item Amos 7:9\hebword{יָרׇבְעָ֖ם}
																
																\item Amos 7:10\hebword{אֶל־יָרׇבְעָ֥ם}
																
																\item Amos 7:11\hebword{יָרׇבְעָ֑ם}
																
																\item Amos 8:9\hebword{בַּֽצׇּהֳרָ֑יִם} This kamatz katan is subject to debate between experts and reading traditions.
																
																\item Amos 8:10\hebword{עַל־כׇּל־מׇתְנַ֙יִם֙}
																
																\item Amos 8:10\hebword{קׇרְחָ֑ה}
																
																\item Amos 9:9\hebword{בְכׇֽל־הַגּוֹיִ֖ם}
																
																								\end{itemize}\end{multicols}
															\subsection{Obadiah}
														\begin{multicols}{2}\begin{itemize}
																
																\item Obd 1:11\hebword{עֲמׇֽדְךָ֣} This kamatz katan is subject to debate between experts and reading traditions.
																
																\item Obd 1:11\hebword{וְנׇכְרִ֞ים}
																
																\item Obd 1:12\hebword{נׇכְר֔וֹ}
																
																\item Obd 1:12\hebword{אׇבְדָ֑ם}
																
																\item Obd 1:16\hebword{קׇדְשִׁ֔י}
																
																								\end{itemize}\end{multicols}
															\subsection{Jonah}
														\begin{multicols}{2}\begin{itemize}
																
																\item Jonah 1:3\hebword{וַיָּ֤קׇם}
																
																\item Jonah 2:5\hebword{קׇדְשֶֽׁךָ}
																
																\item Jonah 2:8\hebword{קׇדְשֶֽׁךָ}
																
																\item Jonah 3:3\hebword{וַיָּ֣קׇם}
																
																\item Jonah 3:6\hebword{וַיָּ֙קׇם֙}
																
																\item Jonah 3:8\hebword{בְּחׇזְקָ֑ה}
																
																\item Jonah 4:7\hebword{לַֽמׇּחֳרָ֑ת} This kamatz katan is subject to debate between experts and reading traditions.
																
																								\end{itemize}\end{multicols}
															\subsection{Micah}
														\begin{multicols}{2}\begin{itemize}
																
																\item Micah 1:2\hebword{קׇדְשֽׁוֹ}
																
																\item Micah 1:3\hebword{בׇּ֥מֳתֵי} This kamatz katan is subject to debate between experts and reading traditions.
																
																\item Micah 1:16\hebword{קׇרְחִ֣י}
																
																\item Micah 1:16\hebword{קׇרְחָתֵךְ֙}
																
																\item Micah 2:12\hebword{בׇּצְרָ֑ה}
																
																\item Micah 6:5\hebword{זְכׇר־נָא֙}
																
																\item Micah 6:16\hebword{עׇמְרִ֗י}
																
																\item Micah 7:1\hebword{כְּאׇסְפֵּי־קַ֔יִץ}
																
																\item Micah 7:16\hebword{אׇזְנֵיהֶ֖ם}
																
																								\end{itemize}\end{multicols}
															\subsection{Nahum}
														\begin{multicols}{2}\begin{itemize}
																
																\item Nahum 1:3\hebword{וּגְדׇל־כֹּ֔חַ}
											
																		
																		\item Nahum 1:10\hebword{וּכְסׇבְאָ֖ם}
																		
																		\item Nahum 2:1\hebword{לַעֲבׇר־בָּ֥ךְ}
																				
																				\item Nahum 2:2\hebword{מׇתְנַ֔יִם}
																				
																				\item Nahum 2:4\hebword{הׇרְעָֽלוּ}
																				
																				\item Nahum 2:11\hebword{בְּכׇל־מׇתְנַ֔יִם}
																				
																				\item Nahum 3:12\hebword{כׇּ֨ל־מִבְצָרַ֔יִךְ}
																				
																												\end{itemize}\end{multicols}
																			\subsection{Habakkuk}
																		\begin{multicols}{2}\begin{itemize}
																				
																				\item Hab 2:20\hebword{קׇדְשׁ֑וֹ}
																				
																				\item Hab 3:2\hebword{פׇּֽעׇלְךָ֙} This kamatz katan is subject to debate between experts and reading traditions.
																				
																				\item Hab 3:7\hebword{אׇהֳלֵ֣י} This kamatz katan is subject to debate between experts and reading traditions.
																				
																												\end{itemize}\end{multicols}
																			\subsection{Zephaniah}
																		\begin{multicols}{2}\begin{itemize}
																				
																				\item Zeph 1:8\hebword{נׇכְרִֽי}
																				
																				\item Zeph 2:4\hebword{בַּֽצׇּהֳרַ֙יִם֙} This kamatz katan is subject to debate between experts and reading traditions.
																				
																				\item Zeph 3:8\hebword{לְקׇבְצִ֣י}
																				
																				\item Zeph 3:9\hebword{לְעׇבְד֖וֹ}
																				
																				\item Zeph 3:11\hebword{לְגׇבְהָ֛ה}
																				
																				\item Zeph 3:11\hebword{קׇדְשִֽׁי}
																				
																				\item Zeph 3:14\hebword{וְעׇלְזִי֙}
																				
																				\item Zeph 3:19\hebword{בׇּשְׁתָּֽם}
																				
																												\end{itemize}\end{multicols}
																			\subsection{Haggai}
																		\begin{multicols}{2}\begin{itemize}
																				
																				\item Haggai 1:6\hebword{וְאֵין־לְשׇׂבְעָה֙}
																				
																				\item Haggai 1:6\hebword{וְאֵין־לְשׇׁכְרָ֔ה}
																				
																				\item Haggai 2:2\hebword{אֱמׇר־נָ֗א}
																				
																												\end{itemize}\end{multicols}
																			\subsection{Zechariah}
																		\begin{multicols}{2}\begin{itemize}
																				
																				\item Zec 2:6\hebword{כַּמָּֽה־רׇחְבָּ֖הּ}
																				
																				\item Zec 2:6\hebword{אׇרְכָּֽהּ}
																				
																				\item Zec 2:17\hebword{קׇדְשֽׁוֹ}
																				
																				\item Zec 4:1\hebword{וַיָּ֕שׇׁב}
																				
																				\item Zec 5:2\hebword{אׇרְכָּהּ֙}
																				
																				\item Zec 5:2\hebword{וְרׇחְבָּ֖הּ}
																						
																						\item Zec 7:11\hebword{וְאׇזְנֵיהֶ֖ם}
																						
																						\item Zec 9:2\hebword{תִּגְבׇּל־בָּ֑הּ}
																						
																						\item Zec 9:3\hebword{וַתִּצְבׇּר־כֶּ֙סֶף֙}
																						
																						\item Zec 9:17\hebword{וּמַה־יׇּפְי֑וֹ}
																								
																								\item Zec 12:7\hebword{אֶת־אׇהֳלֵ֥י} This kamatz katan is subject to debate between experts and reading traditions.
																								
																							\end{itemize}\end{multicols}
\subsection{Malachi}
\begin{multicols}{2}\begin{itemize}
																								
																								\item Malachi 1:7\hebword{בֶּאֱמׇרְכֶ֕ם}
																								
																								\item Malachi 1:9\hebword{וִֽיחׇנֵּ֑נוּ}
																								
																								\item Malachi 1:12\hebword{בֶּאֱמׇרְכֶ֗ם}
																								
																								\item Malachi 1:12\hebword{אׇכְלֽוֹ}
																								
																								\item Malachi 1:14\hebword{מׇשְׁחָ֖ת}
																								
																								\item Malachi 2:12\hebword{מֵאׇהֳלֵ֖י} This kamatz katan is subject to debate between experts and reading traditions.
																								
																								\item Malachi 2:17\hebword{בֶּאֱמׇרְכֶ֗ם}
\end{itemize}\end{multicols}

\chapter{The Writings}

\section{The Five Megillot}

\subsection{Song of Songs}

\begin{multicols}{2}\begin{itemize}
		
	\item Song of Songs 1:4\hebword{מׇשְׁכֵ֖נִי}
	
	\item Song of Songs 1:5\hebword{כְּאׇהֳלֵ֣י} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Song of Songs 1:7\hebword{בַּֽצׇּהֳרָ֑יִם} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Song of Songs 2:9\hebword{כׇּתְלֵ֔נוּ}
	
	\item Song of Songs 5:3\hebword{אֶת־כֻּתׇּנְתִּ֔י}
	
	\item Song of Songs 7:2\hebword{אׇמָּֽן}
	
	\item Song of Songs 7:3\hebword{שׇׁרְרֵךְ֙}
	
	\item Song of Songs 7:4\hebword{תׇּאֳמֵ֥י} This kamatz katan is subject to debate between experts and reading traditions.
	
\end{itemize}\end{multicols}

\subsection{Ruth}

\begin{multicols}{2}\begin{itemize}
	
	\item Ruth 1:2\hebword{נׇעֳמִ֜י} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 1:3\hebword{נׇעֳמִ֑י} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 1:4\hebword{עׇרְפָּ֔ה}
	
	\item Ruth 1:6\hebword{וַתָּ֤קׇם}
	
	\item Ruth 1:6\hebword{וַתָּ֖שׇׁב}
	
	\item Ruth 1:8\hebword{נׇעֳמִי֙} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 1:11\hebword{נׇעֳמִי֙} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 1:14\hebword{עׇרְפָּה֙}
	
	\item Ruth 1:16\hebword{לְעׇזְבֵ֖ךְ}
	
	\item Ruth 1:19\hebword{נׇעֳמִֽי} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 1:20\hebword{נׇעֳמִ֑י} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 1:21\hebword{נׇעֳמִ֔י} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 1:22\hebword{וַתָּ֣שׇׁב}
	
	\item Ruth 1:22\hebword{נׇעֳמִ֗י} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 2:1\hebword{וּֽלְנׇעֳמִ֞י} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 2:2\hebword{אֶֽל־נׇעֳמִ֗י} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 2:6\hebword{עִֽם־נׇעֳמִ֖י} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 2:9\hebword{נׇגְעֵ֑ךְ}
	
	\item Ruth 2:12\hebword{פׇּעֳלֵ֑ךְ} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 2:14\hebword{וַיִּצְבׇּט־לָ֣הּ}
	
	\item Ruth 2:15\hebword{וַתָּ֖קׇם}
	
	\item Ruth 2:18\hebword{מִשׇּׂבְעָֽהּ}
	
	\item Ruth 2:20\hebword{נׇעֳמִ֜י} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 2:20\hebword{נׇעֳמִ֗י} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 2:22\hebword{נׇעֳמִ֖י} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 3:1\hebword{נׇעֳמִ֣י} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 3:4\hebword{בְשׇׁכְב֗וֹ}
	
	\item Ruth 3:12\hebword{אׇמְנָ֔ם}
	
	\item Ruth 3:13\hebword{לְגׇאֳלֵ֛ךְ} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 3:14\hebword{וַתָּ֕קׇם}
	
	\item Ruth 3:15\hebword{וַיָּ֤מׇד}
	
	\item Ruth 4:3\hebword{נׇעֳמִ֔י} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 4:4\hebword{אׇזְנְךָ֣}
	
	\item Ruth 4:5\hebword{נׇעֳמִ֑י} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 4:6\hebword{לִגְאׇל־לִ֔י}
	
	\item Ruth 4:9\hebword{נׇעֳמִֽי} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 4:14\hebword{אֶֽל־נׇעֳמִ֔י} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 4:16\hebword{נׇעֳמִ֤י} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Ruth 4:17\hebword{לְנׇעֳמִ֑י} This kamatz katan is subject to debate between experts and reading traditions.
	
\end{itemize}\end{multicols}

\subsection{Lamentations}

\begin{multicols}{2}\begin{itemize}
	
	\item Lam 1:7\hebword{עׇנְיָהּ֙}
	
	\item Lam 1:8\hebword{וַתָּ֥שׇׁב}
	
	\item Lam 1:9\hebword{אֶת־עׇנְיִ֔י}
	
	\item Lam 2:3\hebword{בׇּֽחֳרִי־אַ֗ף} This kamatz katan is subject to debate between experts and reading traditions.
			
			\item Lam 3:7\hebword{נְחׇשְׁתִּֽי}
			
			\item Lam 3:19\hebword{זְכׇר־עָנְיִ֥י}
			
			\item Lam 3:56\hebword{אׇזְנְךָ֛}
			
			\item Lam 3:59\hebword{שׇׁפְטָ֖ה}
			
			\item Lam 4:8\hebword{תׇּֽאֳרָ֔ם} This kamatz katan is subject to debate between experts and reading traditions.
			
			\item Lam 4:21\hebword{תַּעֲבׇר־כּ֔וֹס}
			
			\item Lam 5:2\hebword{לְנׇכְרִֽים}
			
		\end{itemize}\end{multicols}
	
\subsection{Ecclesiastes}

\begin{multicols}{2}\begin{itemize}
					
					\item Eccl 1:13\hebword{בַּֽחׇכְמָ֔ה}
					
					\item Eccl 1:16\hebword{חׇכְמָ֔ה}
					
					\item Eccl 1:16\hebword{חׇכְמָ֥ה}
					
					\item Eccl 1:17\hebword{חׇכְמָ֔ה}
					
					\item Eccl 1:18\hebword{חׇכְמָ֖ה}
					
					\item Eccl 1:18\hebword{רׇב־כָּ֑עַס}
					
					\item Eccl 2:3\hebword{בַּֽחׇכְמָה֙}
					
					\item Eccl 2:9\hebword{חׇכְמָתִ֖י}
					
					\item Eccl 2:12\hebword{חׇכְמָ֔ה}
					
					\item Eccl 2:13\hebword{לַֽחׇכְמָ֖ה}
					
					\item Eccl 2:21\hebword{בְּחׇכְמָ֥ה}
					
					\item Eccl 2:26\hebword{חׇכְמָ֥ה}
					
					\item Eccl 4:6\hebword{חׇפְנַ֛יִם}
					
					\item Eccl 5:16\hebword{וְחׇלְי֥וֹ}
					
					\item Eccl 5:18\hebword{כׇּֽל־הָאָדָ֡ם}
					
					\item Eccl 6:2\hebword{נׇכְרִ֖י}
					
					\item Eccl 6:2\hebword{וׇחֳלִ֥י} This kamatz katan is subject to debate between experts and reading traditions.
					
					\item Eccl 6:9\hebword{מֵֽהֲלׇךְ־נָ֑פֶשׁ}
					
					\item Eccl 7:10\hebword{מֵחׇכְמָ֖ה}
					
					\item Eccl 7:11\hebword{חׇכְמָ֖ה}
					
					\item Eccl 7:12\hebword{הַֽחׇכְמָ֖ה}
					
					\item Eccl 7:12\hebword{הַֽחׇכְמָ֖ה}
					
					\item Eccl 7:19\hebword{הַֽחׇכְמָ֖ה}
					
					\item Eccl 7:23\hebword{בַֽחׇכְמָ֑ה}
					
					\item Eccl 7:25\hebword{חׇכְמָ֖ה}
					
					\item Eccl 8:1\hebword{חׇכְמַ֤ת}
					
					\item Eccl 8:9\hebword{לְכׇֽל־מַעֲשֶׂ֔ה}
					
					\item Eccl 8:16\hebword{חׇכְמָ֔ה}
					
					\item Eccl 9:10\hebword{וְחׇכְמָ֔ה}
					
					\item Eccl 9:13\hebword{חׇכְמָ֖ה}
					
					\item Eccl 9:15\hebword{בְּחׇכְמָת֑וֹ}
					
					\item Eccl 9:16\hebword{חׇכְמָ֖ה}
					
					\item Eccl 9:16\hebword{וְחׇכְמַ֤ת}
					
					\item Eccl 9:18\hebword{חׇכְמָ֖ה}
					
					\item Eccl 10:1\hebword{מֵחׇכְמָ֥ה}
					
					\item Eccl 10:10\hebword{חׇכְמָֽה}
					
\end{itemize}\end{multicols}

\subsection{Esther}

\begin{multicols}{2}\begin{itemize}
					
					\item Esther 1:3\hebword{לְמׇלְכ֔וֹ}
					
					\item Esther 1:11\hebword{אֶת־יׇפְיָ֔הּ}
					
					\item Esther 1:17\hebword{בְּאׇמְרָ֗ם}
					
					\item Esther 2:5\hebword{מׇרְדֳּכַ֗י}
							
							\item Esther 2:5\hebword{מׇרְדְּכַ֗י}
							
							\item Esther 2:6\hebword{הׇגְלָה֙}
							
							\item Esther 2:6\hebword{הׇגְלְתָ֔ה}
							
							\item Esther 2:6\hebword{יְכׇנְיָ֣ה}
							
							\item Esther 2:7\hebword{מׇרְדֳּכַ֛י}
							
							\item Esther 2:10\hebword{מׇרְדֳּכַ֛י}
							
							\item Esther 2:11\hebword{מׇרְדֳּכַי֙}
							
							\item Esther 2:15\hebword{מׇרְדֳּכַ֡י}
							
							\item Esther 2:19\hebword{וּמׇרְדֳּכַ֖י}
							
							\item Esther 2:20\hebword{מׇרְדֳּכָ֑י}
							
							\item Esther 2:20\hebword{מׇרְדֳּכַי֙}
							
							\item Esther 2:20\hebword{בְאׇמְנָ֖ה}
							
							\item Esther 2:21\hebword{וּמׇרְדֳּכַ֖י}
							
							\item Esther 2:22\hebword{לְמׇרְדֳּכַ֔י}
							
							\item Esther 2:22\hebword{מׇרְדֳּכָֽי}
							
							\item Esther 3:2\hebword{וּמׇ֨רְדֳּכַ֔י}
							
							\item Esther 3:3\hebword{לְמׇרְדֳּכָ֑י}
							
							\item Esther 3:4\hebword{כְּאׇמְרָ֤ם}
							
							\item Esther 3:4\hebword{מׇרְדֳּכַ֔י}
							
							\item Esther 3:5\hebword{מׇרְדֳּכַ֔י}
							
							\item Esther 3:6\hebword{בְּמׇרְדֳּכַ֣י}
							
							\item Esther 3:6\hebword{מׇרְדֳּכָ֑י}
							
							\item Esther 3:6\hebword{מׇרְדֳּכָֽי}
							
							\item Esther 4:1\hebword{וּמׇרְדֳּכַ֗י}
							
							\item Esther 4:1\hebword{מׇרְדֳּכַי֙}
							
							\item Esther 4:4\hebword{אֶֽת־מׇרְדֳּכַ֗י}
							
							\item Esther 4:5\hebword{עַֽל־מׇרְדֳּכָ֑י}
							
							\item Esther 4:6\hebword{אֶֽל־מׇרְדֳּכָ֑י}
							
							\item Esther 4:7\hebword{מׇרְדֳּכַ֔י}
							
							\item Esther 4:9\hebword{מׇרְדֳּכָֽי}
							
							\item Esther 4:10\hebword{אֶֽל־מׇרְדֳּכָֽי}
							
							\item Esther 4:12\hebword{לְמׇרְדֳּכָ֔י}
							
							\item Esther 4:13\hebword{מׇרְדֳּכַ֖י}
							
							\item Esther 4:15\hebword{אֶֽל־מׇרְדֳּכָֽי}
							
							\item Esther 4:17\hebword{מׇרְדֳּכָ֑י}
							
							\item Esther 5:9\hebword{אֶֽת־מׇרְדֳּכַ֜י}
							
							\item Esther 5:9\hebword{עַֽל־מׇרְדֳּכַ֖י}
							
							\item Esther 5:11\hebword{עׇשְׁר֖וֹ}
							
							\item Esther 5:13\hebword{אֶת־מׇרְדֳּכַ֣י}
							
							\item Esther 5:14\hebword{אֶֽת־מׇרְדֳּכַי֙}
							
							\item Esther 6:2\hebword{מׇרְדֳּכַ֜י}
							
							\item Esther 6:3\hebword{לְמׇרְדֳּכַ֖י}
							
							\item Esther 6:4\hebword{אֶֽת־מׇרְדֳּכַ֔י}
							
							\item Esther 6:10\hebword{לְמׇרְדֳּכַ֣י}
							
							\item Esther 6:11\hebword{אֶֽת־מׇרְדֳּכָ֑י}
							
							\item Esther 6:12\hebword{וַיָּ֥שׇׁב}
							
							\item Esther 6:12\hebword{מׇרְדֳּכַ֖י}
							
							\item Esther 6:13\hebword{מׇרְדֳּכַ֞י}
							
							\item Esther 7:9\hebword{לְֽמׇרְדֳּכַ֞י}
							
							\item Esther 7:10\hebword{לְמׇרְדֳּכָ֑י}
							
							\item Esther 8:1\hebword{וּמׇרְדֳּכַ֗י}
							
							\item Esther 8:2\hebword{לְמׇרְדֳּכָ֑י}
							
							\item Esther 8:2\hebword{אֶֽת־מׇרְדֳּכַ֖י}
							
							\item Esther 8:4\hebword{וַתָּ֣קׇם}
							
							\item Esther 8:6\hebword{בְּאׇבְדַ֖ן}
							
							\item Esther 8:7\hebword{וּֽלְמׇרְדֳּכַ֖י}
							
							\item Esther 8:9\hebword{מׇרְדֳּכַ֣י}
							
							\item Esther 8:15\hebword{וּמׇרְדֳּכַ֞י}
							
							\item Esther 9:3\hebword{פַּֽחַד־מׇרְדֳּכַ֖י}
							
							\item Esther 9:4\hebword{מׇרְדֳּכַי֙}
							
							\item Esther 9:4\hebword{וְשׇׁמְע֖וֹ}
							
							\item Esther 9:4\hebword{מׇרְדֳּכַ֖י}
							
							\item Esther 9:20\hebword{מׇרְדֳּכַ֔י}
							
							\item Esther 9:23\hebword{מׇרְדֳּכַ֖י}
							
							\item Esther 9:29\hebword{וּמׇרְדֳּכַ֥י}
							
							\item Esther 9:31\hebword{מׇרְדֳּכַ֤י}
							
							\item Esther 10:2\hebword{תׇקְפּוֹ֙}
							
							\item Esther 10:2\hebword{מׇרְדֳּכַ֔י}
							
							\item Esther 10:3\hebword{מׇרְדֳּכַ֣י}
							
						\end{itemize}\end{multicols}
					
\section{Sifrei Eme״t}

\subsection{Psalms}

\begin{multicols}{2}
	\begin{itemize} \item Psalms 2:6\hebword{הַר־קׇדְשִֽׁי}
		
		\item Psalms 3:1\hebword{בְּ֝בׇרְח֗וֹ}

\item Psalms 3:5\hebword{קׇדְשׁ֣וֹ}

\item Psalms 4:2\hebword{בְּקׇרְאִ֡י}

\item Psalms 4:4\hebword{בְּקׇרְאִ֥י}

\item Psalms 5:4\hebword{אֶעֱרׇךְ־לְ֝ךָ֗}

\item Psalms 5:8\hebword{אֶל־הֵיכַל־קׇ֝דְשְׁךָ֗}

\item Psalms 6:3\hebword{חׇנֵּ֥נִי}

\item Psalms 7:9\hebword{שׇׁפְטֵ֥נִי}

\item Psalms 7:10\hebword{יִגְמׇר־נָ֬א}

\item Psalms 7:17\hebword{קׇ֝דְקֳד֗וֹ}

\item Psalms 8:9\hebword{אׇרְח֥וֹת}

\item Psalms 9:14\hebword{עׇ֭נְיִי}

\item Psalms 10:9\hebword{בְּמׇשְׁכ֥וֹ}

\item Psalms 10:17\hebword{אׇזְנֶֽךָ}

\item Psalms 11:4\hebword{קׇדְשׁ֗וֹ}

\item Psalms 11:6\hebword{וְ֭גׇפְרִית}

\item Psalms 15:1\hebword{בְּאׇהֳלֶ֑ךָ} This kamatz katan is subject to debate between experts and reading traditions.

\item Psalms 15:1\hebword{קׇדְשֶֽׁךָ}

\item Psalms 16:1\hebword{שׇֽׁמְרֵ֥נִי} This kamatz katan is subject to debate between experts and reading traditions.

\item Psalms 17:3\hebword{בַּל־יַעֲבׇר־פִּֽי}

\item Psalms 17:4\hebword{אׇרְח֥וֹת}

\item Psalms 17:6\hebword{הַֽט־אׇזְנְךָ֥}

\item Psalms 17:8\hebword{שׇׁ֭מְרֵנִי}

\item Psalms 18:2\hebword{אֶרְחׇמְךָ֖}

\item Psalms 18:7\hebword{בְאׇזְנָֽיו}

\item Psalms 18:29\hebword{חׇשְׁכִּֽי}

\item Psalms 19:12\hebword{בְּ֝שׇׁמְרָ֗ם}

\item Psalms 20:7\hebword{קׇדְשׁ֑וֹ}

\item Psalms 20:10\hebword{בְיוֹם־קׇרְאֵֽנוּ}

\item Psalms 21:2\hebword{בְּעׇזְּךָ֥}

\item Psalms 22:11\hebword{הׇשְׁלַ֣כְתִּי}



\item Psalms 24:3\hebword{קׇדְשֽׁוֹ}

\item Psalms 25:7\hebword{זְכׇר־לִי־אַ֑תָּה}

\item Psalms 25:10\hebword{כׇּל־אׇרְח֣וֹת}

\item Psalms 25:16\hebword{וְחׇנֵּ֑נִי}

\item Psalms 25:18\hebword{עׇ֭נְיִי}

\item Psalms 25:20\hebword{שׇׁמְרָ֣ה}

\item Psalms 26:1\hebword{שׇׁפְטֵ֤נִי}

\item Psalms 26:2\hebword{צׇרְפָ֖ה}

\item Psalms 26:11\hebword{וְחׇנֵּֽנִי}

\item Psalms 27:5\hebword{אׇהֳל֑וֹ} This kamatz katan is subject to debate between experts and reading traditions.

\item Psalms 27:6\hebword{בְ֭אׇהֳלוֹ} This kamatz katan is subject to debate between experts and reading traditions.

\item Psalms 27:7\hebword{וְחׇנֵּ֥נִי}

\item Psalms 28:2\hebword{בְּנׇשְׂאִ֥י}

\item Psalms 28:2\hebword{קׇדְשֶֽׁךָ}

\item Psalms 28:4\hebword{כְּפׇעֳלָם֮} This kamatz katan is subject to debate between experts and reading traditions.

\item Psalms 30:4\hebword{מִיׇּֽרְדִי}

\item Psalms 30:5\hebword{קׇדְשֽׁוֹ}

\item Psalms 30:11\hebword{וְחׇנֵּ֑נִי}

\item Psalms 31:3\hebword{אׇזְנְךָ֮}

\item Psalms 31:8\hebword{אֶת־עׇנְיִ֑י}

\item Psalms 31:10\hebword{חׇנֵּ֥נִי}

\item Psalms 31:23\hebword{בְחׇפְזִ֗י}


\item Psalms 33:16\hebword{בְּרׇב־חָ֑יִל}

\item Psalms 33:16\hebword{בְּרׇב־כֹּֽחַ}

\item Psalms 33:21\hebword{קׇדְשׁ֣וֹ}

\item Psalms 34:15\hebword{וְרׇדְפֵֽהוּ}

\item Psalms 34:16\hebword{וְ֝אׇזְנָ֗יו}


\item Psalms 35:8\hebword{יִפׇּל־בָּֽהּ}

\item Psalms 35:10\hebword{כׇּ‍֥ל} This kamatz katan is subject to debate between experts and reading traditions.

\item Psalms 35:24\hebword{שׇׁפְטֵ֣נִי}

\item Psalms 37:3\hebword{שְׁכׇן־אֶ֗֝רֶץ}

\item Psalms 37:6\hebword{כַּֽצׇּהֳרָֽיִם} This kamatz katan is subject to debate between experts and reading traditions.

\item Psalms 37:30\hebword{חׇכְמָ֑ה}

\item Psalms 37:37\hebword{שְׁמׇר־תָּ֭ם}

\item Psalms 39:6\hebword{כׇּֽל־הֶ֥בֶל}

\item Psalms 40:7\hebword{אׇ֭זְנַיִם}

\item Psalms 40:16\hebword{בׇּשְׁתָּ֑ם}

\item Psalms 41:4\hebword{בְחׇלְיֽוֹ}

\item Psalms 41:5\hebword{חׇנֵּ֑נִי}

\item Psalms 41:7\hebword{יִקְבׇּץ־אָ֥וֶן}

\item Psalms 41:11\hebword{חׇנֵּ֥נִי}

\item Psalms 42:7\hebword{אֶ֭זְכׇּרְךָ}

\item Psalms 42:11\hebword{בְּאׇמְרָ֥ם}

\item Psalms 43:1\hebword{שׇׁפְטֵ֤נִי}

\item Psalms 43:3\hebword{אֶל־הַֽר־קׇ֝דְשְׁךָ֗}

\item Psalms 44:2\hebword{בְּאׇזְנֵ֬ינוּ}

\item Psalms 44:19\hebword{אׇרְחֶֽךָ}

\item Psalms 44:22\hebword{יַחֲקׇר־זֹ֑את}

\item Psalms 44:25\hebword{עׇנְיֵ֣נוּ}

\item Psalms 45:3\hebword{יׇפְיָפִ֡יתָ}

\item Psalms 45:11\hebword{אׇזְנֵ֑ךְ}

\item Psalms 45:12\hebword{יׇפְיֵ֑ךְ}

\item Psalms 47:9\hebword{קׇדְשֽׁוֹ}

\item Psalms 48:2\hebword{הַר־קׇדְשֽׁוֹ}

\item Psalms 49:4\hebword{חׇכְמ֑וֹת}

\item Psalms 49:5\hebword{אׇזְנִ֑י}

\item Psalms 49:7\hebword{עׇ֝שְׁרָ֗ם}

\item Psalms 49:8\hebword{כׇּפְרֽוֹ}

\item Psalms 51:3\hebword{חׇנֵּ֣נִי}

\item Psalms 51:6\hebword{בְּדׇבְרֶ֗ךָ}

\item Psalms 51:6\hebword{בְשׇׁפְטֶֽךָ}

\item Psalms 51:8\hebword{חׇכְמָ֥ה}

\item Psalms 51:13\hebword{קׇ֝דְשְׁךָ֗}


\item Psalms 52:7\hebword{יִתׇּצְךָ}
	
	\item Psalms 52:9\hebword{עׇשְׁר֑וֹ}
	
	\item Psalms 55:18\hebword{וְ֭צׇהֳרַיִם} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Psalms 55:19\hebword{מִקְּרׇב־לִ֑י}
	
	\item Psalms 56:2\hebword{חׇנֵּ֣נִי}
	
	\item Psalms 57:1\hebword{בְּבׇרְח֥וֹ}

\item Psalms 57:2\hebword{חׇנֵּ֤נִי}

\item Psalms 57:2\hebword{חׇנֵּ֗נִי}

\item Psalms 58:5\hebword{אׇזְנֽוֹ}

\item Psalms 58:7\hebword{הֲרׇס־שִׁנֵּ֥ימוֹ}

\item Psalms 60:2\hebword{וַיָּ֤שׇׁב}

\item Psalms 60:8\hebword{בְּקׇדְשׁ֗וֹ}

\item Psalms 61:5\hebword{בְ֭אׇהׇלְךָ} This kamatz katan is subject to debate between experts and reading traditions.

\item Psalms 66:10\hebword{כִּצְרׇף־כָּֽסֶף}

\item Psalms 66:11\hebword{בְמׇתְנֵֽינוּ}

\item Psalms 67:2\hebword{יְחׇנֵּ֥נוּ}

\item Psalms 68:6\hebword{קׇדְשֽׁוֹ}

\item Psalms 68:22\hebword{קׇדְקֹ֥ד}

\item Psalms 68:27\hebword{יַעֲמׇס־לָ֗נוּ}

\item Psalms 69:3\hebword{מׇעֳמָ֑ד} This kamatz katan is subject to debate between experts and reading traditions.

\item Psalms 69:4\hebword{בְקׇרְאִי֮}
	
	\item Psalms 69:9\hebword{וְ֝נׇכְרִ֗י}
	
	\item Psalms 69:14\hebword{בְּרׇב־חַסְדֶּ֑ךָ}
	
	\item Psalms 69:19\hebword{קׇרְבָ֣ה}
	
	\item Psalms 69:20\hebword{וּ֭בׇשְׁתִּי}
	
	\item Psalms 69:24\hebword{וּ֝מׇתְנֵיהֶ֗ם}
	
	\item Psalms 69:25\hebword{שְׁפׇךְ־עֲלֵיהֶ֥ם}
	
	\item Psalms 69:26\hebword{בְּ֝אׇהֳלֵיהֶ֗ם} This kamatz katan is subject to debate between experts and reading traditions.
	
	\item Psalms 70:4\hebword{בׇּשְׁתָּ֑ם}
	
	
	\item Psalms 71:2\hebword{אׇ֝זְנְךָ֗}
	
	\item Psalms 74:5\hebword{בִּסְבׇךְ־עֵ֗֝ץ}
			
			\item Psalms 74:13\hebword{בְעׇזְּךָ֣}
			
			\item Psalms 74:18\hebword{זְכׇר־זֹ֗את}
			
			\item Psalms 77:13\hebword{בְכׇל־פׇּעֳלֶ֑ךָ} This kamatz katan is subject to debate between experts and reading traditions.
			
			\item Psalms 78:1\hebword{אׇ֝זְנְכֶ֗ם}
			
			\item Psalms 78:18\hebword{לִֽשְׁאׇל־אֹ֥כֶל}
			
			\item Psalms 78:30\hebword{אׇכְלָ֥ם}
			
			\item Psalms 78:51\hebword{בְּאׇהֳלֵי־חָֽם} This kamatz katan is subject to debate between experts and reading traditions.
			
			\item Psalms 78:54\hebword{קׇדְשׁ֑וֹ}
			
			\item Psalms 78:55\hebword{בְּ֝אׇהֳלֵיהֶ֗ם} This kamatz katan is subject to debate between experts and reading traditions.
			
			\item Psalms 79:1\hebword{קׇדְשֶׁ֑ךָ}
			
			\item Psalms 79:8\hebword{אַֽל־תִּזְכׇּר־לָנוּ֮}
					
					\item Psalms 79:9\hebword{עׇזְרֵ֤נוּ}
					
					\item Psalms 80:10\hebword{שׇׁ֝רָשֶׁ֗יהָ} This kamatz katan is subject to debate between experts and reading traditions.
					
					\item Psalms 81:8\hebword{אֶבְחׇנְךָ֨}
					
					\item Psalms 82:8\hebword{שׇׁפְטָ֣ה}
					
					\item Psalms 83:7\hebword{אׇהֳלֵ֣י} This kamatz katan is subject to debate between experts and reading traditions.
					
					\item Psalms 84:11\hebword{בְּאׇהֳלֵי־רֶֽשַׁע} This kamatz katan is subject to debate between experts and reading traditions.
					
					\item Psalms 86:1\hebword{אׇזְנְךָ֣}
					
					\item Psalms 86:3\hebword{חׇנֵּ֥נִי}
			
			\item Psalms 88:3\hebword{אׇ֝זְנְךָ֗}
			
			\item Psalms 88:6\hebword{חׇ֫פְשִׁ֥י}
			
			\item Psalms 89:21\hebword{קׇדְשִׁ֣י}
			
			\item Psalms 89:29\hebword{אֶשְׁמׇר־}
					
					\item Psalms 89:36\hebword{בְקׇדְשִׁ֑י}
					
					\item Psalms 89:48\hebword{זְכׇר־אֲנִ֥י}
					
					\item Psalms 90:10\hebword{וְ֭רׇהְבָּם}
					
					\item Psalms 90:12\hebword{חׇכְמָֽה}
					
					\item Psalms 90:16\hebword{פׇעֳלֶ֑ךָ} This kamatz katan is subject to debate between experts and reading traditions.
					
					\item Psalms 91:6\hebword{צׇהֳרָֽיִם} This kamatz katan is subject to debate between experts and reading traditions.
					
					\item Psalms 91:10\hebword{בְּאׇהֳלֶֽךָ} This kamatz katan is subject to debate between experts and reading traditions.
					
					\item Psalms 91:11\hebword{לִ֝שְׁמׇרְךָ֗}
					
					\item Psalms 92:5\hebword{בְּפׇעֳלֶ֑ךָ} This kamatz katan is subject to debate between experts and reading traditions.
					
					\item Psalms 92:12\hebword{אׇזְנָֽי}
					
					\item Psalms 93:3\hebword{דׇּכְיָֽם}
					
					\item Psalms 94:20\hebword{הַֽ֭יְחׇבְרְךָ}
					
					\item Psalms 95:9\hebword{פׇעֳלִֽי} This kamatz katan is subject to debate between experts and reading traditions.
					
					\item Psalms 97:12\hebword{קׇדְשֽׁוֹ}
					
					\item Psalms 98:1\hebword{קׇדְשֽׁוֹ}
					
					\item Psalms 99:9\hebword{קׇדְשׁ֑וֹ}
					
					\item Psalms 101:2\hebword{בְּתׇם־לְ֝בָבִ֗י}
					
					\item Psalms 101:5\hebword{מְלׇשְׁנִ֬י}
					
					\item Psalms 102:3\hebword{אׇזְנֶ֑ךָ}
					
					\item Psalms 102:20\hebword{קׇדְשׁ֑וֹ}
					
					\item Psalms 103:1\hebword{קׇדְשֽׁוֹ}
					
					\item Psalms 104:21\hebword{אׇכְלָֽם}
					
					\item Psalms 104:23\hebword{לְפׇעֳל֑וֹ} This kamatz katan is subject to debate between experts and reading traditions.
					
					\item Psalms 104:24\hebword{בְּחׇכְמָ֣ה}
					
					\item Psalms 104:27\hebword{אׇכְלָ֣ם}
					
					\item Psalms 105:3\hebword{קׇדְשׁ֑וֹ}
					
					\item Psalms 105:14\hebword{לְעׇשְׁקָ֑ם}
			
					
					\item Psalms 105:42\hebword{קׇדְשׁ֑וֹ}
					
					\item Psalms 106:4\hebword{זׇכְרֵ֣נִי}
					
					\item Psalms 106:4\hebword{פׇּ֝קְדֵ֗נִי}
					
					\item Psalms 106:25\hebword{בְאׇהֳלֵיהֶ֑ם} This kamatz katan is subject to debate between experts and reading traditions.
					
					\item Psalms 106:29\hebword{וַתִּפְרׇץ־בָּ֗֝ם}
					
					\item Psalms 106:44\hebword{בְּ֝שׇׁמְע֗וֹ}
					
					\item Psalms 106:47\hebword{קׇדְשֶׁ֑ךָ}
					
					\item Psalms 107:23\hebword{בׇּאֳנִיּ֑וֹת} This kamatz katan is subject to debate between experts and reading traditions.
					
					\item Psalms 107:27\hebword{וְכׇל־חׇ֝כְמָתָ֗ם}
					
					\item Psalms 107:43\hebword{וְיִשְׁמׇר־אֵ֑לֶּה}
							
							\item Psalms 108:8\hebword{בְּקׇדְשׁ֗וֹ}
							
							\item Psalms 109:10\hebword{מֵחׇרְבֽוֹתֵיהֶֽם}
							
							\item Psalms 109:26\hebword{עׇ֭זְרֵנִי}
							
							\item Psalms 109:29\hebword{בׇּשְׁתָּֽם}
							
							\item Psalms 111:3\hebword{פׇּעֳל֑וֹ} This kamatz katan is subject to debate between experts and reading traditions.
							
							\item Psalms 111:10\hebword{חׇכְמָ֨ה}
							
							\item Psalms 114:2\hebword{לְקׇדְשׁ֑וֹ}
							
							\item Psalms 115:6\hebword{אׇזְנַ֣יִם}
							
							\item Psalms 116:2\hebword{אׇזְנ֣וֹ}
							
							\item Psalms 116:11\hebword{בְחׇפְזִ֑י}
						
							
							\item Psalms 118:15\hebword{בְּאׇהֳלֵ֥י} This kamatz katan is subject to debate between experts and reading traditions.
							
							\item Psalms 119:7\hebword{בְּ֝לׇמְדִ֗י}
							
							\item Psalms 119:9\hebword{אֶת־אׇרְח֑וֹ}
							
							\item Psalms 119:29\hebword{חׇנֵּֽנִי}
							
							\item Psalms 119:50\hebword{בְעׇנְיִ֑י}
							
							\item Psalms 119:58\hebword{חׇ֝נֵּ֗נִי}
							
							\item Psalms 119:86\hebword{עׇזְרֵֽנִי}
							
							\item Psalms 119:92\hebword{בְעׇנְיִֽי}
							
							\item Psalms 119:132\hebword{וְחׇנֵּ֑נִי}
							
							\item Psalms 119:153\hebword{רְאֵה־עׇנְיִ֥י}
							
							\item Psalms 119:173\hebword{לְעׇזְרֵ֑נִי}
							
							\item Psalms 120:5\hebword{עִֽם־אׇהֳלֵ֥י} This kamatz katan is subject to debate between experts and reading traditions.
							
							\item Psalms 121:7\hebword{יִשְׁמׇרְךָ֥}
							
							\item Psalms 121:8\hebword{יִשְׁמׇר־צֵאתְךָ֥}
							
							\item Psalms 123:2\hebword{שֶׁיְּחׇנֵּֽנוּ}
							
							\item Psalms 123:3\hebword{חׇנֵּ֣נוּ}
							
							\item Psalms 123:3\hebword{חׇנֵּ֑נוּ}
							
							\item Psalms 127:1\hebword{לֹא־יִשְׁמׇר־עִ֗֝יר}
							
							\item Psalms 130:2\hebword{אׇ֭זְנֶיךָ}
							
							\item Psalms 130:3\hebword{תִּשְׁמׇר־יָ֑הּ}
							
							\item Psalms 135:17\hebword{אׇזְנַ֣יִם}
							
							\item Psalms 137:1\hebword{בְּ֝זׇכְרֵ֗נוּ}
							
							\item Psalms 138:2\hebword{קׇדְשְׁךָ֡}
							
							\item Psalms 139:3\hebword{אׇרְחִ֣י}
							
							\item Psalms 139:16\hebword{גׇּלְמִ֤י}
							
							\item Psalms 139:23\hebword{חׇקְרֵ֣נִי}
							
							\item Psalms 140:5\hebword{שׇׁמְרֵ֤נִי}
							
							\item Psalms 141:1\hebword{בְּקׇרְאִי־לָֽךְ}
							
							\item Psalms 141:3\hebword{שׇׁמְרָ֣ה}
							
							\item Psalms 141:9\hebword{שׇׁמְרֵ֗נִי}
							
							\item Psalms 143:5\hebword{בְכׇל־פׇּעֳלֶ֑ךָ} This kamatz katan is subject to debate between experts and reading traditions.
							
							\item Psalms 145:8\hebword{וּגְדׇל־חָֽסֶד}
							
							\item Psalms 145:15\hebword{אֶת־אׇכְלָ֣ם}
							
							\item Psalms 145:21\hebword{קׇדְשׁ֗וֹ}
							
							\item Psalms 148:6\hebword{חׇק־נָ֝תַ֗ן}
							
							\item Psalms 150:1\hebword{בְּקׇדְשׁ֑וֹ}
									
							\end{itemize}\end{multicols}
						
						\subsection{Proverbs}
						\begin{multicols}{2}\begin{itemize}

									\item Prov 1:2\hebword{חׇכְמָ֣ה}
									
									\item Prov 1:4\hebword{עׇרְמָ֑ה}
									
									\item Prov 1:7\hebword{חׇכְמָ֥ה}
									
									\item Prov 1:16\hebword{לִשְׁפׇּךְ־דָּֽם}
									
									\item Prov 1:19\hebword{אׇ֭רְחוֹת}
									
									\item Prov 1:20\hebword{חׇ֭כְמוֹת}
									
									\item Prov 1:33\hebword{יִשְׁכׇּן־בֶּ֑טַח}
									
									\item Prov 2:2\hebword{לַחׇכְמָ֣ה}
									
									\item Prov 2:2\hebword{אׇזְנֶ֑ךָ}
									
									\item Prov 2:6\hebword{חׇכְמָ֑ה}
									
									\item Prov 2:8\hebword{אׇרְח֣וֹת}
									
									\item Prov 2:10\hebword{חׇכְמָ֣ה}
									
									\item Prov 2:13\hebword{אׇרְח֣וֹת}
									
									\item Prov 2:15\hebword{אׇרְחֹתֵיהֶ֣ם}
									
									\item Prov 2:16\hebword{מִ֝נׇּכְרִיָּ֗ה}
									
									\item Prov 2:19\hebword{אׇרְח֥וֹת}
									
									\item Prov 2:20\hebword{וְאׇרְח֖וֹת}
									
									\item Prov 3:3\hebword{קׇשְׁרֵ֥ם}
									
									\item Prov 3:3\hebword{כׇּ֝תְבֵ֗ם}
									
									\item Prov 3:13\hebword{חׇכְמָ֑ה}
									
									\item Prov 3:19\hebword{בְּחׇכְמָ֥ה}
									
									\item Prov 4:4\hebword{יִֽתְמׇךְ־דְּבָרַ֥י}
									
									\item Prov 4:5\hebword{חׇ֭כְמָה}
									
									\item Prov 4:7\hebword{חׇ֭כְמָה}
									
									\item Prov 4:7\hebword{חׇכְמָ֑ה}
									
									\item Prov 4:11\hebword{חׇ֭כְמָה}
									
									\item Prov 4:15\hebword{אַל־תַּעֲבׇר־בּ֑וֹ}
									
									\item Prov 4:20\hebword{הַט־אׇזְנֶֽךָ}
									
									\item Prov 4:21\hebword{שׇׁ֝מְרֵ֗ם}
									
									\item Prov 5:1\hebword{לְחׇכְמָתִ֣י}
									
									\item Prov 5:1\hebword{הַט־אׇזְנֶֽךָ}
									
									\item Prov 5:10\hebword{נׇכְרִֽי}
									
									\item Prov 5:13\hebword{אׇזְנִֽי}
									
									\item Prov 5:20\hebword{נׇכְרִיָּֽה}
									
									\item Prov 6:21\hebword{קׇשְׁרֵ֣ם}
									
									\item Prov 6:21\hebword{עׇ֝נְדֵ֗ם}
									
									\item Prov 6:22\hebword{בְּֽ֭שׇׁכְבְּךָ}
									
									\item Prov 6:24\hebword{לִ֭שְׁמׇרְךָ}
									
									\item Prov 6:24\hebword{נׇכְרִיָּֽה}
									
									\item Prov 6:25\hebword{יׇ֭פְיָהּ}
									
									\item Prov 7:3\hebword{קׇשְׁרֵ֥ם}
									
									\item Prov 7:3\hebword{כׇּ֝תְבֵ֗ם}
									
									\item Prov 7:4\hebword{לַ֭חׇכְמָה}
									
									\item Prov 7:5\hebword{לִ֭שְׁמׇרְךָ}
									
									\item Prov 7:5\hebword{מִ֝נׇּכְרִיָּ֗ה}
									
									\item Prov 7:18\hebword{בׇּאֳהָבִֽים} This kamatz katan is subject to debate between experts and reading traditions.
									
									\item Prov 8:1\hebword{הֲלֹֽא־חׇכְמָ֥ה}
									
									\item Prov 8:5\hebword{עׇרְמָ֑ה}
									
									\item Prov 8:11\hebword{חׇ֭כְמָה}
									
									\item Prov 8:12\hebword{אֲֽנִי־חׇ֭כְמָה}
									
									\item Prov 8:12\hebword{עׇרְמָ֑ה}
									
									\item Prov 8:25\hebword{הׇטְבָּ֑עוּ}
									
									\item Prov 9:1\hebword{חׇ֭כְמוֹת}
									
									\item Prov 9:10\hebword{חׇ֭כְמָה}
									
									\item Prov 10:13\hebword{חׇכְמָ֑ה}
									
									\item Prov 10:23\hebword{וְ֝חׇכְמָ֗ה}
									
									\item Prov 10:31\hebword{חׇכְמָ֑ה}
									
									\item Prov 11:2\hebword{חׇכְמָֽה}
									
									\item Prov 11:12\hebword{בׇּז־לְרֵעֵ֥הוּ}
									
									\item Prov 11:14\hebword{יִפׇּל־עָ֑ם}
									
									\item Prov 11:28\hebword{בְּ֭עׇשְׁרוֹ}
									
									\item Prov 12:6\hebword{אֱרׇב־דָּ֑ם}
									
									\item Prov 13:6\hebword{תׇּם־דָּ֑רֶךְ}
									
									\item Prov 13:8\hebword{עׇשְׁר֑וֹ}
									
									\item Prov 13:10\hebword{חׇכְמָֽה}
									
									\item Prov 13:23\hebword{רׇב־אֹ֭כֶל}
									
									\item Prov 14:2\hebword{בְּ֭יׇשְׁרוֹ}
									
									\item Prov 14:4\hebword{וְרׇב־תְּ֝בוּא֗וֹת}
									
									\item Prov 14:6\hebword{חׇכְמָ֣ה}
									
									\item Prov 14:8\hebword{חׇכְמַ֣ת}
									
									\item Prov 14:21\hebword{בׇּז־לְרֵעֵ֥הוּ}
									
									\item Prov 14:24\hebword{עׇשְׁרָ֑ם}
									
									\item Prov 14:28\hebword{בְּרׇב־עָ֥ם}
									
									\item Prov 14:33\hebword{חׇכְמָ֑ה}
									
									\item Prov 15:33\hebword{חׇכְמָ֑ה}
									
									\item Prov 16:2\hebword{כׇּֽל־דַּרְכֵי־אִ֭ישׁ}
									
									\item Prov 16:16\hebword{קְֽנֹה־חׇכְמָ֗ה}
									
									\item Prov 17:16\hebword{חׇכְמָ֣ה}
									
									\item Prov 17:23\hebword{אׇרְח֥וֹת}
									
									\item Prov 17:24\hebword{חׇכְמָ֑ה}
									
									\item Prov 18:4\hebword{חׇכְמָֽה}
									
									\item Prov 19:7\hebword{כׇּ‍֥ל} This kamatz katan is subject to debate between experts and reading traditions.
									
									\item Prov 20:6\hebword{רׇב־אָדָ֗ם}
									
									\item Prov 20:11\hebword{פׇּעֳלֽוֹ} This kamatz katan is subject to debate between experts and reading traditions.
									
									\item Prov 20:15\hebword{וְרׇב־פְּנִינִ֑ים}
									
									\item Prov 20:16\hebword{נׇכְרִיָּ֣ה}
									
									\item Prov 21:8\hebword{פׇּעֳלֽוֹ} This kamatz katan is subject to debate between experts and reading traditions.
									
									\item Prov 21:11\hebword{בַּֽעֲנׇשׁ־לֵ֭ץ}
									
									\item Prov 21:30\hebword{חׇׇ֭כְמָה}
									
									\item Prov 22:8\hebword{יִקְצׇר־אָ֑וֶן}
									
									\item Prov 22:11\hebword{טְהׇר־לֵ֑ב}
									
									\item Prov 22:14\hebword{יִפׇּל־שָֽׁם}
									
									\item Prov 22:17\hebword{אׇזְנְךָ֗}
									
									\item Prov 22:22\hebword{אַֽל־תִּגְזׇל־דָּ֭ל}
									
									\item Prov 23:9\hebword{בְּאׇזְנֵ֣י}
									
									\item Prov 23:12\hebword{וְ֝אׇזְנֶ֗ךָ}
									
									\item Prov 23:23\hebword{חׇכְמָ֖ה}
									
									\item Prov 23:27\hebword{נׇכְרִיָּֽה}
									
									\item Prov 24:3\hebword{בְּ֭חׇכְמָה}
									
									\item Prov 24:7\hebword{חׇכְמ֑וֹת}
									
									\item Prov 24:12\hebword{כְּפׇעֳלֽוֹ} This kamatz katan is subject to debate between experts and reading traditions.
									
									\item Prov 24:14\hebword{חׇכְמָ֗ה}
									
									\item Prov 24:29\hebword{כְּפׇעֳלֽוֹ} This kamatz katan is subject to debate between experts and reading traditions.
									
									\item Prov 25:7\hebword{אֲמׇר־לְךָ֗}
									
									\item Prov 25:11\hebword{עַל־אׇפְנָֽיו}
									
									\item Prov 25:15\hebword{תִּשְׁבׇּר־גָּֽרֶם}
									
									\item Prov 25:26\hebword{מׇשְׁחָ֑ת}
									
									\item Prov 26:17\hebword{בְּאׇזְנֵי־כָ֑לֶב}
									
									\item Prov 27:2\hebword{נׇ֝כְרִ֗י}
									
									\item Prov 27:13\hebword{נׇכְרִיָּ֣ה}
									
									\item Prov 28:9\hebword{אׇ֭זְנוֹ}
									
									\item Prov 28:26\hebword{בְּ֝חׇכְמָ֗ה}
									
									\item Prov 28:28\hebword{וּ֝בְאׇבְדָ֗ם}
									
									\item Prov 29:3\hebword{חׇ֭כְמָה}
									
									\item Prov 29:15\hebword{חׇכְמָ֑ה}
									
									\item Prov 30:3\hebword{חׇכְמָ֑ה}
									
									\item Prov 30:4\hebword{בְּחׇפְנָ֡יו}
									
									\item Prov 30:31\hebword{מׇתְנַ֣יִם}
									
									\item Prov 31:7\hebword{יִזְכׇּר־עֽוֹד}
									
									\item Prov 31:9\hebword{שְׁפׇט־צֶ֑דֶק}
									
									\item Prov 31:14\hebword{כׇּאֳנִיּ֣וֹת} This kamatz katan is subject to debate between experts and reading traditions.
									
									\item Prov 31:15\hebword{וַתָּ֤קׇם}
									
									\item Prov 31:17\hebword{מׇתְנֶ֑יהָ}
									
									\item Prov 31:26\hebword{בְחׇכְמָ֑ה}
									
								\end{itemize}\end{multicols}
							
							\subsection{Job}
							\begin{multicols}{2}\begin{itemize}
									
									\item Job 1:20\hebword{וַיָּ֤קׇם}
									
									\item Job 1:20\hebword{וַיָּ֖גׇז}
									
									\item Job 2:7\hebword{קׇדְקֳדֽוֹ}
									
									\item Job 3:5\hebword{תִּשְׁכׇּן־עָלָ֣יו}
									
									\item Job 3:19\hebword{חׇפְשִׁ֥י}
									
									\item Job 4:7\hebword{זְכׇר־נָ֗א}
									
									\item Job 4:12\hebword{אׇ֝זְנִ֗י}
									
									\item Job 4:18\hebword{תׇּהֳלָֽה} This kamatz katan is subject to debate between experts and reading traditions.
									
									\item Job 4:21\hebword{בְחׇכְמָֽה}
									
									\item Job 5:2\hebword{יַהֲרׇג־כָּ֑עַשׂ}
									
									\item Job 5:13\hebword{בְּעׇרְמָ֑ם}
									
									\item Job 5:14\hebword{בַֽצׇּהֳרָֽיִם} This kamatz katan is subject to debate between experts and reading traditions.
									
									\item Job 5:23\hebword{הׇשְׁלְמָה־לָּֽךְ}
									
									\item Job 5:24\hebword{אׇהֳלֶ֑ךָ} This kamatz katan is subject to debate between experts and reading traditions.
									
									\item Job 6:18\hebword{אׇרְח֣וֹת}
									
									\item Job 6:19\hebword{אׇרְח֣וֹת}
									
									\item Job 7:2\hebword{פׇעֳלֽוֹ} This kamatz katan is subject to debate between experts and reading traditions.
									
									\item Job 7:3\hebword{הׇנְחַ֣לְתִּי}
									
									\item Job 8:13\hebword{אׇ֭רְחוֹת}
									
									\item Job 8:17\hebword{שׇׁרָשָׁ֣יו} This kamatz katan is subject to debate between experts and reading traditions.
									
									\item Job 9:2\hebword{אׇ֭מְנָם}
									
									\item Job 9:8\hebword{עַל־בׇּ֥מֳתֵי} This kamatz katan is subject to debate between experts and reading traditions.
									
									\item Job 9:20\hebword{תׇּֽם־אָ֗֝נִי} This kamatz katan is subject to debate between experts and reading traditions.
									
									\item Job 9:21\hebword{תׇּֽם־אָ֭נִי} This kamatz katan is subject to debate between experts and reading traditions.
									
									\item Job 9:27\hebword{אִם־אׇ֭מְרִי}
									
									\item Job 10:9\hebword{זְכׇר־נָ֭א}
									
									\item Job 10:15\hebword{עׇנְיִֽי}
									
									\item Job 11:6\hebword{חׇכְמָה֮}
											
											\item Job 11:8\hebword{גׇּבְהֵ֣י}
											
											\item Job 11:17\hebword{וּֽ֭מִצׇּהֳרַיִם} This kamatz katan is subject to debate between experts and reading traditions.
											
											\item Job 12:2\hebword{אׇ֭מְנָם}
											
											\item Job 12:2\hebword{חׇכְמָֽה}
											
											\item Job 12:12\hebword{חׇכְמָ֑ה}
											
											\item Job 12:13\hebword{חׇכְמָ֣ה}
											
											\item Job 12:18\hebword{בְּמׇתְנֵיהֶֽם}
											
											\item Job 13:1\hebword{אׇ֝זְנִ֗י}
											
											\item Job 13:5\hebword{לְחׇכְמָֽה}
											
											\item Job 13:17\hebword{בְּאׇזְנֵיכֶֽם}
											
											\item Job 13:27\hebword{כׇּל־אׇרְחוֹתָ֑י עַל־שׇׁרְשֵׁ֥י}
											
											\item Job 14:8\hebword{שׇׁרְשׁ֑וֹ}
											
											\item Job 15:8\hebword{חׇכְמָֽה}
											
											\item Job 15:21\hebword{בְּאׇזְנָ֑יו}
											
											\item Job 15:34\hebword{אׇהֳלֵי־שֹֽׁחַד} This kamatz katan is subject to debate between experts and reading traditions.
											
											\item Job 16:8\hebword{וַיָּ֥קׇם}
													
													\item Job 16:12\hebword{בְּ֭עׇרְפִּי}
													
													\item Job 17:3\hebword{עׇרְבֵ֣נִי}
													
													\item Job 17:9\hebword{וּֽטְהׇר־יָ֝דַ֗יִם}
															
															\item Job 18:6\hebword{בְּאׇהֳל֑וֹ} This kamatz katan is subject to debate between experts and reading traditions.
															
															\item Job 18:14\hebword{מֵ֭אׇהֳלוֹ} This kamatz katan is subject to debate between experts and reading traditions.
															
															\item Job 18:15\hebword{בְּ֭אׇהֳלוֹ} This kamatz katan is subject to debate between experts and reading traditions.
															
															\item Job 18:15\hebword{גׇפְרִֽית}
															
															\item Job 18:16\hebword{שׇׁרָשָׁ֣יו} This kamatz katan is subject to debate between experts and reading traditions.
															
															\item Job 19:4\hebword{וְאַף־אׇמְנָ֥ם}
															
															\item Job 19:5\hebword{אִם־אׇ֭מְנָם}
															
															\item Job 19:8\hebword{אׇרְחִ֣י}
															
															\item Job 19:12\hebword{לְאׇהֳלִֽי} This kamatz katan is subject to debate between experts and reading traditions.
															
															\item Job 19:15\hebword{נׇ֝כְרִ֗י}
															
															\item Job 19:21\hebword{חׇנֻּ֬נִי}
															
															\item Job 19:21\hebword{חׇנֻּ֣נִי}
															
															\item Job 19:28\hebword{מַה־נִּרְדׇּף־ל֑וֹ}
															
															\item Job 20:21\hebword{לְאׇכְל֑וֹ}
															
															\item Job 20:26\hebword{לִצְפּ֫וּנָ֥יו}
															
															\item Job 20:26\hebword{בְּאׇהֳלֽוֹ} This kamatz katan is subject to debate between experts and reading traditions.
															
															\item Job 22:2\hebword{יִסְכׇּן־גָּ֑בֶר}
															
															\item Job 22:23\hebword{מֵאׇהֳלֶֽךָ} This kamatz katan is subject to debate between experts and reading traditions.
															
															\item Job 22:28\hebword{וְיָ֣קׇם}
															
															\item Job 23:6\hebword{הַבְּרׇב־כֹּ֭חַ}
															
															\item Job 24:5\hebword{בְּ֭פׇעֳלָם} This kamatz katan is subject to debate between experts and reading traditions.
															
															\item Job 24:14\hebword{יִֽקְטׇל־עָנִ֥י}
															
															\item Job 26:3\hebword{חׇכְמָ֑ה}
															
															\item Job 28:12\hebword{וְֽ֭הַחׇכְמָה}
															
															\item Job 28:18\hebword{חׇ֝כְמָ֗ה}
															
															\item Job 28:20\hebword{וְֽ֭הַחׇכְמָה}
															
															\item Job 28:22\hebword{בְּ֝אׇזְנֵ֗ינוּ}
															
															\item Job 28:28\hebword{חׇכְמָ֑ה}
															
															\item Job 29:4\hebword{חׇרְפִּ֑י}
															
															\item Job 29:4\hebword{אׇהֳלִֽי} This kamatz katan is subject to debate between experts and reading traditions.
															
															\item Job 29:19\hebword{שׇׁרְשִׁ֣י}
															
															\item Job 30:12\hebword{אׇרְח֥וֹת}
															
															\item Job 30:15\hebword{הׇהְפַּ֥ךְ}
															
															\item Job 30:18\hebword{בְּרׇב־כֹּ֭חַ}
															
															\item Job 30:18\hebword{כֻתׇּנְתִּ֣י}
															
															\item Job 31:31\hebword{אׇהֳלִ֑י} This kamatz katan is subject to debate between experts and reading traditions.
															
															\item Job 31:40\hebword{בׇאְשָׁ֑ה}
															
															\item Job 32:7\hebword{חׇכְמָֽה}
															
															\item Job 32:13\hebword{חׇכְמָ֑ה}
															
															\item Job 33:8\hebword{בְאׇזְנָ֑י}
															
															\item Job 33:11\hebword{כׇּל־אׇרְחֹתָֽי}
															
															\item Job 33:33\hebword{חׇכְמָֽה}
															
															\item Job 34:9\hebword{יִסְכׇּן־גָּ֑בֶר}
															
															\item Job 34:12\hebword{אַף־אׇמְנָ֗ם}
															
															\item Job 35:3\hebword{מַה־יִּסְכׇּן־לָ֑ךְ}
															
															\item Job 35:6\hebword{מַה־תִּפְעׇל־בּ֑וֹ}
															
															\item Job 36:4\hebword{כִּֽי־אׇ֭מְנָם}
															
															\item Job 36:9\hebword{פׇּעֳלָ֑ם} This kamatz katan is subject to debate between experts and reading traditions.
															
															\item Job 36:10\hebword{אׇ֭זְנָם}
															
															\item Job 36:15\hebword{בְעׇנְי֑וֹ}
															
															\item Job 36:15\hebword{אׇזְנָֽם}
															
															\item Job 36:18\hebword{וְרׇב־כֹּ֗֝פֶר}
															
															\item Job 36:24\hebword{פׇעֳל֑וֹ} This kamatz katan is subject to debate between experts and reading traditions.
															
															\item Job 36:30\hebword{וְשׇׁרְשֵׁ֖י}
															
															\item Job 37:12\hebword{לְפׇעֳלָ֑ם} This kamatz katan is subject to debate between experts and reading traditions.
															
															\item Job 38:3\hebword{אֱזׇר־נָ֣א}
															
															\item Job 38:4\hebword{בְּיׇסְדִי־אָ֑רֶץ}
															
															\item Job 38:6\hebword{הׇטְבָּ֑עוּ}
															
															\item Job 38:7\hebword{בְּרׇן־יַ֭חַד}
															
															\item Job 38:19\hebword{יִשְׁכׇּן־א֑וֹר}
															
															\item Job 38:36\hebword{חׇכְמָ֑ה}
															
															\item Job 38:37\hebword{בְּחׇכְמָ֑ה}
															
															\item Job 39:5\hebword{חׇפְשִׁ֑י}
															
															\item Job 39:9\hebword{עׇבְדֶ֑ךָ}
															
															\item Job 39:10\hebword{הֲֽתִקְשׇׁר־רֵ֭ים}
															
															\item Job 39:12\hebword{וְֽגׇרְנְךָ֥}
															
															\item Job 39:17\hebword{חׇכְמָ֑ה}
															
															\item Job 40:7\hebword{אֱזׇר־נָ֣א}
															
															\item Job 40:13\hebword{טׇמְנֵ֣ם}
															
															\item Job 40:16\hebword{בְמׇתְנָ֑יו}
															
															\item Job 40:24\hebword{יִנְקׇב־אָֽף}
															
															\item Job 41:25\hebword{מׇשְׁל֑וֹ}
															
															\item Job 42:17\hebword{וַיָּ֣מׇת}
															
														\end{itemize}\end{multicols}

\section{Histories}

\subsection{Daniel}

\begin{multicols}{2}\begin{itemize}

\item Dan 1:4\hebword{בְּכׇל־חׇכְמָ֗ה}

\item Dan 1:17\hebword{וְחׇכְמָ֑ה}

\item Dan 1:20\hebword{חׇכְמַ֣ת}

\item Dan 2:9\hebword{קׇֽדָמַ֔י} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 2:11\hebword{וְאׇחֳרָן֙} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 2:20\hebword{חׇכְמְתָ֛א}

\item Dan 2:21\hebword{חׇכְמְתָא֙}

\item Dan 2:23\hebword{חׇכְמְתָ֛א}

\item Dan 2:30\hebword{בְחׇכְמָה֙}

\item Dan 2:31\hebword{לְקׇבְלָ֑ךְ}

\item Dan 2:37\hebword{וְתׇקְפָּ֥א}

\item Dan 2:39\hebword{אׇחֳרִ֖י} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 2:39\hebword{אׇחֳרִי֙} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 2:44\hebword{אׇחֳרָ֖ן} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 3:3\hebword{לׇקֳבֵ֣ל} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 3:7\hebword{כׇּֽל־עַמְמַיָּ֡א}

\item Dan 3:7\hebword{כׇּֽל־עַֽמְמַיָּ֜א}

\item Dan 3:29\hebword{אׇחֳרָ֔ן} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 3:32\hebword{קׇֽדָמַ֖י} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 3:33\hebword{וְשׇׁלְטָנֵ֖הּ}

\item Dan 4:3\hebword{קׇֽדָמַ֔י} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 4:5\hebword{אׇחֳרֵ֡ין} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 4:5\hebword{קׇֽדָמַ֨י} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 4:5\hebword{קׇֽדָמ֥וֹהִי} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 4:9\hebword{עׇפְיֵ֤הּ}

\item Dan 4:11\hebword{עׇפְיֵ֖הּ}

\item Dan 4:12\hebword{שׇׁרְשׁ֙וֹהִי֙}

\item Dan 4:18\hebword{וְעׇפְיֵ֤הּ}

\item Dan 4:19\hebword{וְשׇׁלְטָנָ֖ךְ}

\item Dan 4:20\hebword{שׇׁרְשׁ֙וֹהִי֙}

\item Dan 4:23\hebword{שׇׁרְשׁ֙וֹהִי֙}

\item Dan 4:31\hebword{שׇׁלְטָנֵהּ֙}

\item Dan 4:31\hebword{שׇׁלְטָ֣ן}

\item Dan 4:33\hebword{הׇתְקְנַ֔ת}

\item Dan 5:1\hebword{וְלׇקֳבֵ֥ל} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 5:5\hebword{לׇקֳבֵ֣ל} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 5:10\hebword{לׇקֳבֵ֨ל} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 5:11\hebword{וְשׇׂכְלְתָנ֛וּ}

\item Dan 5:11\hebword{וְחׇכְמָ֥ה}

\item Dan 5:11\hebword{כְּחׇכְמַת־אֱלָהִ֖ין}

\item Dan 5:12\hebword{וְשׇׂכְלְתָנ֡וּ}

\item Dan 5:14\hebword{וְשׇׂכְלְתָנ֛וּ}

\item Dan 5:14\hebword{וְחׇכְמָ֥ה}

\item Dan 5:15\hebword{קׇֽדָמַ֗י} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 5:17\hebword{לְאׇחֳרָ֣ן} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 5:20\hebword{הׇנְחַת֙}

\item Dan 5:20\hebword{מִן־כׇּרְסֵ֣א}

\item Dan 5:23\hebword{קׇֽדָמָ֗ךְ} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 6:19\hebword{קׇֽדָמ֑וֹהִי} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 6:20\hebword{בְּנׇגְהָ֑א}

\item Dan 6:23\hebword{קׇֽדָמ֙וֹהִי֙} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 6:23\hebword{קׇֽדָמָךְ֙} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 6:27\hebword{בְּכׇל־שׇׁלְטָ֣ן}

\item Dan 6:27\hebword{וְשׇׁלְטָנֵ֖הּ}

\item Dan 7:5\hebword{אׇחֳרִ֨י} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 7:6\hebword{אׇֽחֳרִי֙} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 7:6\hebword{וְשׇׁלְטָ֖ן}

\item Dan 7:7\hebword{קׇֽדָמַ֔הּ} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 7:8\hebword{אׇחֳרִ֤י} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 7:9\hebword{כׇרְסָוָן֙}

\item Dan 7:9\hebword{כׇּרְסְיֵהּ֙}

\item Dan 7:12\hebword{שׇׁלְטָנְה֑וֹן}

\item Dan 7:14\hebword{שׇׁלְטָן֙}

\item Dan 7:14\hebword{שׇׁלְטָנֵ֞הּ}

\item Dan 7:14\hebword{שׇׁלְטָ֤ן}

\item Dan 7:20\hebword{וְאׇחֳרִי֙} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 7:24\hebword{וְאׇחֳרָ֞ן} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 7:26\hebword{וְשׇׁלְטָנֵ֣הּ}

\item Dan 7:27\hebword{וְשׇׁלְטָנָ֜א}

\item Dan 7:27\hebword{שׇׁלְטָ֣נַיָּ֔א}

\item Dan 8:6\hebword{וַיָּ֥רׇץ}

\item Dan 8:8\hebword{וּכְעׇצְמ֗וֹ}

\item Dan 8:17\hebword{עׇמְדִ֔י}

\item Dan 8:18\hebword{עַל־עׇמְדִֽי}

\item Dan 9:1\hebword{הׇמְלַ֔ךְ}

\item Dan 9:2\hebword{לְמׇלְכ֔וֹ}

\item Dan 9:2\hebword{לְחׇרְב֥וֹת}

\item Dan 9:16\hebword{יָֽשׇׁב־נָ֤א}

\item Dan 9:16\hebword{הַר־קׇדְשֶׁ֑ךָ}

\item Dan 9:18\hebword{אׇזְנְךָ֮}

\item Dan 9:24\hebword{קׇדְשֶׁ֗ךָ}

\item Dan 9:24\hebword{קׇֽדָשִֽׁים} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 10:5\hebword{וּמׇתְנָ֥יו}

\item Dan 10:9\hebword{וּכְשׇׁמְעִי֙}

\item Dan 10:11\hebword{עַל־עׇמְדֶ֔ךָ}

\item Dan 10:13\hebword{לְעׇזְרֵ֑נִי}

\item Dan 10:17\hebword{לֹֽא־יַעֲמׇד־בִּ֣י}

\item Dan 11:1\hebword{עׇמְדִ֛י}

\item Dan 11:2\hebword{בְעׇשְׁר֔וֹ}

\item Dan 11:4\hebword{וּכְעׇמְדוֹ֙}

\item Dan 11:4\hebword{כְמׇשְׁלוֹ֙}

\item Dan 11:7\hebword{שׇׁרָשֶׁ֖יהָ} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 11:40\hebword{וּבׇאֳנִיּ֖וֹת} This kamatz katan is subject to debate between experts and reading traditions.

\item Dan 11:45\hebword{אׇהֳלֵ֣י} This kamatz katan is subject to debate between experts and reading traditions.
\end{itemize}\end{multicols}

\subsection{Ezra-Nehemiah}
\begin{multicols}{2}\begin{itemize}
		\item Ezra 2:2\hebword{מׇרְדֳּכַ֥י}
		
		\item Ezra 2:58\hebword{כׇּ֨ל־הַנְּתִינִ֔ים}
		
		\item Ezra 2:69\hebword{וְכׇתְנֹ֥ת}
		
		\item Ezra 3:2\hebword{וַיָּ֩קׇם֩}
		
		\item Ezra 3:12\hebword{בְּיׇסְד֔וֹ}
		
		\item Ezra 4:10\hebword{אׇסְנַפַּר֙} This kamatz katan is subject to debate between experts and reading traditions.
		
		\item Ezra 4:15\hebword{בִּֽסְפַר־דׇּכְרָ֨נַיָּ֜א}
		
		\item Ezra 4:15\hebword{דׇּכְרָנַיָּא֮}
		
		\item Ezra 4:15\hebword{הׇֽחָרְבַֽת} This kamatz katan is subject to debate between experts and reading traditions.
		
		\item Ezra 4:16\hebword{לׇקֳבֵ֣ל} This kamatz katan is subject to debate between experts and reading traditions.
		
		\item Ezra 4:18\hebword{קׇדָמָֽי} This kamatz katan is subject to debate between experts and reading traditions.
		
		\item Ezra 5:8\hebword{אׇסְפַּ֥רְנָא} This kamatz katan is subject to debate between experts and reading traditions.
		
		\item Ezra 6:8\hebword{אׇסְפַּ֗רְנָא}
		
		\item Ezra 6:12\hebword{אׇסְפַּ֖רְנָא}
		
		\item Ezra 6:13\hebword{לׇקֳבֵ֗ל} This kamatz katan is subject to debate between experts and reading traditions.
		
		\item Ezra 6:13\hebword{אׇסְפַּ֥רְנָא}
		
		\item Ezra 7:17\hebword{אׇסְפַּ֨רְנָא}
		
		\item Ezra 7:19\hebword{לְפׇלְחָ֖ן}
		
		\item Ezra 7:21\hebword{אׇסְפַּ֖רְנָא}
		
		\item Ezra 7:25\hebword{כְּחׇכְמַ֨ת}
		
		\item Ezra 7:26\hebword{אׇסְפַּ֕רְנָא}
		
		\item Ezra 8:22\hebword{לְעׇזְרֵ֥נוּ}
		
		\item Ezra 9:3\hebword{וּכְשׇׁמְעִי֙}
		
		\item Ezra 9:5\hebword{וּבְקׇרְעִ֥י}
		
		\item Ezra 9:8\hebword{קׇדְשׁ֑וֹ}
		
		\item Ezra 9:9\hebword{אֶת־חׇרְבֹתָ֔יו}
		
		\item Ezra 10:2\hebword{נׇכְרִיּ֖וֹת}
		
		\item Ezra 10:3\hebword{נִֽכְרׇת־בְּרִ֣ית}
		
		\item Ezra 10:5\hebword{וַיָּ֣קׇם}
		
		\item Ezra 10:6\hebword{וַיָּ֣קׇם}
		
		\item Ezra 10:8\hebword{יׇחֳרַ֖ם} This kamatz katan is subject to debate between experts and reading traditions.
		
		\item Ezra 10:10\hebword{וַיָּ֨קׇם}
		
		\item Ezra 10:10\hebword{נׇכְרִיּ֑וֹת}
		
		\item Ezra 10:11\hebword{הַנׇּכְרִיּֽוֹת}
		
		\item Ezra 10:14\hebword{נׇכְרִיּוֹת֙}
		
		\item Ezra 10:17\hebword{נׇכְרִיּ֑וֹת}
		
		\item Ezra 10:18\hebword{נׇכְרִיּ֑וֹת}
		
		\item Ezra 10:44\hebword{נׇכְרִיּ֑וֹת}
		
		\item Neh 1:4\hebword{כְּשׇׁמְעִ֣י}
		
		\item Neh 1:6\hebword{אׇזְנְךָֽ־קַשֶּׁ֣בֶת}
		
		\item Neh 1:8\hebword{זְכׇר־נָא֙}
		
		\item Neh 1:11\hebword{אׇזְנְךָֽ־קַ֠שֶּׁ֠בֶת}
		
		\item Neh 3:1\hebword{וַיָּ֡קׇם}
		
		\item Neh 4:7\hebword{רׇמְחֵיהֶ֖ם}
		
		\item Neh 4:9\hebword{וַנָּ֤שׇׁב}
		
		\item Neh 4:12\hebword{עַל־מׇתְנָ֖יו}
		
		\item Neh 5:13\hebword{גַּם־חׇצְנִ֣י}
		
		\item Neh 5:13\hebword{כׇֽל־הַקָּהָ֜ל}
		
				
				\item Neh 5:19\hebword{זׇכְרָה־לִּ֥י}
				
				\item Neh 6:10\hebword{לְהׇרְגֶ֔ךָ}
				
				\item Neh 6:10\hebword{לְהׇרְגֶֽךָ}
				
				\item Neh 6:14\hebword{זׇכְרָ֧ה}
		
						
						\item Neh 7:69\hebword{כׇּתְנוֹת֙}
						
						\item Neh 7:71\hebword{וְכׇתְנֹ֥ת}
						
						\item Neh 8:3\hebword{וְאׇזְנֵ֥י}
						
						\item Neh 8:7\hebword{עַל־עׇמְדָֽם}
						
						\item Neh 8:9\hebword{כְּשׇׁמְעָ֖ם}
						
						\item Neh 8:17\hebword{כׇֽל־הַ֠קָּהָ֠ל}
						
						\item Neh 9:3\hebword{עַל־עׇמְדָ֔ם}
						
						\item Neh 9:4\hebword{וַיָּ֜קׇם}
						
						\item Neh 9:14\hebword{קׇדְשְׁךָ֖}
						
						\item Neh 9:16\hebword{אֶת־עׇרְפָּ֔ם}
						
						\item Neh 9:17\hebword{אֶת־עׇרְפָּ֔ם}
						
						\item Neh 9:29\hebword{וְעׇרְפָּ֥ם}
						
						\item Neh 11:29\hebword{וּבְצׇרְעָ֖ה}
						
						\item Neh 12:45\hebword{הַֽטׇּהֳרָ֔ה} This kamatz katan is subject to debate between experts and reading traditions.
						
						\item Neh 13:1\hebword{בְּאׇזְנֵ֣י}
						
						\item Neh 13:3\hebword{כְּשׇׁמְעָ֣ם}
						
						\item Neh 13:11\hebword{עַל־עׇמְדָֽם}
						
						\item Neh 13:14\hebword{זׇכְרָה־לִּ֥י}
						
						\item Neh 13:22\hebword{זׇכְרָה־לִּ֣י}
						
						\item Neh 13:26\hebword{הַנׇּכְרִיּֽוֹת}
						
						\item Neh 13:27\hebword{נׇכְרִיּֽוֹת}
						
						\item Neh 13:29\hebword{זׇכְרָ֥ה}
						
						\item Neh 13:29\hebword{גׇּאֳלֵ֣י} This kamatz katan is subject to debate between experts and reading traditions.
						
						\item Neh 13:31\hebword{זׇכְרָה־לִּ֥י}
						
	\end{itemize}\end{multicols}

\subsection{Chronicles}
\begin{multicols}{2}\begin{itemize}
		\item 1Chron 1:19\hebword{יׇקְטָֽן}
		
		\item 1Chron 1:20\hebword{וְיׇקְטָ֣ן}
		
		\item 1Chron 1:23\hebword{יׇקְטָֽן}
		
		\item 1Chron 1:32\hebword{וְיׇקְשָׁ֛ן}
		
		\item 1Chron 1:32\hebword{יׇקְשָׁ֖ן}
		
		\item 1Chron 1:43\hebword{מְלׇךְ־מֶ֖לֶךְ}
		
		\item 1Chron 1:44\hebword{וַיָּ֖מׇת}
		
		\item 1Chron 1:44\hebword{מִבׇּצְרָֽה}
		
		\item 1Chron 1:45\hebword{וַיָּ֖מׇת}
		
		\item 1Chron 1:46\hebword{וַיָּ֖מׇת}
		
		\item 1Chron 1:47\hebword{וַיָּ֖מׇת}
		
		\item 1Chron 1:48\hebword{וַיָּ֖מׇת}
		
		\item 1Chron 1:49\hebword{וַיָּ֖מׇת}
		
		\item 1Chron 1:51\hebword{וַיָּ֖מׇת}
		
		\item 1Chron 1:52\hebword{אׇהֳלִיבָמָ֛ה} This kamatz katan is subject to debate between experts and reading traditions.
		
		\item 1Chron 2:19\hebword{וַתָּ֖מׇת}
		
		\item 1Chron 2:30\hebword{וַיָּ֥מׇת}
		
		\item 1Chron 2:32\hebword{וַיָּ֥מׇת}
		
		\item 1Chron 2:44\hebword{יׇרְקְעָ֑ם}
				
				\item 1Chron 2:47\hebword{יׇהְדָּ֑י}
				
				\item 1Chron 2:54\hebword{הַצׇּרְעִֽי}
				
				\item 1Chron 3:4\hebword{וַיִּ֨מְלׇךְ־שָׁ֔ם}
				
				\item 1Chron 3:16\hebword{יְכׇנְיָ֥ה}
				
				\item 1Chron 3:17\hebword{יְכׇנְיָ֣ה}
				
				\item 1Chron 4:10\hebword{עׇצְבִּ֑י}
				
				\item 1Chron 4:13\hebword{עׇתְנִיאֵ֖ל}
				
				\item 1Chron 4:13\hebword{עׇתְנִיאֵ֖ל}
				
				\item 1Chron 4:14\hebword{אֶת־עׇפְרָ֑ה}
				
				\item 1Chron 4:30\hebword{וּבְחׇרְמָ֖ה}
				
				\item 1Chron 4:41\hebword{אֶת־אׇהֳלֵיהֶ֜ם} This kamatz katan is subject to debate between experts and reading traditions.
				
				\item 1Chron 5:10\hebword{בְּאׇ֣הֳלֵיהֶ֔ם} This kamatz katan is subject to debate between experts and reading traditions.
				
				\item 1Chron 5:16\hebword{וּבְכׇֽל־מִגְרְשֵׁ֥י}
				
				\item 1Chron 5:17\hebword{יָרׇבְעָ֥ם}
				
				\item 1Chron 6:6\hebword{יְאׇתְרַ֥י}
				
				\item 1Chron 6:53\hebword{וְאֶֽת־יׇקְמְעָם֙}
						
						\item 1Chron 7:8\hebword{וְעׇמְרִי֙}
						
						\item 1Chron 7:15\hebword{צְלׇפְחָ֑ד}
						
						\item 1Chron 7:15\hebword{לִצְלׇפְחָ֖ד}
						
						\item 1Chron 7:34\hebword{וְרׇהְגָּ֖ה}
						
						\item 1Chron 9:1\hebword{הׇגְל֥וּ}
						
						\item 1Chron 9:4\hebword{בֶּן־עׇמְרִי֙}
						
						\item 1Chron 9:19\hebword{הַקׇּרְחִ֗ים}
						
						\item 1Chron 9:31\hebword{הַקׇּרְחִ֑י}
						
						\item 1Chron 10:1\hebword{וַיָּ֤נׇס}
						
						\item 1Chron 10:4\hebword{וְדׇקְרֵ֣נִי}
						
						\item 1Chron 10:6\hebword{וַיָּ֤מׇת}
						
						\item 1Chron 10:8\hebword{מִֽמׇּחֳרָ֔ת} This kamatz katan is subject to debate between experts and reading traditions.
						
						\item 1Chron 10:10\hebword{וְאֶת־גֻּלְגׇּלְתּ֥וֹ}
						
						\item 1Chron 10:13\hebword{וַיָּ֣מׇת}
						
						\item 1Chron 11:11\hebword{יָשׇׁבְעָ֣ם}
						
						\item 1Chron 12:7\hebword{וְיָשׇׁבְעָ֖ם}
						
						\item 1Chron 12:7\hebword{הַקׇּרְחִֽים}
						
						\item 1Chron 12:18\hebword{לְעׇזְרֵ֔נִי}
						
						\item 1Chron 12:23\hebword{לְעׇזְר֑וֹ}
						
						\item 1Chron 13:10\hebword{וַיָּ֥מׇת}
						
						\item 1Chron 14:15\hebword{כְּֽשׇׁמְעֲךָ֞}
						
						\item 1Chron 16:10\hebword{קׇדְשׁ֔וֹ}
						
						\item 1Chron 16:21\hebword{לְעׇשְׁקָ֔ם}
						
						\item 1Chron 16:35\hebword{קׇדְשֶׁ֔ךָ}
						
						\item 1Chron 16:37\hebword{וַיַּעֲזׇב־שָׁ֗ם}
						
						\item 1Chron 17:20\hebword{בְּאׇזְנֵֽינוּ}
						
						\item 1Chron 18:10\hebword{לִשְׁאׇל־ל֨וֹ}
						
						\item 1Chron 19:1\hebword{וַיָּ֕מׇת}
						
						\item 1Chron 19:18\hebword{וַיָּ֣נׇס}
						
						\item 1Chron 20:3\hebword{וַיָּ֧שׇׁב}
						
						\item 1Chron 20:5\hebword{גׇּלְיָ֣ת}
						
						\item 1Chron 21:5\hebword{כׇֽל־יִשְׂרָאֵ֡ל}
						
						\item 1Chron 21:15\hebword{אׇרְנָ֥ן}
						
						\item 1Chron 21:18\hebword{אׇרְנָ֥ן}
						
						\item 1Chron 21:20\hebword{וַיָּ֣שׇׁב}
						
						\item 1Chron 21:20\hebword{אׇרְנָ֗ן}
						
						\item 1Chron 21:20\hebword{וְאׇרְנָ֖ן}
						
						\item 1Chron 21:21\hebword{עַד־אׇרְנָ֑ן}
						
						\item 1Chron 21:21\hebword{אׇרְנָן֙}
						
						\item 1Chron 21:22\hebword{אֶל־אׇרְנָ֗ן}
						
						\item 1Chron 21:23\hebword{אׇרְנָ֤ן}
						
						\item 1Chron 21:24\hebword{לְאׇרְנָ֔ן}
						
						\item 1Chron 21:25\hebword{לְאׇרְנָ֖ן}
						
						\item 1Chron 21:28\hebword{אׇרְנָ֣ן}
						
						\item 1Chron 22:14\hebword{בְעׇנְיִ֜י}
						
						\item 1Chron 23:13\hebword{קׇדָשִׁ֤ים} This kamatz katan is subject to debate between experts and reading traditions.
						
						\item 1Chron 23:28\hebword{וְעַֽל־טׇהֳרַ֖ת} This kamatz katan is subject to debate between experts and reading traditions.
						
						\item 1Chron 24:2\hebword{וַיָּ֨מׇת}
						
						\item 1Chron 25:4\hebword{יׇשְׁבְּקָ֣שָׁה}
						
						\item 1Chron 25:7\hebword{כׇּ֨ל־הַמֵּבִ֔ין}
						
						\item 1Chron 25:24\hebword{לְיׇשְׁבְּקָ֔שָׁה}
						
						\item 1Chron 26:1\hebword{לַקׇּרְחִ֕ים}
						
						\item 1Chron 26:7\hebword{עׇ֠תְנִ֠י}
						
						\item 1Chron 26:19\hebword{הַקׇּרְחִ֖י}
						
						\item 1Chron 26:23\hebword{לָעׇזִּיאֵלִֽי}
						
						\item 1Chron 27:1\hebword{חׇדְשֵׁ֣י}
						
						\item 1Chron 27:2\hebword{יָשׇׁבְעָ֖ם}
						
						\item 1Chron 27:15\hebword{לְעׇתְנִיאֵ֑ל}
						
						\item 1Chron 27:18\hebword{עׇמְרִ֖י}
						
						\item 1Chron 28:2\hebword{וַיָּ֨קׇם}
						
						\item 1Chron 28:8\hebword{וּבְאׇזְנֵ֣י}
						
						\item 1Chron 28:9\hebword{וְעׇבְדֵ֗הוּ}
						
						\item 1Chron 28:21\hebword{בַּֽחׇכְמָה֙}
						
						\item 1Chron 29:16\hebword{קׇדְשֶׁ֑ךָ}
						
						\item 1Chron 29:18\hebword{שׇׁמְרָה־זֹּ֣את}
						
						\item 1Chron 29:20\hebword{כׇֽל־הַקָּהָ֗ל}
						
						\item 1Chron 29:21\hebword{לְֽמׇחֳרַת֮} This kamatz katan is subject to debate between experts and reading traditions.
						
						\item 1Chron 29:28\hebword{וַיָּ֙מׇת֙}
						
						\item 2Chron 1:10\hebword{חׇכְמָ֤ה}
						
						\item 2Chron 1:11\hebword{חׇכְמָ֣ה}
						
						\item 2Chron 1:12\hebword{הַחׇכְמָ֥ה}
						
						\item 2Chron 2:5\hebword{יַֽעֲצׇר־כֹּ֙חַ֙}
						
						\item 2Chron 2:15\hebword{כְּכׇל־צׇרְכֶּ֔ךָ}
						
						\item 2Chron 3:1\hebword{אׇרְנָ֥ן}
						
						\item 2Chron 3:8\hebword{אׇרְכּ֞וֹ}
						
						\item 2Chron 3:8\hebword{וְרׇחְבּ֖וֹ}
						
						\item 2Chron 3:11\hebword{אׇרְכָּ֖ם}
						
						\item 2Chron 4:1\hebword{אׇרְכּ֔וֹ}
						
						\item 2Chron 4:1\hebword{רׇחְבּ֑וֹ}
						
						\item 2Chron 4:5\hebword{וְעׇבְי֣וֹ}
						
						\item 2Chron 4:6\hebword{לְרׇחְצָ֣ה}
						
						\item 2Chron 4:6\hebword{לְרׇחְצָ֥ה}
						
						\item 2Chron 5:1\hebword{אֶת־קׇדְשֵׁ֣י}
						
						\item 2Chron 6:13\hebword{אׇרְכּ֗וֹ}
						
						\item 2Chron 6:13\hebword{רׇחְבּ֔וֹ}
						
						\item 2Chron 6:32\hebword{אֶל־הַנׇּכְרִ֗י}
						
						\item 2Chron 6:33\hebword{הַנׇּכְרִ֑י}
						
						\item 2Chron 6:40\hebword{וְאׇזְנֶ֖יךָ}
						
						\item 2Chron 6:42\hebword{זׇכְרָ֕ה}
						
						\item 2Chron 7:10\hebword{לְאׇהֳלֵיהֶ֑ם} This kamatz katan is subject to debate between experts and reading traditions.
						
						\item 2Chron 7:15\hebword{וְאׇזְנַ֖י}
						
						\item 2Chron 9:3\hebword{חׇכְמַ֣ת}
						
						\item 2Chron 9:5\hebword{וְעַל־חׇכְמָתֶֽךָ}
						
						\item 2Chron 9:6\hebword{חׇכְמָתֶ֑ךָ}
						
						\item 2Chron 9:7\hebword{אֶת־חׇכְמָתֶֽךָ}
						
						\item 2Chron 9:18\hebword{מׇאֳחָזִ֔ים} This kamatz katan is subject to debate between experts and reading traditions.
						
						\item 2Chron 9:22\hebword{וְחׇכְמָֽה}
						
						\item 2Chron 9:23\hebword{אֶת־חׇכְמָת֔וֹ}
						
						\item 2Chron 9:29\hebword{עַל־יָרׇבְעָ֖ם}
						
						\item 2Chron 10:2\hebword{יָרׇבְעָ֤ם}
						
						\item 2Chron 10:2\hebword{וַיָּ֥שׇׁב}
						
						\item 2Chron 10:2\hebword{יָרׇבְעָ֖ם}
						
						\item 2Chron 10:3\hebword{יָרׇבְעָ֖ם}
						
						\item 2Chron 10:10\hebword{קָטׇנִּ֥י}
						
						\item 2Chron 10:10\hebword{מִמׇּתְנֵ֥י}
						
						\item 2Chron 10:12\hebword{יָרׇבְעָ֧ם}
						
						\item 2Chron 10:15\hebword{אֶל־יָרׇבְעָ֖ם}
						
						\item 2Chron 11:4\hebword{אֶל־יָרׇבְעָֽם}
						
						\item 2Chron 11:10\hebword{וְאֶת־צׇרְעָה֙}
						
						\item 2Chron 11:14\hebword{יָֽרׇבְעָם֙}
						
						\item 2Chron 12:13\hebword{בְּמׇלְכ֜וֹ}
						
						\item 2Chron 12:15\hebword{וְיָרׇבְעָ֖ם}
						
						\item 2Chron 13:1\hebword{יָרׇבְעָ֑ם}
						
						\item 2Chron 13:2\hebword{יָרׇבְעָֽם}
						
						\item 2Chron 13:3\hebword{וְיָרׇבְעָ֗ם}
				
				\item 2Chron 13:4\hebword{וַיָּ֣קׇם}
				
				\item 2Chron 13:4\hebword{יָרׇבְעָ֥ם}
				
				\item 2Chron 13:6\hebword{וַיָּ֙קׇם֙}
				
				\item 2Chron 13:6\hebword{יָרׇבְעָ֣ם}
				
				\item 2Chron 13:8\hebword{יָרׇבְעָ֖ם}
				
				\item 2Chron 13:13\hebword{וְיָרׇבְעָ֗ם}
				
				\item 2Chron 13:15\hebword{אֶת־יָרׇבְעָם֙}
				
				\item 2Chron 13:19\hebword{יָרׇבְעָם֒}
				
				\item 2Chron 13:20\hebword{כֹּֽחַ־יָרׇבְעָ֛ם}
				
				\item 2Chron 14:10\hebword{עׇזְרֵ֜נוּ}
				
				\item 2Chron 14:14\hebword{וְגַם־אׇהֳלֵ֥י} This kamatz katan is subject to debate between experts and reading traditions.
				
				\item 2Chron 15:4\hebword{וַיָּ֙שׇׁב֙}
				
				\item 2Chron 15:18\hebword{אֶת־קׇדְשֵׁ֥י}
				
				\item 2Chron 15:18\hebword{וְקׇדָשָׁ֖יו} This kamatz katan is subject to debate between experts and reading traditions.
				
				\item 2Chron 16:12\hebword{חׇלְי֑וֹ}
				
				\item 2Chron 16:12\hebword{וְגַם־בְּחׇלְיוֹ֙}
				
				\item 2Chron 16:13\hebword{וַיָּ֕מׇת}
				
				\item 2Chron 16:13\hebword{לְמׇלְכֽוֹ}
				
				\item 2Chron 17:7\hebword{לְמׇלְכ֗וֹ}
				
				\item 2Chron 18:4\hebword{דְּרׇשׁ־נָ֥א}
				
				\item 2Chron 18:33\hebword{הׇֽחֳלֵֽיתִי} This kamatz katan is subject to debate between experts and reading traditions.
				
				\item 2Chron 18:34\hebword{וַיָּ֕מׇת}
				
				\item 2Chron 19:1\hebword{וַ֠יָּ֠שׇׁב}
				
				\item 2Chron 19:4\hebword{וַיָּ֜שׇׁב}
				
				\item 2Chron 20:12\hebword{תִשְׁפׇּט־בָּ֔ם}
				
				\item 2Chron 20:19\hebword{הַקׇּרְחִ֑ים}
				
				\item 2Chron 20:29\hebword{בְּשׇׁמְעָ֕ם}
				
				\item 2Chron 20:31\hebword{בְּמׇלְכ֗וֹ}
				
				\item 2Chron 21:4\hebword{וַיָּ֨קׇם}
				
				\item 2Chron 21:5\hebword{בְּמׇלְכ֑וֹ}
				
				\item 2Chron 21:15\hebword{בׇּחֳלָיִ֥ים} This kamatz katan is subject to debate between experts and reading traditions.
				
				\item 2Chron 21:18\hebword{לׇחֳלִ֖י} This kamatz katan is subject to debate between experts and reading traditions.
				
				\item 2Chron 21:19\hebword{עִם־חׇלְי֔וֹ}
				
				\item 2Chron 21:19\hebword{וַיָּ֖מׇת}
				
				\item 2Chron 21:20\hebword{בְמׇלְכ֔וֹ}
				
				\item 2Chron 22:2\hebword{בְמׇלְכ֔וֹ}
				
				\item 2Chron 22:2\hebword{בַּת־עׇמְרִֽי}
				
				\item 2Chron 22:6\hebword{וַיָּ֜שׇׁב}
				
				\item 2Chron 22:10\hebword{וַתָּ֗קׇם}
				
				\item 2Chron 24:1\hebword{בְּמׇלְכ֔וֹ}
				
				\item 2Chron 24:7\hebword{כׇּל־קׇדְשֵׁ֣י}
				
				\item 2Chron 25:10\hebword{בׇּחֳרִי־אָֽף} This kamatz katan is subject to debate between experts and reading traditions.
				
				\item 2Chron 25:24\hebword{וַיָּ֖שׇׁב}
				
				\item 2Chron 25:27\hebword{וַיָּ֣נׇס}
				
				\item 2Chron 26:3\hebword{בְמׇלְכ֔וֹ}
				
				\item 2Chron 26:5\hebword{דׇּרְשׁ֣וֹ}
				
				\item 2Chron 26:21\hebword{הַֽחׇפְשִׁית֙}
				
				\item 2Chron 27:1\hebword{בְּמׇלְכ֔וֹ}
				
				\item 2Chron 27:8\hebword{בְמׇלְכ֑וֹ}
				
				\item 2Chron 28:1\hebword{בְּמׇלְכ֔וֹ}
				
				\item 2Chron 28:6\hebword{בְּעׇזְבָ֕ם}
				
				\item 2Chron 29:3\hebword{לְמׇלְכ֜וֹ}
			
				
				\item 2Chron 30:8\hebword{עׇרְפְּכֶ֖ם}
				
				\item 2Chron 30:16\hebword{עַל־עׇמְדָם֙}
				
				\item 2Chron 30:19\hebword{כְּטׇהֳרַ֥ת} This kamatz katan is subject to debate between experts and reading traditions.
				
				\item 2Chron 30:27\hebword{קׇדְשׁ֖וֹ}
				
				\item 2Chron 31:6\hebword{קׇֽדָשִׁ֔ים} This kamatz katan is subject to debate between experts and reading traditions.
				
				\item 2Chron 31:12\hebword{כׇּֽנַנְיָ֣הוּ} This kamatz katan is subject to debate between experts and reading traditions.
				
				\item 2Chron 31:13\hebword{כׇּֽנַנְיָ֙הוּ֙} This kamatz katan is subject to debate between experts and reading traditions.
				
				\item 2Chron 31:14\hebword{וְקׇדְשֵׁ֖י}
				
				\item 2Chron 32:8\hebword{לְעׇזְרֵ֔נוּ}
				
				\item 2Chron 32:21\hebword{וַיָּ֩שׇׁב֩}
				
				\item 2Chron 33:1\hebword{בְמׇלְכ֑וֹ}
				
				\item 2Chron 33:3\hebword{וַיָּ֗שׇׁב}
				
				\item 2Chron 33:21\hebword{בְּמׇלְכ֑וֹ}
				
				\item 2Chron 34:1\hebword{בְמׇלְכ֑וֹ}
				
				\item 2Chron 34:3\hebword{לְמׇלְכ֗וֹ}
				
				\item 2Chron 34:7\hebword{וַיָּ֖שׇׁב}
				
				\item 2Chron 34:8\hebword{לְמׇלְכ֔וֹ}
				
				\item 2Chron 34:22\hebword{בֶּן־תׇּקְהַ֗ת}
						
						\item 2Chron 34:27\hebword{בְּשׇׁמְעֲךָ֤}
						
						\item 2Chron 34:30\hebword{בְאׇזְנֵיהֶ֗ם}
						
						\item 2Chron 34:31\hebword{עַל־עׇמְד֗וֹ}
						
						\item 2Chron 35:9\hebword{וְ֠כׇֽנַנְיָ֠הוּ} This kamatz katan is subject to debate between experts and reading traditions.
						
						\item 2Chron 35:10\hebword{עַל־עׇמְדָ֛ם}
						
						\item 2Chron 35:23\hebword{הׇחֳלֵ֖יתִי} This kamatz katan is subject to debate between experts and reading traditions.
						
						\item 2Chron 35:24\hebword{וַיָּ֕מׇת}
						
						\item 2Chron 36:2\hebword{בְּמׇלְכ֑וֹ}
						
						\item 2Chron 36:5\hebword{בְּמׇלְכ֔וֹ}
						
						\item 2Chron 36:9\hebword{בְּמׇלְכ֔וֹ}
						
						\item 2Chron 36:11\hebword{בְמׇלְכ֑וֹ}
						
						\item 2Chron 36:13\hebword{אֶת־עׇרְפּוֹ֙}
						
						\item 2Chron 36:14\hebword{לִמְעׇל־מַ֔עַל}
	\end{itemize}\end{multicols}

\chapter{In Liturgy}
Ȝ ȝ
Listing kamatz katans in liturgy is a bit of a challenging task, since there are so many versions of the liturgy and much of it is composed of biblical verses.  Nonetheless, a few common examples are listed below.  Only the most common verses are included, since the entire Tanakh is included above. As before the word \hebword{כׇל} is omitted because of how common it is.
\begin{itemize}
		\item In many places, the root \hebword{קׇדְש־} with various suffixes
		\item In many places, \hebword{זׇכְרֵֽנּוּ} \hebword{חׇנֵּנוּ} \hebword{קׇרְאֵֽנוּ}
		\item In many places, \hebword{אׇכְלָם} and \hebword{חׇכְמָה}
		\item In many places, \hebword{אׇהֳל־} with various suffixes and \hebword{צׇהֳרָֽיִם}, both of which are subject to debate between experts and reading traditions.
		\item Musaf ȝamida and Korbanot \hebword{קׇרְבַּן}, with various suffixes
		\item Ashrei \hebword{וּגְדׇל־חָֽסֶד}
		\item Yotzer \hebword{וּבְטׇהֳרָה} This kamatz katan is subject to debate between experts and reading traditions.
		\item First and second paragraphs of Shema \hebword{וּֽבְשׇׁכְבְּךָ֖}
		\item Second paragraph of Shema \hebword{וּלְעׇבְד֔וֹ}
		\item In Avinu Malkeinu and the additional line for the Ten Days of Repentence, \hebword{זׇכְרֵֽנוּ} \hebword{וְכׇתְבֵֽנוּ} and during ne'ila \hebword{חׇתְמֵֽנוּ}
		\item In Ledor vador, \hebword{גׇּדְלֶךָ}
		\item In the blessing of Go'el Yisrael in the weekday ȝamida, \hebword{בְעׇנְיֵֽנוּ}
		\item In Modim \hebword{וּלְעׇבְדְּךָ}
		\item In Musaf and the yehi ratzon after the ȝamida, \hebword{נַעֲבׇדְךָ}
		\item In Ȝaleinu, \hebword{בְּגׇבְהֵי}
		\item In hamaȝariv aravim, \hebword{בְּחׇכְמָה}
		\item In Ahavat Ȝolam, \hebword{בְּשׇׁכְבֵּֽנוּ}
		\item In Kedusha Desidra, \hebword{יַעֲמׇס־לָ֗נוּ} and \hebword{וּלְעׇבְדוֹ}
		\item At the end of the Psalm for Tuesday \hebword{שׇׁפְטָ֣ה}
		\item In the Psalm for Wednesday \hebword{הַֽ֭יְחׇבְרְךָ}
		\item In the Psalm for Thursday \hebword{אֶבְחׇנְךָ֨}
		\item In the Psalm for Friday (which also appears in Kabbalat Shabbat and Shabbat/Festival Pesukei Dezimra) \hebword{דׇּכְיָֽם}
		\item In the misheberakh for the community, \hebword{צׇרְכֵי}
		\item In ta\d{h}anun, \hebword{אַֽל־תִּזְכׇּר־לָנוּ֮} and \hebword{עׇזְרֵ֤נוּ}
		\item In the Shabbat and Festival ȝamida, \hebword{לְעׇבְדְּךָ}
	\end{itemize}

\end{document} 