	\title{A list of words with Kamatz Katans in the Torah}
	
	\author{Nathan Kasimer}
	
	\maketitle
	
	\section{Introduction}
	This is a list of kamatz katans in the Torah.  The list was generated using a Python script from the "Miqra According to the Masora" project.  While it was reviewed and checked manually, the checking process was not very in-depth, and it likely contains errors.  Please report errors found by submitting an issue report in the github repo here: \url{https://github.com/nkasimer/kamatz-katan-list/issues}
	
	The various forms of the word \hebword{כל} have not been included because of how common the word is.  Special mention should be made, however, of Isaiah 40:12, where the word \hebword{כל} has a kamatz gadol and is a verb.  To ease looking up, all words are listed with their prefixes, except that prefixed \hebword{וְ} and \hebword{וּ} were removed. Metegs were removed to ease matching up duplicate words.  Words are listed without maqqaf, again to ease matching up duplicates.  Often this obscures the reason why the kamatz is katan, but this is intended just as a list, not as a thorough guide.  Dagesh in the first letter of words has been removed, also to match up duplicates.
	
	Words where reading traditions vary have been noted.  Generally these are words where a kamatz is followed by a gutteral consonant which is followed by a chataf-kamatz.  Sephardim, following the Radak, pronounce these as kamatz gadol.
	
	The listing is according to first appearance in the Torah.